---
title: "06_Relative_Abundance_Fig2"
output: html_document
author: "Ema H Graham"
---
For Questions Email: ema.graham@huskers.unl.edu

## Description

Input Notes: 
Will need the following files:
- Sequencing_Data_Info_Sheet3.csv (Metadata, provided on Github)
- counts2_bowtie.csv (generated in 03_Virome_Contig_Mapping.sh)
- vc_tax.csv (generated in 04_Contig_Annotation.sh)
- Bray_bw_win.csv (will generate in excel using this script)

Output Notes: 
Will generate a relative abundance plot (Figure 2) for the top then most abundant viral family taxonomy per subject by location.
Will statistically compare the Bray dissimilarity distances within subject location top ten most abundant viral familes between all other subject location viral family abundance profiles. Will generate box plots for Supplementary Figure 4.

```{r setup,message=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(phyloseq)
library(ggplot2)
library(ggsignif)
library(cowplot)
library(reshape2)
```

## Make Phyloseq Object

Upload sample metadata for the Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
Upload_Metadata <- read_csv("Sequencing_Data_Info_Sheet3.csv")
Metadata <- Upload_Metadata
# In the metadata change the Time_Collected so that it is better for graph outputs
Metadata$Time <- Metadata$Time_Collected
Metadata$Time[which(Metadata$Time == "T_0")] <- "00_Weeks"
Metadata$Time[which(Metadata$Time == "2_week")] <- "02_Weeks"
Metadata$Time[which(Metadata$Time == "1_month")] <- "04_Weeks"
Metadata$Time[which(Metadata$Time == "3_month")] <- "12_Weeks"
Metadata$Time[which(Metadata$Time == "6_month")] <- "24_Weeks"
# Make sample_data for Phyloseq
META <- sample_data(Metadata)
sample_names(META)= META$SampleID
```
Upload count data to make the OTU table for the Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_counts <- read.csv("counts2_bowtie.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CHeckV_counts  <- subset(CHeckV_counts , select = -c(length))
# Make otu_table for Phyloseq
CHeckV_bar_OTU <- otu_table(CHeckV_counts, taxa_are_rows = TRUE)
```
Upload taxonomy information to make the OTU table for the Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
tax_ann <- read.csv("vc_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
tax_ann <-as.matrix(tax_ann)
# Make tax_table for Phyloseq
CHeckV_bar_tax <- tax_table(tax_ann)
```
Make Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_bar_PHY <- phyloseq(CHeckV_bar_OTU, CHeckV_bar_tax, META)
```
Remove samples from individuals who did not complete from the study, samples from individuals who did not have a complete set of samples, and samples that were repeated samples
```{r,message=FALSE,warning=FALSE,results="hide"}
Samples_toRemove <- c("HV_001_27", "HV_002_27", "HV_003_27", "HV_004_27", "HV_005_27", "HV_006_27", "HV_007_27", "HV_008_27",
                      "HV_009_27", "HV_010_27", "HV_011_27", "HV_012_27", "HV_013_27", "HV_014_27", "HV_015_27", "HV_016_27",
                      "HV_017_27", "HV_018_27", "HV_019_27", "HV_020_27", "HV_021_27", "HV_022_27", "HV_023_27", "HV_024_27",
                      "HV_025_27", "HV_026_27", "HV_027_27", "HV_028_27", "HV_029_27", "HV_030_27", "HV_015_20", "HV_015_21", 
                      "HV_020_22", "HV_027_02", "HV_027_03", "HV_027_04", "HV_027_05", "HV_027_06", "HV_027_07", "HV_020_10",
                      "HV_021_13", "HV_027_01","HV_003_15")
```
Final Phyloseq Object
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_bar_PHY2 <- subset_samples(CHeckV_bar_PHY, !(SampleID %in% Samples_toRemove))
```
Human Skin Virome Phyloseq Object
```{r}
CHeckV_bar_PHY2
```

## Left Hand Taxa Sums

Calculate the top ten most abundant identified family level taxonomy for each subject for all left hand samples
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_bar_PHY2_LH<- subset_samples(CHeckV_bar_PHY2, Location=="left")
P_01 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P01")
TopNOTUs_P01 <- sort(tapply(taxa_sums(P_01), tax_table(P_01)[, "Family"], sum), TRUE)[1:10]
P_02 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P02")
TopNOTUs_P02 <- sort(tapply(taxa_sums(P_02), tax_table(P_02)[, "Family"], sum), TRUE)[1:10]
P_03 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P03")
TopNOTUs_P03 <- sort(tapply(taxa_sums(P_03), tax_table(P_03)[, "Family"], sum), TRUE)[1:10]
P_04 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P04")
TopNOTUs_P04 <- sort(tapply(taxa_sums(P_04), tax_table(P_04)[, "Family"], sum), TRUE)[1:10]
P_05 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P05")
TopNOTUs_P05 <- sort(tapply(taxa_sums(P_05), tax_table(P_05)[, "Family"], sum), TRUE)[1:10]
P_06 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P06")
TopNOTUs_P06 <- sort(tapply(taxa_sums(P_06), tax_table(P_06)[, "Family"], sum), TRUE)[1:10]
P_07 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P07")
TopNOTUs_P07 <- sort(tapply(taxa_sums(P_07), tax_table(P_07)[, "Family"], sum), TRUE)[1:10]
P_08 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P08")
TopNOTUs_P08 <- sort(tapply(taxa_sums(P_08), tax_table(P_08)[, "Family"], sum), TRUE)[1:10]
P_09 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P09")
TopNOTUs_P09 <- sort(tapply(taxa_sums(P_09), tax_table(P_09)[, "Family"], sum), TRUE)[1:10]
P_10 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P10")
TopNOTUs_P10 <- sort(tapply(taxa_sums(P_10), tax_table(P_10)[, "Family"], sum), TRUE)[1:10]
P_11 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P11")
TopNOTUs_P11 <- sort(tapply(taxa_sums(P_11), tax_table(P_11)[, "Family"], sum), TRUE)[1:10]
P_12 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P12")
TopNOTUs_P12 <- sort(tapply(taxa_sums(P_12), tax_table(P_12)[, "Family"], sum), TRUE)[1:10]
P_13 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P13")
TopNOTUs_P13 <- sort(tapply(taxa_sums(P_13), tax_table(P_13)[, "Family"], sum), TRUE)[1:10]
P_14 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P14")
TopNOTUs_P14 <- sort(tapply(taxa_sums(P_14), tax_table(P_14)[, "Family"], sum), TRUE)[1:10]
P_15 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P15")
TopNOTUs_P15 <- sort(tapply(taxa_sums(P_15), tax_table(P_15)[, "Family"], sum), TRUE)[1:10]
P_16 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P16")
TopNOTUs_P16 <- sort(tapply(taxa_sums(P_16), tax_table(P_16)[, "Family"], sum), TRUE)[1:10]
P_17 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P17")
TopNOTUs_P17 <- sort(tapply(taxa_sums(P_17), tax_table(P_17)[, "Family"], sum), TRUE)[1:10]
P_18 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P18")
TopNOTUs_P18 <- sort(tapply(taxa_sums(P_18), tax_table(P_18)[, "Family"], sum), TRUE)[1:10]
P_19 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P19")
TopNOTUs_P19 <- sort(tapply(taxa_sums(P_19), tax_table(P_19)[, "Family"], sum), TRUE)[1:10]
P_20 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P20")
TopNOTUs_P20 <- sort(tapply(taxa_sums(P_20), tax_table(P_20)[, "Family"], sum), TRUE)[1:10]
P_21 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P21")
TopNOTUs_P21 <- sort(tapply(taxa_sums(P_21), tax_table(P_21)[, "Family"], sum), TRUE)[1:10]
P_22 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P22")
TopNOTUs_P22 <- sort(tapply(taxa_sums(P_22), tax_table(P_22)[, "Family"], sum), TRUE)[1:10]
P_23 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P23")
TopNOTUs_P23 <- sort(tapply(taxa_sums(P_23), tax_table(P_23)[, "Family"], sum), TRUE)[1:10]
P_24 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P24")
TopNOTUs_P24 <- sort(tapply(taxa_sums(P_24), tax_table(P_24)[, "Family"], sum), TRUE)[1:10]
P_25 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P25")
TopNOTUs_P25 <- sort(tapply(taxa_sums(P_25), tax_table(P_25)[, "Family"], sum), TRUE)[1:10]
P_26 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P26")
TopNOTUs_P26 <- sort(tapply(taxa_sums(P_26), tax_table(P_26)[, "Family"], sum), TRUE)[1:10]
P_27 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P27")
TopNOTUs_P27 <- sort(tapply(taxa_sums(P_27), tax_table(P_27)[, "Family"], sum), TRUE)[1:10]
P_28 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P28")
TopNOTUs_P28 <- sort(tapply(taxa_sums(P_28), tax_table(P_28)[, "Family"], sum), TRUE)[1:10]
P_29 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P29")
TopNOTUs_P29 <- sort(tapply(taxa_sums(P_29), tax_table(P_29)[, "Family"], sum), TRUE)[1:10]
P_30 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P30")
TopNOTUs_P30 <- sort(tapply(taxa_sums(P_30), tax_table(P_30)[, "Family"], sum), TRUE)[1:10]
P_31 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P31")
TopNOTUs_P31 <- sort(tapply(taxa_sums(P_31), tax_table(P_31)[, "Family"], sum), TRUE)[1:10]
P_32 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P32")
TopNOTUs_P32 <- sort(tapply(taxa_sums(P_32), tax_table(P_32)[, "Family"], sum), TRUE)[1:10]
P_34 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P34")
TopNOTUs_P34 <- sort(tapply(taxa_sums(P_34), tax_table(P_34)[, "Family"], sum), TRUE)[1:10]
P_35 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P35")
TopNOTUs_P35 <- sort(tapply(taxa_sums(P_35), tax_table(P_35)[, "Family"], sum), TRUE)[1:10]
P_36 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P36")
TopNOTUs_P36 <- sort(tapply(taxa_sums(P_36), tax_table(P_36)[, "Family"], sum), TRUE)[1:10]
P_37 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P37")
TopNOTUs_P37 <- sort(tapply(taxa_sums(P_37), tax_table(P_37)[, "Family"], sum), TRUE)[1:10]
P_38 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P38")
TopNOTUs_P38 <- sort(tapply(taxa_sums(P_38), tax_table(P_38)[, "Family"], sum), TRUE)[1:10]
P_39 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P39")
TopNOTUs_P39 <- sort(tapply(taxa_sums(P_39), tax_table(P_39)[, "Family"], sum), TRUE)[1:10]
P_40 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P40")
TopNOTUs_P40 <- sort(tapply(taxa_sums(P_40), tax_table(P_40)[, "Family"], sum), TRUE)[1:10]
P_41 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P41")
TopNOTUs_P41 <- sort(tapply(taxa_sums(P_41), tax_table(P_41)[, "Family"], sum), TRUE)[1:10]
P_42 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P42")
TopNOTUs_P42 <- sort(tapply(taxa_sums(P_42), tax_table(P_42)[, "Family"], sum), TRUE)[1:10]
P_43 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P43")
TopNOTUs_P43 <- sort(tapply(taxa_sums(P_43), tax_table(P_43)[, "Family"], sum), TRUE)[1:10]
TopNOTUs_10_LH<-c(TopNOTUs_P01,TopNOTUs_P02,TopNOTUs_P03,TopNOTUs_P04,TopNOTUs_P05,TopNOTUs_P06,TopNOTUs_P07,TopNOTUs_P08,TopNOTUs_P09,TopNOTUs_P10,TopNOTUs_P11,TopNOTUs_P12,TopNOTUs_P13,TopNOTUs_P14,TopNOTUs_P15,TopNOTUs_P16,TopNOTUs_P17,TopNOTUs_P18,TopNOTUs_P19,TopNOTUs_P20,TopNOTUs_P21,TopNOTUs_P22,TopNOTUs_P23,TopNOTUs_P24,TopNOTUs_P25,TopNOTUs_P26,TopNOTUs_P27,TopNOTUs_P28,TopNOTUs_P29,TopNOTUs_P30,TopNOTUs_P31,TopNOTUs_P32,TopNOTUs_P34,TopNOTUs_P35,TopNOTUs_P36,TopNOTUs_P37,TopNOTUs_P38,TopNOTUs_P39,TopNOTUs_P40,TopNOTUs_P41,TopNOTUs_P42,TopNOTUs_P43)
TopNOTUs_10_list_LH<-unique(names(TopNOTUs_10_LH))
```
Viral Families that were not able to be taxonomically annotated (i.e. Unclassified Virus) were reduced
```{r,message=FALSE,warning=FALSE,results="hide"}
TopNOTUs_10_list_noUn_LH<-TopNOTUs_10_list_LH[!grepl("Unclassified",TopNOTUs_10_list_LH)]
TopNOTUs_10_list_noUn_LH<-TopNOTUs_10_list_noUn_LH[!grepl("Unlcassified",TopNOTUs_10_list_noUn_LH)]
TopNOTUs_10_list_noUn_LH<-c(TopNOTUs_10_list_noUn_LH,"Unclassified Cressdnaviricota")
TopNOTUs_10_list_noUn_LH<-c(TopNOTUs_10_list_noUn_LH,"Unclassified Duplodnaviria")
TopNOTUs_10_list_noUn_LH<-c(TopNOTUs_10_list_noUn_LH,"Unclassified Monodnaviria")
```
Top ten most abundant family level taxa per individual for left hand samples
```{r}
TopNOTUs_10_list_noUn_LH
```

## Right Hand Taxa Sums

Calculate the top ten most abundant identified family level taxonomy for each subject for all right hand samples
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_bar_PHY2_RH<- subset_samples(CHeckV_bar_PHY2, Location=="right")
P_01 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P01")
TopNOTUs_P01 <- sort(tapply(taxa_sums(P_01), tax_table(P_01)[, "Family"], sum), TRUE)[1:10]
P_02 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P02")
TopNOTUs_P02 <- sort(tapply(taxa_sums(P_02), tax_table(P_02)[, "Family"], sum), TRUE)[1:10]
P_03 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P03")
TopNOTUs_P03 <- sort(tapply(taxa_sums(P_03), tax_table(P_03)[, "Family"], sum), TRUE)[1:10]
P_04 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P04")
TopNOTUs_P04 <- sort(tapply(taxa_sums(P_04), tax_table(P_04)[, "Family"], sum), TRUE)[1:10]
P_05 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P05")
TopNOTUs_P05 <- sort(tapply(taxa_sums(P_05), tax_table(P_05)[, "Family"], sum), TRUE)[1:10]
P_06 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P06")
TopNOTUs_P06 <- sort(tapply(taxa_sums(P_06), tax_table(P_06)[, "Family"], sum), TRUE)[1:10]
P_07 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P07")
TopNOTUs_P07 <- sort(tapply(taxa_sums(P_07), tax_table(P_07)[, "Family"], sum), TRUE)[1:10]
P_08 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P08")
TopNOTUs_P08 <- sort(tapply(taxa_sums(P_08), tax_table(P_08)[, "Family"], sum), TRUE)[1:10]
P_09 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P09")
TopNOTUs_P09 <- sort(tapply(taxa_sums(P_09), tax_table(P_09)[, "Family"], sum), TRUE)[1:10]
P_10 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P10")
TopNOTUs_P10 <- sort(tapply(taxa_sums(P_10), tax_table(P_10)[, "Family"], sum), TRUE)[1:10]
P_11 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P11")
TopNOTUs_P11 <- sort(tapply(taxa_sums(P_11), tax_table(P_11)[, "Family"], sum), TRUE)[1:10]
P_12 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P12")
TopNOTUs_P12 <- sort(tapply(taxa_sums(P_12), tax_table(P_12)[, "Family"], sum), TRUE)[1:10]
P_13 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P13")
TopNOTUs_P13 <- sort(tapply(taxa_sums(P_13), tax_table(P_13)[, "Family"], sum), TRUE)[1:10]
P_14 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P14")
TopNOTUs_P14 <- sort(tapply(taxa_sums(P_14), tax_table(P_14)[, "Family"], sum), TRUE)[1:10]
P_15 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P15")
TopNOTUs_P15 <- sort(tapply(taxa_sums(P_15), tax_table(P_15)[, "Family"], sum), TRUE)[1:10]
P_16 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P16")
TopNOTUs_P16 <- sort(tapply(taxa_sums(P_16), tax_table(P_16)[, "Family"], sum), TRUE)[1:10]
P_17 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P17")
TopNOTUs_P17 <- sort(tapply(taxa_sums(P_17), tax_table(P_17)[, "Family"], sum), TRUE)[1:10]
P_18 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P18")
TopNOTUs_P18 <- sort(tapply(taxa_sums(P_18), tax_table(P_18)[, "Family"], sum), TRUE)[1:10]
P_19 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P19")
TopNOTUs_P19 <- sort(tapply(taxa_sums(P_19), tax_table(P_19)[, "Family"], sum), TRUE)[1:10]
P_20 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P20")
TopNOTUs_P20 <- sort(tapply(taxa_sums(P_20), tax_table(P_20)[, "Family"], sum), TRUE)[1:10]
P_21 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P21")
TopNOTUs_P21 <- sort(tapply(taxa_sums(P_21), tax_table(P_21)[, "Family"], sum), TRUE)[1:10]
P_22 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P22")
TopNOTUs_P22 <- sort(tapply(taxa_sums(P_22), tax_table(P_22)[, "Family"], sum), TRUE)[1:10]
P_23 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P23")
TopNOTUs_P23 <- sort(tapply(taxa_sums(P_23), tax_table(P_23)[, "Family"], sum), TRUE)[1:10]
P_24 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P24")
TopNOTUs_P24 <- sort(tapply(taxa_sums(P_24), tax_table(P_24)[, "Family"], sum), TRUE)[1:10]
P_25 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P25")
TopNOTUs_P25 <- sort(tapply(taxa_sums(P_25), tax_table(P_25)[, "Family"], sum), TRUE)[1:10]
P_26 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P26")
TopNOTUs_P26 <- sort(tapply(taxa_sums(P_26), tax_table(P_26)[, "Family"], sum), TRUE)[1:10]
P_27 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P27")
TopNOTUs_P27 <- sort(tapply(taxa_sums(P_27), tax_table(P_27)[, "Family"], sum), TRUE)[1:10]
P_28 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P28")
TopNOTUs_P28 <- sort(tapply(taxa_sums(P_28), tax_table(P_28)[, "Family"], sum), TRUE)[1:10]
P_29 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P29")
TopNOTUs_P29 <- sort(tapply(taxa_sums(P_29), tax_table(P_29)[, "Family"], sum), TRUE)[1:10]
P_30 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P30")
TopNOTUs_P30 <- sort(tapply(taxa_sums(P_30), tax_table(P_30)[, "Family"], sum), TRUE)[1:10]
P_31 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P31")
TopNOTUs_P31 <- sort(tapply(taxa_sums(P_31), tax_table(P_31)[, "Family"], sum), TRUE)[1:10]
P_32 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P32")
TopNOTUs_P32 <- sort(tapply(taxa_sums(P_32), tax_table(P_32)[, "Family"], sum), TRUE)[1:10]
P_34 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P34")
TopNOTUs_P34 <- sort(tapply(taxa_sums(P_34), tax_table(P_34)[, "Family"], sum), TRUE)[1:10]
P_35 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P35")
TopNOTUs_P35 <- sort(tapply(taxa_sums(P_35), tax_table(P_35)[, "Family"], sum), TRUE)[1:10]
P_36 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P36")
TopNOTUs_P36 <- sort(tapply(taxa_sums(P_36), tax_table(P_36)[, "Family"], sum), TRUE)[1:10]
P_37 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P37")
TopNOTUs_P37 <- sort(tapply(taxa_sums(P_37), tax_table(P_37)[, "Family"], sum), TRUE)[1:10]
P_38 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P38")
TopNOTUs_P38 <- sort(tapply(taxa_sums(P_38), tax_table(P_38)[, "Family"], sum), TRUE)[1:10]
P_39 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P39")
TopNOTUs_P39 <- sort(tapply(taxa_sums(P_39), tax_table(P_39)[, "Family"], sum), TRUE)[1:10]
P_40 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P40")
TopNOTUs_P40 <- sort(tapply(taxa_sums(P_40), tax_table(P_40)[, "Family"], sum), TRUE)[1:10]
P_41 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P41")
TopNOTUs_P41 <- sort(tapply(taxa_sums(P_41), tax_table(P_41)[, "Family"], sum), TRUE)[1:10]
P_42 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P42")
TopNOTUs_P42 <- sort(tapply(taxa_sums(P_42), tax_table(P_42)[, "Family"], sum), TRUE)[1:10]
P_43 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P43")
TopNOTUs_P43 <- sort(tapply(taxa_sums(P_43), tax_table(P_43)[, "Family"], sum), TRUE)[1:10]
TopNOTUs_10_RH<-c(TopNOTUs_P01,TopNOTUs_P02,TopNOTUs_P03,TopNOTUs_P04,TopNOTUs_P05,TopNOTUs_P06,TopNOTUs_P07,TopNOTUs_P08,TopNOTUs_P09,TopNOTUs_P10,TopNOTUs_P11,TopNOTUs_P12,TopNOTUs_P13,TopNOTUs_P14,TopNOTUs_P15,TopNOTUs_P16,TopNOTUs_P17,TopNOTUs_P18,TopNOTUs_P19,TopNOTUs_P20,TopNOTUs_P21,TopNOTUs_P22,TopNOTUs_P23,TopNOTUs_P24,TopNOTUs_P25,TopNOTUs_P26,TopNOTUs_P27,TopNOTUs_P28,TopNOTUs_P29,TopNOTUs_P30,TopNOTUs_P31,TopNOTUs_P32,TopNOTUs_P34,TopNOTUs_P35,TopNOTUs_P36,TopNOTUs_P37,TopNOTUs_P38,TopNOTUs_P39,TopNOTUs_P40,TopNOTUs_P41,TopNOTUs_P42,TopNOTUs_P43)
TopNOTUs_10_list_RH<-unique(names(TopNOTUs_10_RH))
```
Viral Families that were not able to be taxonomically annotated (i.e. Unclassified Virus) were reduced
```{r,message=FALSE,warning=FALSE,results="hide"}
TopNOTUs_10_list_noUn_RH<-TopNOTUs_10_list_RH[!grepl("Unclassified",TopNOTUs_10_list_RH)]
TopNOTUs_10_list_noUn_RH<-TopNOTUs_10_list_noUn_RH[!grepl("Unlcassified",TopNOTUs_10_list_noUn_RH)]
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Caudovirales")
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Cressdnaviricota")
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Duplodnaviria")
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Monodnaviria")
```
Top ten most abundant family level taxa per individual for right hand samples
```{r}
TopNOTUs_10_list_noUn_RH
```

## Scalp Taxa Sums

Calculate the top ten most abundant identified family level taxonomy for each subject for all scalp samples
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_bar_PHY2_SC<- subset_samples(CHeckV_bar_PHY2, Location=="scalp")
P_01 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P01")
TopNOTUs_P01 <- sort(tapply(taxa_sums(P_01), tax_table(P_01)[, "Family"], sum), TRUE)[1:10]
P_02 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P02")
TopNOTUs_P02 <- sort(tapply(taxa_sums(P_02), tax_table(P_02)[, "Family"], sum), TRUE)[1:10]
P_03 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P03")
TopNOTUs_P03 <- sort(tapply(taxa_sums(P_03), tax_table(P_03)[, "Family"], sum), TRUE)[1:10]
P_04 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P04")
TopNOTUs_P04 <- sort(tapply(taxa_sums(P_04), tax_table(P_04)[, "Family"], sum), TRUE)[1:10]
P_05 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P05")
TopNOTUs_P05 <- sort(tapply(taxa_sums(P_05), tax_table(P_05)[, "Family"], sum), TRUE)[1:10]
P_06 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P06")
TopNOTUs_P06 <- sort(tapply(taxa_sums(P_06), tax_table(P_06)[, "Family"], sum), TRUE)[1:10]
P_07 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P07")
TopNOTUs_P07 <- sort(tapply(taxa_sums(P_07), tax_table(P_07)[, "Family"], sum), TRUE)[1:10]
P_08 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P08")
TopNOTUs_P08 <- sort(tapply(taxa_sums(P_08), tax_table(P_08)[, "Family"], sum), TRUE)[1:10]
P_09 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P09")
TopNOTUs_P09 <- sort(tapply(taxa_sums(P_09), tax_table(P_09)[, "Family"], sum), TRUE)[1:10]
P_10 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P10")
TopNOTUs_P10 <- sort(tapply(taxa_sums(P_10), tax_table(P_10)[, "Family"], sum), TRUE)[1:10]
P_11 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P11")
TopNOTUs_P11 <- sort(tapply(taxa_sums(P_11), tax_table(P_11)[, "Family"], sum), TRUE)[1:10]
P_12 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P12")
TopNOTUs_P12 <- sort(tapply(taxa_sums(P_12), tax_table(P_12)[, "Family"], sum), TRUE)[1:10]
P_13 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P13")
TopNOTUs_P13 <- sort(tapply(taxa_sums(P_13), tax_table(P_13)[, "Family"], sum), TRUE)[1:10]
P_14 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P14")
TopNOTUs_P14 <- sort(tapply(taxa_sums(P_14), tax_table(P_14)[, "Family"], sum), TRUE)[1:10]
P_15 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P15")
TopNOTUs_P15 <- sort(tapply(taxa_sums(P_15), tax_table(P_15)[, "Family"], sum), TRUE)[1:10]
P_16 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P16")
TopNOTUs_P16 <- sort(tapply(taxa_sums(P_16), tax_table(P_16)[, "Family"], sum), TRUE)[1:10]
P_17 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P17")
TopNOTUs_P17 <- sort(tapply(taxa_sums(P_17), tax_table(P_17)[, "Family"], sum), TRUE)[1:10]
P_18 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P18")
TopNOTUs_P18 <- sort(tapply(taxa_sums(P_18), tax_table(P_18)[, "Family"], sum), TRUE)[1:10]
P_19 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P19")
TopNOTUs_P19 <- sort(tapply(taxa_sums(P_19), tax_table(P_19)[, "Family"], sum), TRUE)[1:10]
P_20 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P20")
TopNOTUs_P20 <- sort(tapply(taxa_sums(P_20), tax_table(P_20)[, "Family"], sum), TRUE)[1:10]
P_21 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P21")
TopNOTUs_P21 <- sort(tapply(taxa_sums(P_21), tax_table(P_21)[, "Family"], sum), TRUE)[1:10]
P_22 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P22")
TopNOTUs_P22 <- sort(tapply(taxa_sums(P_22), tax_table(P_22)[, "Family"], sum), TRUE)[1:10]
P_23 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P23")
TopNOTUs_P23 <- sort(tapply(taxa_sums(P_23), tax_table(P_23)[, "Family"], sum), TRUE)[1:10]
P_24 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P24")
TopNOTUs_P24 <- sort(tapply(taxa_sums(P_24), tax_table(P_24)[, "Family"], sum), TRUE)[1:10]
P_25 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P25")
TopNOTUs_P25 <- sort(tapply(taxa_sums(P_25), tax_table(P_25)[, "Family"], sum), TRUE)[1:10]
P_26 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P26")
TopNOTUs_P26 <- sort(tapply(taxa_sums(P_26), tax_table(P_26)[, "Family"], sum), TRUE)[1:10]
P_27 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P27")
TopNOTUs_P27 <- sort(tapply(taxa_sums(P_27), tax_table(P_27)[, "Family"], sum), TRUE)[1:10]
P_28 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P28")
TopNOTUs_P28 <- sort(tapply(taxa_sums(P_28), tax_table(P_28)[, "Family"], sum), TRUE)[1:10]
P_29 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P29")
TopNOTUs_P29 <- sort(tapply(taxa_sums(P_29), tax_table(P_29)[, "Family"], sum), TRUE)[1:10]
P_30 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P30")
TopNOTUs_P30 <- sort(tapply(taxa_sums(P_30), tax_table(P_30)[, "Family"], sum), TRUE)[1:10]
P_31 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P31")
TopNOTUs_P31 <- sort(tapply(taxa_sums(P_31), tax_table(P_31)[, "Family"], sum), TRUE)[1:10]
P_32 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P32")
TopNOTUs_P32 <- sort(tapply(taxa_sums(P_32), tax_table(P_32)[, "Family"], sum), TRUE)[1:10]
P_34 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P34")
TopNOTUs_P34 <- sort(tapply(taxa_sums(P_34), tax_table(P_34)[, "Family"], sum), TRUE)[1:10]
P_35 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P35")
TopNOTUs_P35 <- sort(tapply(taxa_sums(P_35), tax_table(P_35)[, "Family"], sum), TRUE)[1:10]
P_36 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P36")
TopNOTUs_P36 <- sort(tapply(taxa_sums(P_36), tax_table(P_36)[, "Family"], sum), TRUE)[1:10]
P_37 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P37")
TopNOTUs_P37 <- sort(tapply(taxa_sums(P_37), tax_table(P_37)[, "Family"], sum), TRUE)[1:10]
P_38 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P38")
TopNOTUs_P38 <- sort(tapply(taxa_sums(P_38), tax_table(P_38)[, "Family"], sum), TRUE)[1:10]
P_39 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P39")
TopNOTUs_P39 <- sort(tapply(taxa_sums(P_39), tax_table(P_39)[, "Family"], sum), TRUE)[1:10]
P_40 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P40")
TopNOTUs_P40 <- sort(tapply(taxa_sums(P_40), tax_table(P_40)[, "Family"], sum), TRUE)[1:10]
P_41 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P41")
TopNOTUs_P41 <- sort(tapply(taxa_sums(P_41), tax_table(P_41)[, "Family"], sum), TRUE)[1:10]
P_42 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P42")
TopNOTUs_P42 <- sort(tapply(taxa_sums(P_42), tax_table(P_42)[, "Family"], sum), TRUE)[1:10]
P_43 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P43")
TopNOTUs_P43 <- sort(tapply(taxa_sums(P_43), tax_table(P_43)[, "Family"], sum), TRUE)[1:10]
TopNOTUs_10_SC<-c(TopNOTUs_P01,TopNOTUs_P02,TopNOTUs_P03,TopNOTUs_P04,TopNOTUs_P05,TopNOTUs_P06,TopNOTUs_P07,TopNOTUs_P08,TopNOTUs_P09,TopNOTUs_P10,TopNOTUs_P11,TopNOTUs_P12,TopNOTUs_P13,TopNOTUs_P14,TopNOTUs_P15,TopNOTUs_P16,TopNOTUs_P17,TopNOTUs_P18,TopNOTUs_P19,TopNOTUs_P20,TopNOTUs_P21,TopNOTUs_P22,TopNOTUs_P23,TopNOTUs_P24,TopNOTUs_P25,TopNOTUs_P26,TopNOTUs_P27,TopNOTUs_P28,TopNOTUs_P29,TopNOTUs_P30,TopNOTUs_P31,TopNOTUs_P32,TopNOTUs_P34,TopNOTUs_P35,TopNOTUs_P36,TopNOTUs_P37,TopNOTUs_P38,TopNOTUs_P39,TopNOTUs_P40,TopNOTUs_P41,TopNOTUs_P42,TopNOTUs_P43)
TopNOTUs_10_list_SC<-unique(names(TopNOTUs_10_SC))
```
Viral Families that were not able to be taxonomically annotated (i.e. Unclassified Virus) were reduced
```{r,message=FALSE,warning=FALSE,results="hide"}
TopNOTUs_10_list_noUn_SC<-TopNOTUs_10_list_SC[!grepl("Unclassified",TopNOTUs_10_list_SC)]
TopNOTUs_10_list_noUn_SC<-TopNOTUs_10_list_noUn_SC[!grepl("Unlcassified",TopNOTUs_10_list_noUn_SC)]
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Caudovirales")
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Cressdnaviricota")
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Duplodnaviria")
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Monodnaviria")
```
Top ten most abundant family level taxa per individual for scalp samples
```{r}
TopNOTUs_10_list_noUn_SC
```

## Relative Abundance

Calculation of relative abundance for the top ten most abundant taxonomy per subject for left hand 
```{r,message=FALSE,warning=FALSE,results="hide"}
ent10_LH <- subset_taxa(CHeckV_bar_PHY2, Family %in% TopNOTUs_10_list_noUn_LH)
glom.subject_LH <- merge_samples(ent10_LH, "Subject")
# Calculate the relative abundance for each family in set
glom.subject.family_LH <- transform_sample_counts(glom.subject_LH, function(x) x / sum(x) )
glom_LH <- tax_glom(glom.subject.family_LH, taxrank = 'Family')
# Turn into a data.frame for graph generation
data_glom_LH<- psmelt(glom_LH)
data_glom_LH$Family <- as.character(data_glom_LH$Family)
data_glom_LH$Location<-"Left Hand"
data_glom_LH$Family <- factor(data_glom_LH$Family, levels = c("Siphoviridae", "Podoviridae", "Uncultured phage", "Myoviridae", "Herelleviridae", "Genomoviridae", "Microviridae", "Papillomaviridae", "Lake Sarah-associated circular molecule 3", "Pithoviridae", "Uncultured virus", "Sewage-associated circular DNA molecule", "Streptococcus satellite phage Javan305", "Caulimoviridae", "Staphylococcus phage PhiSepi-HH1", "Phycodnaviridae", "Circoviridae", "Staphylococcus phage PI-Sepi-HH2", "Baculoviridae", "Poxviridae", "Polyomaviridae", "Bovine faeces associated circular DNA virus 1", "Unclassified Cressdnaviricota", "Unclassified Duplodnaviria", "Unclassified Monodnaviria"))
```
Calculation of relative abundance for the top ten most abundant taxonomy per subject for right hand 
```{r,message=FALSE,warning=FALSE,results="hide"}
ent10_RH <- subset_taxa(CHeckV_bar_PHY2, Family %in% TopNOTUs_10_list_noUn_RH)
glom.subject_RH <- merge_samples(ent10_RH, "Subject")
# Calculate the relative abundance for each family in set
glom.subject.family_RH <- transform_sample_counts(glom.subject_RH, function(x) x / sum(x) )
glom_RH <- tax_glom(glom.subject.family_RH, taxrank = 'Family')
# Turn into a data.frame for graph generation
data_glom_RH<- psmelt(glom_RH)
data_glom_RH$Family <- as.character(data_glom_RH$Family)
data_glom_RH$Location<-"Right Hand"
data_glom_RH$Family <- factor(data_glom_RH$Family, levels = c("Caulimoviridae", "Siphoviridae", "Microviridae", "Papillomaviridae", "Genomoviridae", "Herelleviridae", "Baculoviridae", "Circoviridae", "Uncultured phage", "Myoviridae", "Sewage-associated circular DNA molecule", "Lake Sarah-associated circular molecule 3", "Podoviridae", "Mimiviridae", "Staphylococcus phage PI-Sepi-HH2", "Staphylococcus phage PhiSepi-HH1", "Streptococcus satellite phage Javan359", "Streptococcus satellite phage Javan360", "Smacoviridae", "Uncultured human fecal virus clone E.ramosum_S04.r3.N09_4_c1", "Inoviridae", "Uncultured virus isolate Wastewater_Circular_Virus_FL54", "Unclassified Caudovirales", "Unclassified Cressdnaviricota", "Unclassified Duplodnaviria", "Unclassified Monodnaviria"))
```
Calculation of relative abundance for the top ten most abundant taxonomy per subject for scalp
```{r,message=FALSE,warning=FALSE,results="hide"}
ent10_SC <- subset_taxa(CHeckV_bar_PHY2, Family %in% TopNOTUs_10_list_noUn_SC)
glom.subject_SC <- merge_samples(ent10_SC, "Subject")
# Calculate the relative abundance for each family in set
glom.subject.family_SC <- transform_sample_counts(glom.subject_SC, function(x) x / sum(x) )
glom_SC <- tax_glom(glom.subject.family_SC, taxrank = 'Family')
# Turn into a data.frame for graph generation
data_glom_SC<- psmelt(glom_SC)
data_glom_SC$Family <- as.character(data_glom_SC$Family)
data_glom_SC$Location<-"Scalp"
data_glom_SC$Family <- factor(data_glom_SC$Family, levels = c("Circoviridae", "Siphoviridae", "Herelleviridae", "Genomoviridae", "Papillomaviridae", "Lake Sarah-associated circular molecule 3", "Myoviridae", "Uncultured virus", "Podoviridae", "Microviridae", "Caulimoviridae", "Sewage-associated circular DNA molecule", "Autographiviridae", "Retroviridae", "Anelloviridae", "Gopherus associated circular DNA virus 4", "Baculoviridae", "Phycodnaviridae", "Chicken virus mg4_2302", "Streptococcus satellite phage Javan361", "Unclassified Caudovirales", "Unclassified Cressdnaviricota", "Unclassified Duplodnaviria", "Unclassified Monodnaviria" ))
```
Combine the three location datasets
```{r,message=FALSE,warning=FALSE,results="hide"}
data_glom_ALL<-rbind(data_glom_SC,data_glom_RH,data_glom_LH)
```
Generate relative abundance plot
```{r,message=FALSE,warning=FALSE,results="hide"}
spatial_plot <- ggplot(data=data_glom_ALL, aes(x=Location, y=Abundance, fill=Family)) + facet_grid(~Sample, scales = "free")+geom_col(position = "fill")

relativeabund<-spatial_plot + geom_bar(aes(), stat="identity", position="stack",colour = 'black')  +
theme(legend.position="bottom",axis.title.x = element_text(vjust=1, hjust=2,size=12),legend.text=element_text(size=12),
      axis.title.y = element_text(vjust=1,size=12),) + guides(fill=guide_legend(nrow=7),size=12)+theme(axis.text.x = element_text(angle = 90,size=12))+ylab("Relative Abundance")
ggsave(plot=relativeabund,"Figures/RelativeAbundanceFIGURE.pdf",dpi = 500, width = 29,
  height = 16, units="in",pointsize=12)
```
Relative abundance of the top ten most abundant identified viral families per subject by location
```{r}
relativeabund
```

## Statistically compare relative abundance of the top ten most abundant identified viral families per subject by location profiles

```{r}
sample_names(glom_RH)<- gsub('P', 'RH_P', sample_names(glom_RH))
sample_names(glom_LH)<- gsub('P', 'LH_P', sample_names(glom_LH))
sample_names(glom_SC)<- gsub('P', 'SC_P', sample_names(glom_SC))
total_glom<-merge_phyloseq(glom_RH,glom_LH,glom_SC )
mea_glom<-phyloseq::distance(total_glom, method="bray")
df_glom <- melt(as.matrix(mea_glom), varnames = c("row", "col"))
```
Overall Bray Within Subject Location vs Between Subject P01
```{r,message=FALSE,warning=FALSE,results="hide"}
P01_df<-c("LH_P01","RH_P01","SC_P01")
P01_df_glom<-subset(df_glom, col %in% P01_df)
df_between<-subset(P01_df_glom, !row %in% P01_df)
df_within<-subset(P01_df_glom, row %in% P01_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P01_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P01_both
```
Overall Bray Within Subject Location vs Between Subject P02
```{r,message=FALSE,warning=FALSE,results="hide"}
P02_df<-c("LH_P02","RH_P02","SC_P02")
P02_df_glom<-subset(df_glom, col %in% P02_df)
df_between<-subset(P02_df_glom, !row %in% P02_df)
df_within<-subset(P02_df_glom, row %in% P02_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P02_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P02_both
```
Overall Bray Within Subject Location vs Between Subject P03
```{r,message=FALSE,warning=FALSE,results="hide"}
P03_df<-c("LH_P03","RH_P03","SC_P03")
P03_df_glom<-subset(df_glom, col %in% P03_df)
df_between<-subset(P03_df_glom, !row %in% P03_df)
df_within<-subset(P03_df_glom, row %in% P03_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P03_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P03_both
```
Overall Bray Within Subject Location vs Between Subject P04
```{r,message=FALSE,warning=FALSE,results="hide"}
P04_df<-c("LH_P04","RH_P04","SC_P04")
P04_df_glom<-subset(df_glom, col %in% P04_df)
df_between<-subset(P04_df_glom, !row %in% P04_df)
df_within<-subset(P04_df_glom, row %in% P04_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P04_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P04_both
```
Overall Bray Within Subject Location vs Between Subject P05
```{r,message=FALSE,warning=FALSE,results="hide"}
P05_df<-c("LH_P05","RH_P05","SC_P05")
P05_df_glom<-subset(df_glom, col %in% P05_df)
df_between<-subset(P05_df_glom, !row %in% P05_df)
df_within<-subset(P05_df_glom, row %in% P05_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P05_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P05_both
```
Overall Bray Within Subject Location vs Between Subject P06
```{r,message=FALSE,warning=FALSE,results="hide"}
P06_df<-c("LH_P06","RH_P06","SC_P06")
P06_df_glom<-subset(df_glom, col %in% P06_df)
df_between<-subset(P06_df_glom, !row %in% P06_df)
df_within<-subset(P06_df_glom, row %in% P06_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P06_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P06_both
```
Overall Bray Within Subject Location vs Between Subject P07
```{r,message=FALSE,warning=FALSE,results="hide"}
P07_df<-c("LH_P07","RH_P07","SC_P07")
P07_df_glom<-subset(df_glom, col %in% P07_df)
df_between<-subset(P07_df_glom, !row %in% P07_df)
df_within<-subset(P07_df_glom, row %in% P07_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P07_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P07_both
```
Overall Bray Within Subject Location vs Between Subject P08
```{r,message=FALSE,warning=FALSE,results="hide"}
P08_df<-c("LH_P08","RH_P08","SC_P08")
P08_df_glom<-subset(df_glom, col %in% P08_df)
df_between<-subset(P08_df_glom, !row %in% P08_df)
df_within<-subset(P08_df_glom, row %in% P08_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P08_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P08_both
```
Overall Bray Within Subject Location vs Between Subject P09
```{r,message=FALSE,warning=FALSE,results="hide"}
P09_df<-c("LH_P09","RH_P09","SC_P09")
P09_df_glom<-subset(df_glom, col %in% P09_df)
df_between<-subset(P09_df_glom, !row %in% P09_df)
df_within<-subset(P09_df_glom, row %in% P09_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P09_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P09_both
```
Overall Bray Within Subject Location vs Between Subject P10
```{r,message=FALSE,warning=FALSE,results="hide"}
P10_df<-c("LH_P10","RH_P10","SC_P10")
P10_df_glom<-subset(df_glom, col %in% P10_df)
df_between<-subset(P10_df_glom, !row %in% P10_df)
df_within<-subset(P10_df_glom, row %in% P10_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P10_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P10_both
```
Overall Bray Within Subject Location vs Between Subject P11
```{r,message=FALSE,warning=FALSE,results="hide"}
P11_df<-c("LH_P11","RH_P11","SC_P11")
P11_df_glom<-subset(df_glom, col %in% P11_df)
df_between<-subset(P11_df_glom, !row %in% P11_df)
df_within<-subset(P11_df_glom, row %in% P11_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P11_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P11_both
```
Overall Bray Within Subject Location vs Between Subject P12
```{r,message=FALSE,warning=FALSE,results="hide"}
P12_df<-c("LH_P12","RH_P12","SC_P12")
P12_df_glom<-subset(df_glom, col %in% P12_df)
df_between<-subset(P12_df_glom, !row %in% P12_df)
df_within<-subset(P12_df_glom, row %in% P12_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P12_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P12_both
```
Overall Bray Within Subject Location vs Between Subject P13
```{r,message=FALSE,warning=FALSE,results="hide"}
P13_df<-c("LH_P13","RH_P13","SC_P13")
P13_df_glom<-subset(df_glom, col %in% P13_df)
df_between<-subset(P13_df_glom, !row %in% P13_df)
df_within<-subset(P13_df_glom, row %in% P13_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P13_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P13_both
```
Overall Bray Within Subject Location vs Between Subject P14
```{r,message=FALSE,warning=FALSE,results="hide"}
P14_df<-c("LH_P14","RH_P14","SC_P14")
P14_df_glom<-subset(df_glom, col %in% P14_df)
df_between<-subset(P14_df_glom, !row %in% P14_df)
df_within<-subset(P14_df_glom, row %in% P14_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P14_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P14_both
```
Overall Bray Within Subject Location vs Between Subject P15
```{r,message=FALSE,warning=FALSE,results="hide"}
P15_df<-c("LH_P15","RH_P15","SC_P15")
P15_df_glom<-subset(df_glom, col %in% P15_df)
df_between<-subset(P15_df_glom, !row %in% P15_df)
df_within<-subset(P15_df_glom, row %in% P15_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P15_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P15_both
```
Overall Bray Within Subject Location vs Between Subject P16
```{r,message=FALSE,warning=FALSE,results="hide"}
P16_df<-c("LH_P16","RH_P16","SC_P16")
P16_df_glom<-subset(df_glom, col %in% P16_df)
df_between<-subset(P16_df_glom, !row %in% P16_df)
df_within<-subset(P16_df_glom, row %in% P16_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P16_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P16_both
```
Overall Bray Within Subject Location vs Between Subject P17
```{r,message=FALSE,warning=FALSE,results="hide"}
P17_df<-c("LH_P17","RH_P17","SC_P17")
P17_df_glom<-subset(df_glom, col %in% P17_df)
df_between<-subset(P17_df_glom, !row %in% P17_df)
df_within<-subset(P17_df_glom, row %in% P17_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P17_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P17_both
```
Overall Bray Within Subject Location vs Between Subject P18
```{r,message=FALSE,warning=FALSE,results="hide"}
P18_df<-c("LH_P18","RH_P18","SC_P18")
P18_df_glom<-subset(df_glom, col %in% P18_df)
df_between<-subset(P18_df_glom, !row %in% P18_df)
df_within<-subset(P18_df_glom, row %in% P18_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P18_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P18_both
```
Overall Bray Within Subject Location vs Between Subject P19
```{r,message=FALSE,warning=FALSE,results="hide"}
P19_df<-c("LH_P19","RH_P19","SC_P19")
P19_df_glom<-subset(df_glom, col %in% P19_df)
df_between<-subset(P19_df_glom, !row %in% P19_df)
df_within<-subset(P19_df_glom, row %in% P19_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P19_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P19_both
```
Overall Bray Within Subject Location vs Between Subject P20
```{r,message=FALSE,warning=FALSE,results="hide"}
P20_df<-c("LH_P20","RH_P20","SC_P20")
P20_df_glom<-subset(df_glom, col %in% P20_df)
df_between<-subset(P20_df_glom, !row %in% P20_df)
df_within<-subset(P20_df_glom, row %in% P20_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P20_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P20_both
```
Overall Bray Within Subject Location vs Between Subject P21
```{r,message=FALSE,warning=FALSE,results="hide"}
P21_df<-c("LH_P21","RH_P21","SC_P21")
P21_df_glom<-subset(df_glom, col %in% P21_df)
df_between<-subset(P21_df_glom, !row %in% P21_df)
df_within<-subset(P21_df_glom, row %in% P21_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P21_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P21_both
```
Overall Bray Within Subject Location vs Between Subject P22
```{r,message=FALSE,warning=FALSE,results="hide"}
P22_df<-c("LH_P22","RH_P22","SC_P22")
P22_df_glom<-subset(df_glom, col %in% P22_df)
df_between<-subset(P22_df_glom, !row %in% P22_df)
df_within<-subset(P22_df_glom, row %in% P22_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P22_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P22_both
```
Overall Bray Within Subject Location vs Between Subject P23
```{r,message=FALSE,warning=FALSE,results="hide"}
P23_df<-c("LH_P23","RH_P23","SC_P23")
P23_df_glom<-subset(df_glom, col %in% P23_df)
df_between<-subset(P23_df_glom, !row %in% P23_df)
df_within<-subset(P23_df_glom, row %in% P23_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P23_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P23_both
```
Overall Bray Within Subject Location vs Between Subject P24
```{r,message=FALSE,warning=FALSE,results="hide"}
P24_df<-c("LH_P24","RH_P24","SC_P24")
P24_df_glom<-subset(df_glom, col %in% P24_df)
df_between<-subset(P24_df_glom, !row %in% P24_df)
df_within<-subset(P24_df_glom, row %in% P24_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P24_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P24_both
```
Overall Bray Within Subject Location vs Between Subject P25
```{r,message=FALSE,warning=FALSE,results="hide"}
P25_df<-c("LH_P25","RH_P25","SC_P25")
P25_df_glom<-subset(df_glom, col %in% P25_df)
df_between<-subset(P25_df_glom, !row %in% P25_df)
df_within<-subset(P25_df_glom, row %in% P25_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P25_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P25_both
```
Overall Bray Within Subject Location vs Between Subject P26
```{r,message=FALSE,warning=FALSE,results="hide"}
P26_df<-c("LH_P26","RH_P26","SC_P26")
P26_df_glom<-subset(df_glom, col %in% P26_df)
df_between<-subset(P26_df_glom, !row %in% P26_df)
df_within<-subset(P26_df_glom, row %in% P26_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P26_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P26_both
```
Overall Bray Within Subject Location vs Between Subject P27
```{r,message=FALSE,warning=FALSE,results="hide"}
P27_df<-c("LH_P27","RH_P27","SC_P27")
P27_df_glom<-subset(df_glom, col %in% P27_df)
df_between<-subset(P27_df_glom, !row %in% P27_df)
df_within<-subset(P27_df_glom, row %in% P27_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P27_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P27_both
```
Overall Bray Within Subject Location vs Between Subject P28
```{r,message=FALSE,warning=FALSE,results="hide"}
P28_df<-c("LH_P28","RH_P28","SC_P28")
P28_df_glom<-subset(df_glom, col %in% P28_df)
df_between<-subset(P28_df_glom, !row %in% P28_df)
df_within<-subset(P28_df_glom, row %in% P28_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P28_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P28_both
```
Overall Bray Within Subject Location vs Between Subject P29
```{r,message=FALSE,warning=FALSE,results="hide"}
P29_df<-c("LH_P29","RH_P29","SC_P29")
P29_df_glom<-subset(df_glom, col %in% P29_df)
df_between<-subset(P29_df_glom, !row %in% P29_df)
df_within<-subset(P29_df_glom, row %in% P29_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P29_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P29_both
```
Overall Bray Within Subject Location vs Between Subject P30
```{r,message=FALSE,warning=FALSE,results="hide"}
P30_df<-c("LH_P30","RH_P30","SC_P30")
P30_df_glom<-subset(df_glom, col %in% P30_df)
df_between<-subset(P30_df_glom, !row %in% P30_df)
df_within<-subset(P30_df_glom, row %in% P30_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P30_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P30_both
```
Overall Bray Within Subject Location vs Between Subject P31
```{r,message=FALSE,warning=FALSE,results="hide"}
P31_df<-c("LH_P31","RH_P31","SC_P31")
P31_df_glom<-subset(df_glom, col %in% P31_df)
df_between<-subset(P31_df_glom, !row %in% P31_df)
df_within<-subset(P31_df_glom, row %in% P31_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P31_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P31_both
```
Overall Bray Within Subject Location vs Between Subject P32
```{r,message=FALSE,warning=FALSE,results="hide"}
P32_df<-c("LH_P32","RH_P32","SC_P32")
P32_df_glom<-subset(df_glom, col %in% P32_df)
df_between<-subset(P32_df_glom, !row %in% P32_df)
df_within<-subset(P32_df_glom, row %in% P32_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P32_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P32_both
```
Overall Bray Within Subject Location vs Between Subject P34
```{r,message=FALSE,warning=FALSE,results="hide"}
P34_df<-c("LH_P34","RH_P34","SC_P34")
P34_df_glom<-subset(df_glom, col %in% P34_df)
df_between<-subset(P34_df_glom, !row %in% P34_df)
df_within<-subset(P34_df_glom, row %in% P34_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P34_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P34_both
```
Overall Bray Within Subject Location vs Between Subject P35
```{r,message=FALSE,warning=FALSE,results="hide"}
P35_df<-c("LH_P35","RH_P35","SC_P35")
P35_df_glom<-subset(df_glom, col %in% P35_df)
df_between<-subset(P35_df_glom, !row %in% P35_df)
df_within<-subset(P35_df_glom, row %in% P35_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P35_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P35_both
```
Overall Bray Within Subject Location vs Between Subject P36
```{r,message=FALSE,warning=FALSE,results="hide"}
P36_df<-c("LH_P36","RH_P36","SC_P36")
P36_df_glom<-subset(df_glom, col %in% P36_df)
df_between<-subset(P36_df_glom, !row %in% P36_df)
df_within<-subset(P36_df_glom, row %in% P36_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P36_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P36_both
```
Overall Bray Within Subject Location vs Between Subject P37
```{r,message=FALSE,warning=FALSE,results="hide"}
P37_df<-c("LH_P37","RH_P37","SC_P37")
P37_df_glom<-subset(df_glom, col %in% P37_df)
df_between<-subset(P37_df_glom, !row %in% P37_df)
df_within<-subset(P37_df_glom, row %in% P37_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P37_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P37_both
```
Overall Bray Within Subject Location vs Between Subject P38
```{r,message=FALSE,warning=FALSE,results="hide"}
P38_df<-c("LH_P38","RH_P38","SC_P38")
P38_df_glom<-subset(df_glom, col %in% P38_df)
df_between<-subset(P38_df_glom, !row %in% P38_df)
df_within<-subset(P38_df_glom, row %in% P38_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P38_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P38_both
```
Overall Bray Within Subject Location vs Between Subject P39
```{r,message=FALSE,warning=FALSE,results="hide"}
P39_df<-c("LH_P39","RH_P39","SC_P39")
P39_df_glom<-subset(df_glom, col %in% P39_df)
df_between<-subset(P39_df_glom, !row %in% P39_df)
df_within<-subset(P39_df_glom, row %in% P39_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P39_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P39_both
```
Overall Bray Within Subject Location vs Between Subject P40
```{r,message=FALSE,warning=FALSE,results="hide"}
P40_df<-c("LH_P40","RH_P40","SC_P40")
P40_df_glom<-subset(df_glom, col %in% P40_df)
df_between<-subset(P40_df_glom, !row %in% P40_df)
df_within<-subset(P40_df_glom, row %in% P40_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P40_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P40_both
```
Overall Bray Within Subject Location vs Between Subject P41
```{r,message=FALSE,warning=FALSE,results="hide"}
P41_df<-c("LH_P41","RH_P41","SC_P41")
P41_df_glom<-subset(df_glom, col %in% P41_df)
df_between<-subset(P41_df_glom, !row %in% P41_df)
df_within<-subset(P41_df_glom, row %in% P41_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P41_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P41_both
```
Overall Bray Within Subject Location vs Between Subject P42
```{r,message=FALSE,warning=FALSE,results="hide"}
P42_df<-c("LH_P42","RH_P42","SC_P42")
P42_df_glom<-subset(df_glom, col %in% P42_df)
df_between<-subset(P42_df_glom, !row %in% P42_df)
df_within<-subset(P42_df_glom, row %in% P42_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P42_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P42_both
```
Overall Bray Within Subject Location vs Between Subject P43
```{r,message=FALSE,warning=FALSE,results="hide"}
P43_df<-c("LH_P43","RH_P43","SC_P43")
P43_df_glom<-subset(df_glom, col %in% P43_df)
df_between<-subset(P43_df_glom, !row %in% P43_df)
df_within<-subset(P43_df_glom, row %in% P43_df)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
Overall_P43_both<-c(mean(df_between$value),mean(df_within2$value))
Overall_P43_both
```
# Results were stored in an excel file named Bray_bw_win.csv (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index

## Make Box Plots with Wilcoxon Test to Compare Between Subject and Within Subject Bray Curtis Dissimilarity

```{r,message=FALSE,warning=FALSE,results="hide"}
bray_plot<-read.csv("Bray_bw_win.csv", quote = "", header = TRUE, stringsAsFactors = FALSE)
my_comparisons <- list( c("Between", "Within")) 
symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
```
```{r,message=FALSE,warning=FALSE,results="hide"}
p_Overall<-ggplot(bray_plot, aes(Comparison,Distance))+
  geom_boxplot(alpha=0.5)+
  ylab("Dissimilarity")+
  theme(legend.position="none", axis.text.x=element_text(angle=45,hjust=1,vjust=1,size=12),axis.title.x=element_blank())+
  stat_compare_means(method = "wilcox.test",comparisons = my_comparisons)+
  theme_half_open()
```
```{r,message=FALSE,warning=FALSE,results="hide"}
p_Overall2<-ggplot(bray_plot, aes(Comparison,Distance))+
  geom_boxplot(alpha=0.5)+
  ylab("Dissimilarity")+
  theme(legend.position="none", axis.text.x=element_text(angle=45,hjust=1,vjust=1,size=12),axis.title.x=element_blank())+
  stat_compare_means(method = "wilcox.test",comparisons = my_comparisons,  symnum.args = symnum.args)+
  theme_half_open()
```
```{r}
p_Overall
```
```{r}
p_Overall2
```
```{r}
ggsave("bray_fig.pdf", p_Overall2,  width = 6, height = 4, units = "in",dpi = 300, pointsize=12)
```
