---
title: "11_Set_C"
output: html_document
author: "Ema H Graham"
---
For Questions Email: ema.graham@huskers.unl.edu

## Description

Input Notes: 
Will need the following files:

Output Notes: 

```{r setup,message=FALSE}
library(readr)
library(dplyr)
library(plyr)
library(tidyr)
library(ggplot2)
```

# Determine Stable Unclassified Contig Markers by Location for Set C

Sum across all contigs for each sample to get the total abundance of each contig per sample 
(This will incorporate all contigs including those idenfied as viral for Set A. They will be removed later.)
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_OTU <- read.csv("counts2_bowtie.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CONTIG_OTU$Species <- row.names(CONTIG_OTU)
CONTIG_OTU <- subset(CONTIG_OTU , select = -c(length))
CONTIG_OTU_SUMS<-CONTIG_OTU
CONTIG_OTU_SUMS<- subset (CONTIG_OTU_SUMS, select = -c(HV_001_27,HV_004_27,HV_005_27,HV_006_27,HV_007_27,HV_008_27,HV_009_27,HV_010_27,HV_011_27,HV_012_27,HV_013_27,HV_014_27,HV_015_20,HV_015_27,HV_016_27,HV_017_27,HV_018_27,HV_019_27,HV_020_10,HV_020_22,HV_020_27,HV_021_13,HV_021_27,HV_022_27,HV_023_27,HV_024_27,HV_025_27,HV_026_27,HV_027_01,HV_027_02,HV_027_05,HV_027_06,HV_027_07,HV_027_27,HV_028_27,HV_029_27,HV_030_27,HV_015_21,HV_027_03,HV_027_04))
CONTIGStable <- CONTIG_OTU_SUMS
```
Convert abundance into binary presence/absence 
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIGStable <- CONTIGStable %>% mutate_if(is.numeric, ~1 * (. != 0))
```
Determine contig prevalence over the five time points by location within a subject
```{r,message=FALSE,warning=FALSE,results="hide"}
#P01 Left
CONTIGStable$P01_LH <- CONTIGStable$HV_001_01 + CONTIGStable$HV_002_01 + CONTIGStable$HV_003_01 + CONTIGStable$HV_004_01 + CONTIGStable$HV_005_01
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_01,HV_002_01,HV_003_01,HV_004_01,HV_005_01 ))
#P01 Right
CONTIGStable$P01_RH <- CONTIGStable$HV_001_02 + CONTIGStable$HV_002_02 + CONTIGStable$HV_003_02 + CONTIGStable$HV_004_02
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_02,HV_002_02,HV_003_02,HV_004_02 ))
#P01 Scalp
CONTIGStable$P01_SC <- CONTIGStable$HV_001_03 + CONTIGStable$HV_004_03 + CONTIGStable$HV_003_03 + CONTIGStable$HV_005_03 + CONTIGStable$HV_002_03
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_03,HV_002_03,HV_003_03,HV_004_03,HV_005_03 ))

#P02 Left
CONTIGStable$P02_LH <- CONTIGStable$HV_001_04 + CONTIGStable$HV_002_04 + CONTIGStable$HV_003_04 + CONTIGStable$HV_004_04 + CONTIGStable$HV_005_04
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_04,HV_002_04,HV_003_04,HV_004_04,HV_005_04 ))
#P02 Right
CONTIGStable$P02_RH <- CONTIGStable$HV_001_05 + CONTIGStable$HV_002_05 + CONTIGStable$HV_003_05 + CONTIGStable$HV_004_05 + CONTIGStable$HV_005_05
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_05,HV_002_05,HV_003_05,HV_004_05,HV_005_05 ))
#P02 Scalp
CONTIGStable$P02_SC <- CONTIGStable$HV_001_06 + CONTIGStable$HV_002_06 + CONTIGStable$HV_003_06 + CONTIGStable$HV_004_06 + CONTIGStable$HV_005_06
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_06,HV_002_06,HV_003_06,HV_004_06,HV_005_06 ))

#P03 Left
CONTIGStable$P03_LH <- CONTIGStable$HV_001_07 + CONTIGStable$HV_002_07 + CONTIGStable$HV_003_07 + CONTIGStable$HV_004_07 + CONTIGStable$HV_005_07
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_07,HV_002_07,HV_003_07,HV_004_07,HV_005_07 ))
#P03 Right
CONTIGStable$P03_RH <- CONTIGStable$HV_001_08 + CONTIGStable$HV_002_08 + CONTIGStable$HV_003_08 + CONTIGStable$HV_004_08 + CONTIGStable$HV_005_08
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_08,HV_002_08,HV_003_08,HV_004_08,HV_005_08 ))
#P03 Scalp
CONTIGStable$P03_SC <- CONTIGStable$HV_001_09 + CONTIGStable$HV_002_09 + CONTIGStable$HV_003_09 + CONTIGStable$HV_004_09 + CONTIGStable$HV_005_09
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_09,HV_002_09,HV_003_09,HV_004_09,HV_005_09 ))

#P04 Left
CONTIGStable$P04_LH <- CONTIGStable$HV_001_10 + CONTIGStable$HV_002_10 + CONTIGStable$HV_003_10 + CONTIGStable$HV_004_10 + CONTIGStable$HV_005_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_10,HV_002_10,HV_003_10,HV_004_10,HV_005_10 ))
#P04 Right
CONTIGStable$P04_RH <- CONTIGStable$HV_001_11 + CONTIGStable$HV_002_11 + CONTIGStable$HV_003_11 + CONTIGStable$HV_004_11 + CONTIGStable$HV_005_11
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_11,HV_002_11,HV_003_11,HV_004_11,HV_005_11 ))
#P04 Scalp
CONTIGStable$P04_SC <- CONTIGStable$HV_001_12 + CONTIGStable$HV_002_12 + CONTIGStable$HV_003_12 + CONTIGStable$HV_004_12 + CONTIGStable$HV_005_12
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_12,HV_002_12,HV_003_12,HV_004_12,HV_005_12 ))

#P05 Left
CONTIGStable$P05_LH <- CONTIGStable$HV_001_13 + CONTIGStable$HV_002_13 + CONTIGStable$HV_003_13 + CONTIGStable$HV_004_13 + CONTIGStable$HV_005_13
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_13,HV_002_13,HV_003_13,HV_004_13,HV_005_13 ))
#P05 Right
CONTIGStable$P05_RH <- CONTIGStable$HV_001_14 + CONTIGStable$HV_002_14 + CONTIGStable$HV_003_14 + CONTIGStable$HV_004_14 + CONTIGStable$HV_005_14
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_14,HV_002_14,HV_003_14,HV_004_14,HV_005_14 ))
#P05 Scalp
CONTIGStable$P05_SC <- CONTIGStable$HV_001_15 + CONTIGStable$HV_002_15  + CONTIGStable$HV_004_15+CONTIGStable$HV_003_15 + CONTIGStable$HV_005_15
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_15,HV_002_15,HV_004_15,HV_005_15,HV_003_15 ))

#P06 Left
CONTIGStable$P06_LH <- CONTIGStable$HV_001_16 + CONTIGStable$HV_003_16 + CONTIGStable$HV_004_16 + CONTIGStable$HV_005_16
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_16,HV_003_16,HV_004_16,HV_005_16 ))
#P06 Right
CONTIGStable$P06_RH <- CONTIGStable$HV_001_18 + CONTIGStable$HV_002_18 + CONTIGStable$HV_003_18 + CONTIGStable$HV_004_18 + CONTIGStable$HV_005_18
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_18,HV_002_18,HV_003_18,HV_004_18,HV_005_18 ))
#P06 Scalp
CONTIGStable$P06_SC <- CONTIGStable$HV_001_19 + CONTIGStable$HV_002_19 + CONTIGStable$HV_003_19 + CONTIGStable$HV_004_19 + CONTIGStable$HV_005_19
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_19,HV_002_19,HV_003_19,HV_004_19,HV_005_19 ))

#P07 Left
CONTIGStable$P07_LH <- CONTIGStable$HV_001_20 + CONTIGStable$HV_002_20 + CONTIGStable$HV_003_20 + CONTIGStable$HV_004_20 + CONTIGStable$HV_005_20
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_20,HV_002_20,HV_003_20,HV_004_20,HV_005_20 ))
#P07 Right
CONTIGStable$P07_RH <- CONTIGStable$HV_001_21 + CONTIGStable$HV_002_21 + CONTIGStable$HV_003_21 + CONTIGStable$HV_004_21 
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_21,HV_002_21,HV_003_21,HV_004_21 ))
#P07 Scalp
CONTIGStable$P07_SC <- CONTIGStable$HV_001_22 + CONTIGStable$HV_002_22 + CONTIGStable$HV_003_22 + CONTIGStable$HV_004_22 + CONTIGStable$HV_005_22
CONTIGStable <- subset(CONTIGStable, select = -c(HV_001_22,HV_002_22,HV_003_22,HV_004_22,HV_005_22 ))

#P08 Left
CONTIGStable$P08_LH <- CONTIGStable$HV_006_01 + CONTIGStable$HV_007_01 + CONTIGStable$HV_008_01 + CONTIGStable$HV_009_01 + CONTIGStable$HV_010_01
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_01,HV_007_01,HV_008_01,HV_009_01,HV_010_01))
#P08 Right
CONTIGStable$P08_RH <- CONTIGStable$HV_006_02 + CONTIGStable$HV_007_02 + CONTIGStable$HV_008_02 + CONTIGStable$HV_010_02
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_02,HV_007_02,HV_008_02,HV_010_02))
#P08 Scalp
CONTIGStable$P08_SC <- CONTIGStable$HV_006_03 + CONTIGStable$HV_007_03 + CONTIGStable$HV_008_03 + CONTIGStable$HV_009_03 + CONTIGStable$HV_010_03
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_03,HV_007_03,HV_008_03,HV_009_03,HV_010_03))

#P09 Left
CONTIGStable$P09_LH <- CONTIGStable$HV_006_04 + CONTIGStable$HV_007_04 + CONTIGStable$HV_008_04 + CONTIGStable$HV_009_04 + CONTIGStable$HV_010_04
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_04,HV_007_04,HV_008_04,HV_009_04,HV_010_04))
#P09 Right
CONTIGStable$P09_RH <- CONTIGStable$HV_006_05 + CONTIGStable$HV_007_05 + CONTIGStable$HV_008_05 + CONTIGStable$HV_009_05 + CONTIGStable$HV_010_05
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_05,HV_007_05,HV_008_05,HV_009_05,HV_010_05))
#P09 Scalp
CONTIGStable$P09_SC <- CONTIGStable$HV_006_06 + CONTIGStable$HV_007_06 + CONTIGStable$HV_008_06 + CONTIGStable$HV_009_06 + CONTIGStable$HV_010_06
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_06,HV_007_06,HV_008_06,HV_009_06,HV_010_06))

#P10 Left
CONTIGStable$P10_LH <- CONTIGStable$HV_006_07 + CONTIGStable$HV_007_07 + CONTIGStable$HV_008_07 + CONTIGStable$HV_009_07 + CONTIGStable$HV_010_07
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_07,HV_007_07,HV_008_07,HV_009_07,HV_010_07))
#P10 Right
CONTIGStable$P10_RH <- CONTIGStable$HV_006_08 + CONTIGStable$HV_007_08 + CONTIGStable$HV_008_08 + CONTIGStable$HV_009_08 + CONTIGStable$HV_010_08
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_08,HV_007_08,HV_008_08,HV_009_08,HV_010_08))
#P10 Scalp
CONTIGStable$P10_SC <- CONTIGStable$HV_006_09 + CONTIGStable$HV_007_09 + CONTIGStable$HV_008_09 + CONTIGStable$HV_009_09 + CONTIGStable$HV_010_09
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_09,HV_007_09,HV_008_09,HV_009_09,HV_010_09))

#P11 Left
CONTIGStable$P11_LH <- CONTIGStable$HV_006_10 + CONTIGStable$HV_007_10 + CONTIGStable$HV_008_10 + CONTIGStable$HV_009_10 + CONTIGStable$HV_010_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_10,HV_007_10,HV_008_10,HV_009_10,HV_010_10))
#P11 Right
CONTIGStable$P11_RH <- CONTIGStable$HV_006_11 + CONTIGStable$HV_007_11 + CONTIGStable$HV_008_11 + CONTIGStable$HV_009_11 + CONTIGStable$HV_010_11
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_11,HV_007_11,HV_008_11,HV_009_11,HV_010_11))
#P11 Scalp
CONTIGStable$P11_SC <- CONTIGStable$HV_006_12 + CONTIGStable$HV_007_12 + CONTIGStable$HV_008_12 + CONTIGStable$HV_009_12 + CONTIGStable$HV_010_12
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_12,HV_007_12,HV_008_12,HV_009_12,HV_010_12))

#P12 Left
CONTIGStable$P12_LH <- CONTIGStable$HV_006_13 + CONTIGStable$HV_007_13 + CONTIGStable$HV_008_13 + CONTIGStable$HV_009_13 + CONTIGStable$HV_010_13
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_13,HV_007_13,HV_008_13,HV_009_13,HV_010_13))
#P12 Right
CONTIGStable$P12_RH <- CONTIGStable$HV_006_14 + CONTIGStable$HV_007_14 + CONTIGStable$HV_008_14 + CONTIGStable$HV_009_14 + CONTIGStable$HV_010_14
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_14,HV_007_14,HV_008_14,HV_009_14,HV_010_14))
#P12 Scalp
CONTIGStable$P12_SC <- CONTIGStable$HV_006_15 + CONTIGStable$HV_007_15 + CONTIGStable$HV_008_15 + CONTIGStable$HV_009_15 + CONTIGStable$HV_010_15
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_15,HV_007_15,HV_008_15,HV_009_15,HV_010_15))

#P13 Left
CONTIGStable$P13_LH <- CONTIGStable$HV_006_16 + CONTIGStable$HV_007_16 + CONTIGStable$HV_008_16 + CONTIGStable$HV_009_16 + CONTIGStable$HV_010_16
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_16,HV_007_16,HV_008_16,HV_009_16,HV_010_16))
#P13 Right
CONTIGStable$P13_RH <- CONTIGStable$HV_006_18 + CONTIGStable$HV_007_18 + CONTIGStable$HV_008_18 + CONTIGStable$HV_009_18 + CONTIGStable$HV_010_18
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_18,HV_007_18,HV_008_18,HV_009_18,HV_010_18))
#P13 Scalp
CONTIGStable$P13_SC <- CONTIGStable$HV_006_19 + CONTIGStable$HV_007_19 + CONTIGStable$HV_008_19 + CONTIGStable$HV_009_19 + CONTIGStable$HV_010_19
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_19,HV_007_19,HV_008_19,HV_009_19,HV_010_19))

#P14 Left
CONTIGStable$P14_LH <- CONTIGStable$HV_006_20 + CONTIGStable$HV_007_20 + CONTIGStable$HV_008_20 + CONTIGStable$HV_009_20 + CONTIGStable$HV_010_20
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_20,HV_007_20,HV_008_20,HV_009_20,HV_010_20))
#P14 Right
CONTIGStable$P14_RH <- CONTIGStable$HV_006_21 + CONTIGStable$HV_007_21 + CONTIGStable$HV_008_21 + CONTIGStable$HV_009_21 + CONTIGStable$HV_010_21
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_21,HV_007_21,HV_008_21,HV_009_21,HV_010_21))
#P14 Scalp
CONTIGStable$P14_SC <- CONTIGStable$HV_006_22 + CONTIGStable$HV_007_22 + CONTIGStable$HV_008_22 + CONTIGStable$HV_009_22 + CONTIGStable$HV_010_22
CONTIGStable <- subset(CONTIGStable, select = -c(HV_006_22,HV_007_22,HV_008_22,HV_009_22,HV_010_22))

#P15 Left
CONTIGStable$P15_LH <- CONTIGStable$HV_011_01 + CONTIGStable$HV_012_01 + CONTIGStable$HV_013_01 + CONTIGStable$HV_014_01 + CONTIGStable$HV_015_01
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_01,HV_012_01,HV_013_01,HV_014_01,HV_015_01))
#P15 Right
CONTIGStable$P15_RH <- CONTIGStable$HV_011_02 + CONTIGStable$HV_012_02 + CONTIGStable$HV_013_02 + CONTIGStable$HV_014_02 + CONTIGStable$HV_015_02
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_02,HV_012_02,HV_013_02,HV_014_02,HV_015_02))
#P15 Scalp
CONTIGStable$P15_SC <- CONTIGStable$HV_011_03 + CONTIGStable$HV_012_03 + CONTIGStable$HV_013_03 + CONTIGStable$HV_014_03 + CONTIGStable$HV_015_03
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_03,HV_012_03,HV_013_03,HV_014_03,HV_015_03))

#P16 Left
CONTIGStable$P16_LH <- CONTIGStable$HV_011_04 + CONTIGStable$HV_012_04 + CONTIGStable$HV_013_04 + CONTIGStable$HV_014_04 + CONTIGStable$HV_015_04
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_04,HV_012_04,HV_013_04,HV_014_04,HV_015_04))
#P16 Right
CONTIGStable$P16_RH <- CONTIGStable$HV_011_05 + CONTIGStable$HV_012_05 + CONTIGStable$HV_013_05 + CONTIGStable$HV_014_05 + CONTIGStable$HV_015_05
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_05,HV_012_05,HV_013_05,HV_014_05,HV_015_05))
#P16 Scalp
CONTIGStable$P16_SC <- CONTIGStable$HV_011_06 + CONTIGStable$HV_012_06 ++ CONTIGStable$HV_014_06 + CONTIGStable$HV_015_06
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_06,HV_012_06,HV_014_06,HV_015_06))

#P17 Left
CONTIGStable$P17_LH <- CONTIGStable$HV_011_07 + CONTIGStable$HV_012_07 + CONTIGStable$HV_013_07 + CONTIGStable$HV_014_07 + CONTIGStable$HV_015_07
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_07,HV_012_07,HV_013_07,HV_014_07,HV_015_07))
#P17 Right
CONTIGStable$P17_RH <- CONTIGStable$HV_011_08 + CONTIGStable$HV_012_08 + CONTIGStable$HV_013_08 + CONTIGStable$HV_014_08 + CONTIGStable$HV_015_08
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_08,HV_012_08,HV_013_08,HV_014_08,HV_015_08))
#P17 Scalp
CONTIGStable$P17_SC <- CONTIGStable$HV_011_09 + CONTIGStable$HV_012_09 + CONTIGStable$HV_013_09 + CONTIGStable$HV_014_09 + CONTIGStable$HV_015_09
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_09,HV_012_09,HV_013_09,HV_014_09,HV_015_09))

#P18 Left
CONTIGStable$P18_LH <- CONTIGStable$HV_011_10 + CONTIGStable$HV_012_10 + CONTIGStable$HV_013_10 + CONTIGStable$HV_014_10 + CONTIGStable$HV_015_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_10,HV_012_10,HV_013_10,HV_014_10,HV_015_10))
#P18 Right
CONTIGStable$P18_RH <- CONTIGStable$HV_011_11 + CONTIGStable$HV_012_11 + CONTIGStable$HV_013_11 + CONTIGStable$HV_014_11 + CONTIGStable$HV_015_11
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_11,HV_012_11,HV_013_11,HV_014_11,HV_015_11))
#P18 Scalp
CONTIGStable$P18_SC <- CONTIGStable$HV_011_12 + CONTIGStable$HV_012_12 + CONTIGStable$HV_013_12 + CONTIGStable$HV_014_12 + CONTIGStable$HV_015_12
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_12,HV_012_12,HV_013_12,HV_014_12,HV_015_12))

#P19 Left
CONTIGStable$P19_LH <- CONTIGStable$HV_011_13 + CONTIGStable$HV_012_13 + CONTIGStable$HV_013_13 + CONTIGStable$HV_014_13 + CONTIGStable$HV_015_13
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_13,HV_012_13,HV_013_13,HV_014_13,HV_015_13))
#P19 Right
CONTIGStable$P19_RH <- CONTIGStable$HV_011_14 + CONTIGStable$HV_012_14 + CONTIGStable$HV_013_14 + CONTIGStable$HV_014_14 + CONTIGStable$HV_015_14
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_14,HV_012_14,HV_013_14,HV_014_14,HV_015_14))
#P19 Scalp
CONTIGStable$P19_SC <- CONTIGStable$HV_011_15 + CONTIGStable$HV_012_15 + CONTIGStable$HV_013_15 + CONTIGStable$HV_014_15 + CONTIGStable$HV_015_15
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_15,HV_012_15,HV_013_15,HV_014_15,HV_015_15))

#P20 Left
CONTIGStable$P20_LH <- CONTIGStable$HV_011_16 + CONTIGStable$HV_012_16 + CONTIGStable$HV_013_16 + CONTIGStable$HV_014_16 + CONTIGStable$HV_015_16
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_16,HV_012_16,HV_013_16,HV_014_16,HV_015_16))
#P20 Right
CONTIGStable$P20_RH <- CONTIGStable$HV_011_18 + CONTIGStable$HV_012_18 + CONTIGStable$HV_013_18 + CONTIGStable$HV_014_18 + CONTIGStable$HV_015_18
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_18,HV_012_18,HV_013_18,HV_014_18,HV_015_18))
#P20 Scalp
CONTIGStable$P20_SC <- CONTIGStable$HV_011_19 + CONTIGStable$HV_012_19 + CONTIGStable$HV_013_19 + CONTIGStable$HV_014_19 + CONTIGStable$HV_015_19
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_19,HV_012_19,HV_013_19,HV_014_19,HV_015_19))

#P21 Left
CONTIGStable$P21_LH <- CONTIGStable$HV_011_20 + CONTIGStable$HV_012_20 + CONTIGStable$HV_013_20 + CONTIGStable$HV_014_20
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_20,HV_012_20,HV_013_20,HV_014_20))
#P21 Right
CONTIGStable$P21_RH <- CONTIGStable$HV_011_21 + CONTIGStable$HV_012_21 + CONTIGStable$HV_013_21 + CONTIGStable$HV_014_21
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_21,HV_012_21,HV_013_21,HV_014_21))
#P21 Scalp
CONTIGStable$P21_SC <- CONTIGStable$HV_011_22 + CONTIGStable$HV_012_22 + CONTIGStable$HV_013_22 + CONTIGStable$HV_014_22
CONTIGStable <- subset(CONTIGStable, select = -c(HV_011_22,HV_012_22,HV_013_22,HV_014_22))

#P22 Left
CONTIGStable$P22_LH <- CONTIGStable$HV_021_02 + CONTIGStable$HV_022_01 + CONTIGStable$HV_023_01 + CONTIGStable$HV_024_01 + CONTIGStable$HV_025_02
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_02,HV_022_01,HV_023_01,HV_024_01,HV_025_02))
#P22 Right
CONTIGStable$P22_RH <- CONTIGStable$HV_026_01 + CONTIGStable$HV_027_08 + CONTIGStable$HV_028_01 + CONTIGStable$HV_029_01 + CONTIGStable$HV_030_01
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_01,HV_027_08,HV_028_01,HV_029_01,HV_030_01))
#P22 Scalp
CONTIGStable$P22_SC <- CONTIGStable$HV_016_01 + CONTIGStable$HV_017_01 + CONTIGStable$HV_018_01 + CONTIGStable$HV_019_01 + CONTIGStable$HV_020_01
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_01,HV_017_01,HV_018_01,HV_019_01,HV_020_01))

#P23 Left
CONTIGStable$P23_LH <- CONTIGStable$HV_021_03 + CONTIGStable$HV_022_02 + CONTIGStable$HV_023_02 + CONTIGStable$HV_024_02 + CONTIGStable$HV_025_03
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_03,HV_022_02,HV_023_02,HV_024_02,HV_025_03))
#P23 Right
CONTIGStable$P23_RH <- CONTIGStable$HV_026_02 + CONTIGStable$HV_027_09 + CONTIGStable$HV_028_02 + CONTIGStable$HV_029_02 + CONTIGStable$HV_030_02
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_02,HV_027_09,HV_028_02,HV_029_02,HV_030_02))
#P23 Scalp
CONTIGStable$P23_SC <- CONTIGStable$HV_016_02 + CONTIGStable$HV_017_02 + CONTIGStable$HV_018_02 + CONTIGStable$HV_019_02 + CONTIGStable$HV_020_02
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_02,HV_017_02,HV_018_02,HV_019_02,HV_020_02))

#P24 Left
CONTIGStable$P24_LH <- CONTIGStable$HV_021_04 + CONTIGStable$HV_022_03 + CONTIGStable$HV_023_03 + CONTIGStable$HV_024_03 + CONTIGStable$HV_025_04
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_04,HV_022_03,HV_023_03,HV_024_03,HV_025_04))
#P24 Right
CONTIGStable$P24_RH <- CONTIGStable$HV_026_03 + CONTIGStable$HV_027_10 + CONTIGStable$HV_028_03 + CONTIGStable$HV_029_03 + CONTIGStable$HV_030_03
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_03,HV_027_10,HV_028_03,HV_029_03,HV_030_03))
#P24 Scalp
CONTIGStable$P24_SC <- CONTIGStable$HV_016_03 + CONTIGStable$HV_017_03 + CONTIGStable$HV_018_03 + CONTIGStable$HV_019_03 + CONTIGStable$HV_021_01
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_03,HV_017_03,HV_018_03,HV_019_03,HV_021_01))

#P25 Left
CONTIGStable$P25_LH <- CONTIGStable$HV_021_05 + CONTIGStable$HV_022_04 + CONTIGStable$HV_023_04 + CONTIGStable$HV_024_04 + CONTIGStable$HV_025_05
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_05,HV_022_04,HV_023_04,HV_024_04,HV_025_05))
#P25 Right
CONTIGStable$P25_RH <- CONTIGStable$HV_026_04 + CONTIGStable$HV_027_11 + CONTIGStable$HV_028_04 + CONTIGStable$HV_029_04 + CONTIGStable$HV_030_04
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_04,HV_027_11,HV_028_04,HV_029_04,HV_030_04))
#P25 Scalp
CONTIGStable$P25_SC <- CONTIGStable$HV_016_04 + CONTIGStable$HV_017_04 + CONTIGStable$HV_018_04 + CONTIGStable$HV_019_04 + CONTIGStable$HV_020_03
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_04,HV_017_04,HV_018_04,HV_019_04,HV_020_03))

#P26 Left
CONTIGStable$P26_LH <- CONTIGStable$HV_021_06 + CONTIGStable$HV_022_05 + CONTIGStable$HV_023_05 + CONTIGStable$HV_024_05 + CONTIGStable$HV_025_06
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_06,HV_022_05,HV_023_05,HV_024_05,HV_025_06))
#P26 Right
CONTIGStable$P26_RH <- CONTIGStable$HV_026_05 + CONTIGStable$HV_027_12 + CONTIGStable$HV_028_05 + CONTIGStable$HV_029_05 + CONTIGStable$HV_030_05
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_05,HV_027_12,HV_028_05,HV_029_05,HV_030_05))
#P26 Scalp
CONTIGStable$P26_SC <- CONTIGStable$HV_016_05 + CONTIGStable$HV_017_05 + CONTIGStable$HV_018_05 + CONTIGStable$HV_019_05 + CONTIGStable$HV_020_04
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_05,HV_017_05,HV_018_05,HV_019_05,HV_020_04))

#P27 Left
CONTIGStable$P27_LH <- CONTIGStable$HV_021_07 + CONTIGStable$HV_022_06 + CONTIGStable$HV_023_06 + CONTIGStable$HV_024_06 + CONTIGStable$HV_025_07
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_07,HV_022_06,HV_023_06,HV_024_06,HV_025_07))
#P27 Right
CONTIGStable$P27_RH <- CONTIGStable$HV_026_06 + CONTIGStable$HV_027_13 + CONTIGStable$HV_028_06 + CONTIGStable$HV_029_06 + CONTIGStable$HV_030_06
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_06,HV_027_13,HV_028_06,HV_029_06,HV_030_06))
#P27 Scalp
CONTIGStable$P27_SC <- CONTIGStable$HV_016_06 + CONTIGStable$HV_017_06 + CONTIGStable$HV_018_06 + CONTIGStable$HV_019_06 + CONTIGStable$HV_020_05
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_06,HV_017_06,HV_018_06,HV_019_06,HV_020_05))

#P28 Left
CONTIGStable$P28_LH <- CONTIGStable$HV_021_08 + CONTIGStable$HV_022_07 + CONTIGStable$HV_023_07 + CONTIGStable$HV_024_07 + CONTIGStable$HV_025_08
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_08,HV_022_07,HV_023_07,HV_024_07,HV_025_08))
#P28 Right
CONTIGStable$P28_RH <- CONTIGStable$HV_026_07 + CONTIGStable$HV_027_14 + CONTIGStable$HV_028_07 + CONTIGStable$HV_029_07 + CONTIGStable$HV_030_07
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_07,HV_027_14,HV_028_07,HV_029_07,HV_030_07))
#P28 Scalp
CONTIGStable$P28_SC <- CONTIGStable$HV_016_07 + CONTIGStable$HV_017_07 + CONTIGStable$HV_018_07 + CONTIGStable$HV_019_07 + CONTIGStable$HV_020_06
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_07,HV_017_07,HV_018_07,HV_019_07,HV_020_06))

#P29 Left
CONTIGStable$P29_LH <- CONTIGStable$HV_021_09 + CONTIGStable$HV_022_08 + CONTIGStable$HV_023_08 + CONTIGStable$HV_024_08 + CONTIGStable$HV_025_09
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_09,HV_022_08,HV_023_08,HV_024_08,HV_025_09))
#P29 Right
CONTIGStable$P29_RH <- CONTIGStable$HV_026_08 + CONTIGStable$HV_027_15 + CONTIGStable$HV_028_08 + CONTIGStable$HV_029_08 + CONTIGStable$HV_030_08
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_08,HV_027_15,HV_028_08,HV_029_08,HV_030_08))
#P29 Scalp
CONTIGStable$P29_SC <- CONTIGStable$HV_016_08 + CONTIGStable$HV_017_08 + CONTIGStable$HV_018_08 + CONTIGStable$HV_019_08 + CONTIGStable$HV_020_07
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_08,HV_017_08,HV_018_08,HV_019_08,HV_020_07))

#P30 Left
CONTIGStable$P30_LH <- CONTIGStable$HV_021_10 + CONTIGStable$HV_022_09 + CONTIGStable$HV_023_09 + CONTIGStable$HV_024_09 + CONTIGStable$HV_025_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_10,HV_022_09,HV_023_09,HV_024_09,HV_025_10))
#P30 Right
CONTIGStable$P30_RH <- CONTIGStable$HV_026_09 + CONTIGStable$HV_027_16 + CONTIGStable$HV_028_09 + CONTIGStable$HV_029_09 + CONTIGStable$HV_030_09
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_09,HV_027_16,HV_028_09,HV_029_09,HV_030_09))
#P30 Scalp
CONTIGStable$P30_SC <- CONTIGStable$HV_016_09 + CONTIGStable$HV_017_09 + CONTIGStable$HV_018_09 + CONTIGStable$HV_019_09 + CONTIGStable$HV_020_08
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_09,HV_017_09,HV_018_09,HV_019_09,HV_020_08))

#P31 Left
CONTIGStable$P31_LH <- CONTIGStable$HV_021_11 + CONTIGStable$HV_022_10 + CONTIGStable$HV_023_10 + CONTIGStable$HV_024_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_11,HV_022_10,HV_023_10,HV_024_10))
#P31 Right
CONTIGStable$P31_RH <- CONTIGStable$HV_026_10 + CONTIGStable$HV_027_18 + CONTIGStable$HV_028_10 + CONTIGStable$HV_029_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_10,HV_027_18,HV_028_10,HV_029_10))
#P31 Scalp
CONTIGStable$P31_SC <- CONTIGStable$HV_016_10 + CONTIGStable$HV_017_10 + CONTIGStable$HV_018_10 + CONTIGStable$HV_019_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_10,HV_017_10,HV_018_10,HV_019_10))

#P32 Left
CONTIGStable$P32_LH <- CONTIGStable$HV_021_12 + CONTIGStable$HV_022_11 + CONTIGStable$HV_023_11 + CONTIGStable$HV_024_11 + CONTIGStable$HV_025_11
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_12,HV_022_11,HV_023_11,HV_024_11,HV_025_11))
#P32 Right
CONTIGStable$P32_RH <- CONTIGStable$HV_026_11 + CONTIGStable$HV_027_19 + CONTIGStable$HV_028_11 + CONTIGStable$HV_029_11 + CONTIGStable$HV_030_10
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_11,HV_027_19,HV_028_11,HV_029_11,HV_030_10))
#P32 Scalp
CONTIGStable$P32_SC <- CONTIGStable$HV_016_11 + CONTIGStable$HV_017_11 + CONTIGStable$HV_018_11 + CONTIGStable$HV_019_11 + CONTIGStable$HV_020_09
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_11,HV_017_11,HV_018_11,HV_019_11,HV_020_09))

#P34 Left
CONTIGStable$P34_LH <- CONTIGStable$HV_021_14 + CONTIGStable$HV_022_12 + CONTIGStable$HV_023_12 + CONTIGStable$HV_024_12 + CONTIGStable$HV_025_12
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_14,HV_022_12,HV_023_12,HV_024_12,HV_025_12))
#P34 Right
CONTIGStable$P34_RH <- CONTIGStable$HV_026_12 + CONTIGStable$HV_027_20 + CONTIGStable$HV_028_12 + CONTIGStable$HV_029_12 + CONTIGStable$HV_030_11
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_12,HV_027_20,HV_028_12,HV_029_12,HV_030_11))
#P34 Scalp
CONTIGStable$P34_SC <- CONTIGStable$HV_016_12 + CONTIGStable$HV_017_12 + CONTIGStable$HV_018_12 + CONTIGStable$HV_019_12 + CONTIGStable$HV_020_11
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_12,HV_017_12,HV_018_12,HV_019_12,HV_020_11))

#P35 Left
CONTIGStable$P35_LH <- CONTIGStable$HV_021_15 + CONTIGStable$HV_022_13 + CONTIGStable$HV_023_13 + CONTIGStable$HV_024_13 + CONTIGStable$HV_025_13
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_15,HV_022_13,HV_023_13,HV_024_13,HV_025_13))
#P35 Right
CONTIGStable$P35_RH <- CONTIGStable$HV_026_13 + CONTIGStable$HV_027_21 + CONTIGStable$HV_028_13 + CONTIGStable$HV_029_13 + CONTIGStable$HV_030_12
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_13,HV_027_21,HV_028_13,HV_029_13,HV_030_12))
#P35 Scalp
CONTIGStable$P35_SC <- CONTIGStable$HV_016_13 + CONTIGStable$HV_017_13 + CONTIGStable$HV_018_13 + CONTIGStable$HV_019_13 + CONTIGStable$HV_020_12
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_13,HV_017_13,HV_018_13,HV_019_13,HV_020_12))

#P36 Left
CONTIGStable$P36_LH <- CONTIGStable$HV_021_16 + CONTIGStable$HV_022_14 + CONTIGStable$HV_023_14 + CONTIGStable$HV_024_14 + CONTIGStable$HV_025_14
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_16,HV_022_14,HV_023_14,HV_024_14,HV_025_14))
#P36 Right
CONTIGStable$P36_RH <- CONTIGStable$HV_026_14 + CONTIGStable$HV_027_22 + CONTIGStable$HV_028_14 + CONTIGStable$HV_029_14 + CONTIGStable$HV_030_13
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_14,HV_027_22,HV_028_14,HV_029_14,HV_030_13))
#P36 Scalp
CONTIGStable$P36_SC <- CONTIGStable$HV_016_14 + CONTIGStable$HV_017_14 + CONTIGStable$HV_018_14 + CONTIGStable$HV_019_14 + CONTIGStable$HV_020_13
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_14,HV_017_14,HV_018_14,HV_019_14,HV_020_13))

#P37 Left
CONTIGStable$P37_LH <- CONTIGStable$HV_021_18 + CONTIGStable$HV_022_15 + CONTIGStable$HV_023_15 + CONTIGStable$HV_024_15 + CONTIGStable$HV_025_15
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_18,HV_022_15,HV_023_15,HV_024_15,HV_025_15))
#P37 Right
CONTIGStable$P37_RH <- CONTIGStable$HV_026_15 + CONTIGStable$HV_028_15 + CONTIGStable$HV_029_15 + CONTIGStable$HV_030_14 + CONTIGStable$HV_030_22
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_15,HV_028_15,HV_029_15,HV_030_14,HV_030_22))
#P37 Scalp
CONTIGStable$P37_SC <- CONTIGStable$HV_016_15 + CONTIGStable$HV_017_15 + CONTIGStable$HV_018_15 + CONTIGStable$HV_019_15 + CONTIGStable$HV_020_14
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_15,HV_017_15,HV_018_15,HV_019_15,HV_020_14))

#P38 Left
CONTIGStable$P38_LH <- CONTIGStable$HV_021_19 + CONTIGStable$HV_022_16 + CONTIGStable$HV_023_16 + CONTIGStable$HV_024_16 + CONTIGStable$HV_025_16
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_19,HV_022_16,HV_023_16,HV_024_16,HV_025_16))
#P38 Right
CONTIGStable$P38_RH <- CONTIGStable$HV_026_16 + CONTIGStable$HV_028_16 + CONTIGStable$HV_029_16 + CONTIGStable$HV_030_15 
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_16,HV_028_16,HV_029_16,HV_030_15))
#P38 Scalp
CONTIGStable$P38_SC <- CONTIGStable$HV_016_16 + CONTIGStable$HV_017_16 + CONTIGStable$HV_018_16 + CONTIGStable$HV_019_16 + CONTIGStable$HV_020_15
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_16,HV_017_16,HV_018_16,HV_019_16,HV_020_15))

#P39 Left
CONTIGStable$P39_LH <- CONTIGStable$HV_021_20 + CONTIGStable$HV_022_18 + CONTIGStable$HV_023_18 + CONTIGStable$HV_024_18 + CONTIGStable$HV_025_18
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_20,HV_022_18,HV_023_18,HV_024_18,HV_025_18))
#P39 Right
CONTIGStable$P39_RH <- CONTIGStable$HV_026_18 + CONTIGStable$HV_028_18 + CONTIGStable$HV_029_18 + CONTIGStable$HV_030_16
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_18,HV_028_18,HV_029_18,HV_030_16))
#P39 Scalp
CONTIGStable$P39_SC <- CONTIGStable$HV_016_18 + CONTIGStable$HV_017_18 + CONTIGStable$HV_018_18 + CONTIGStable$HV_019_18 + CONTIGStable$HV_020_16
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_18,HV_017_18,HV_018_18,HV_019_18,HV_020_16))

#P40 Left
CONTIGStable$P40_LH <- CONTIGStable$HV_021_21 + CONTIGStable$HV_022_19 + CONTIGStable$HV_023_19 + CONTIGStable$HV_024_19 + CONTIGStable$HV_025_19
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_21,HV_022_19,HV_023_19,HV_024_19,HV_025_19))
#P40 Right
CONTIGStable$P40_RH <- CONTIGStable$HV_026_19 + CONTIGStable$HV_028_19 + CONTIGStable$HV_029_19 + CONTIGStable$HV_030_18
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_19,HV_028_19,HV_029_19,HV_030_18))
#P40 Scalp
CONTIGStable$P40_SC <- CONTIGStable$HV_016_19 + CONTIGStable$HV_017_19 + CONTIGStable$HV_018_19 + CONTIGStable$HV_019_19 + CONTIGStable$HV_020_18
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_19,HV_017_19,HV_018_19,HV_019_19,HV_020_18))

#P41 Left
CONTIGStable$P41_LH <- CONTIGStable$HV_021_22 + CONTIGStable$HV_022_20 + CONTIGStable$HV_023_20 + CONTIGStable$HV_024_20 + CONTIGStable$HV_025_20
CONTIGStable <- subset(CONTIGStable, select = -c(HV_021_22,HV_022_20,HV_023_20,HV_024_20,HV_025_20))
#P41 Right
CONTIGStable$P41_RH <- CONTIGStable$HV_026_20 + CONTIGStable$HV_028_20 + CONTIGStable$HV_029_20 + CONTIGStable$HV_030_19
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_20,HV_028_20,HV_029_20,HV_030_19))
#P41 Scalp
CONTIGStable$P41_SC <- CONTIGStable$HV_016_20 + CONTIGStable$HV_017_20 + CONTIGStable$HV_018_20 + CONTIGStable$HV_019_20 + CONTIGStable$HV_020_19
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_20,HV_017_20,HV_018_20,HV_019_20,HV_020_19))

#P42 Left
CONTIGStable$P42_LH <- CONTIGStable$HV_022_21 + CONTIGStable$HV_023_21 + CONTIGStable$HV_024_21 + CONTIGStable$HV_025_21 
CONTIGStable <- subset(CONTIGStable, select = -c(HV_022_21,HV_023_21,HV_024_21,HV_025_21))
#P42 Right
CONTIGStable$P42_RH <- CONTIGStable$HV_026_21 + CONTIGStable$HV_028_21 + CONTIGStable$HV_029_21 + CONTIGStable$HV_030_20
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_21,HV_028_21,HV_029_21,HV_030_20))
#P42 Scalp
CONTIGStable$P42_SC <- CONTIGStable$HV_016_21 + CONTIGStable$HV_017_21 + CONTIGStable$HV_018_21 + CONTIGStable$HV_019_21 + CONTIGStable$HV_020_20
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_21,HV_017_21,HV_018_21,HV_019_21,HV_020_20))

#P43 Left
CONTIGStable$P43_LH <- CONTIGStable$HV_022_22 + CONTIGStable$HV_023_22 + CONTIGStable$HV_024_22 + CONTIGStable$HV_025_01 + CONTIGStable$HV_025_22
CONTIGStable <- subset(CONTIGStable, select = -c(HV_022_22,HV_023_22,HV_024_22,HV_025_01,HV_025_22))
#P43 Right
CONTIGStable$P43_RH <- CONTIGStable$HV_026_22 + CONTIGStable$HV_028_22 + CONTIGStable$HV_029_22 + CONTIGStable$HV_030_21
CONTIGStable <- subset(CONTIGStable, select = -c(HV_026_22,HV_028_22,HV_029_22,HV_030_21))
#P43 Scalp
CONTIGStable$P43_SC <- CONTIGStable$HV_016_22 + CONTIGStable$HV_017_22 + CONTIGStable$HV_018_22 + CONTIGStable$HV_019_22 + CONTIGStable$HV_020_21
CONTIGStable <- subset(CONTIGStable, select = -c(HV_016_22,HV_017_22,HV_018_22,HV_019_22,HV_020_21))
```

## Set C Stable Left Hand Contigs
Subset by left hand and identify contigs that are persistent across 4 out of the 5 time points by subject
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_OTU_LH <- subset(CONTIGStable, select = c(P01_LH,P02_LH,P03_LH,P04_LH,P05_LH,P06_LH,P07_LH,P08_LH,P09_LH,P10_LH,P11_LH,P12_LH,P13_LH,P14_LH,P15_LH,P16_LH, P17_LH,P18_LH,P19_LH,P20_LH,P21_LH,P22_LH,P23_LH,P24_LH,P25_LH,P26_LH,P27_LH,P28_LH,P29_LH,P30_LH,P31_LH,P32_LH,P34_LH,P35_LH,P36_LH,P37_LH,P38_LH,P39_LH,P40_LH,P41_LH,P42_LH,P43_LH,Species))
row.names(CONTIG_OTU_LH) <- CONTIG_OTU_LH$Species
CONTIG_OTU_ALL_LH <- CONTIG_OTU_LH %>% mutate_if(is.numeric, ~1 * (. != 0))
row.names(CONTIG_OTU_ALL_LH) <- CONTIG_OTU_ALL_LH$Species
CONTIG_OTU_ALL_LH <- subset (CONTIG_OTU_ALL_LH, select = -c(Species))
CONTIG_OTU_ALL_LH$Mean <- rowMeans(CONTIG_OTU_ALL_LH)
CONTIG_OTU_ALL_LH$Species <- row.names(CONTIG_OTU_ALL_LH)
CONTIGStable_LH <- CONTIG_OTU_LH %>% mutate_if(is.numeric, ~1 * (. > 3 ))
row.names(CONTIGStable_LH) <- CONTIGStable_LH$Species
CONTIGStable_LH <- subset (CONTIGStable_LH, select = -c(Species))
CONTIGStable_LH$Mean_Stable <- rowMeans(CONTIGStable_LH)
CONTIGStable_LH$Species <- row.names(CONTIGStable_LH)
CONTIG_OTU_LH_Compare<- subset (CONTIGStable_LH, select = c(Mean_Stable,Species))
CONTIG_OTU_LH_Compare<- merge(CONTIG_OTU_ALL_LH, CONTIG_OTU_LH_Compare, by= "Species")
CONTIG_OTU_LH_Compare$Mean_temp <- CONTIG_OTU_LH_Compare$Mean - CONTIG_OTU_LH_Compare$Mean_Stable
CONTIG_LH_Stable2 <- subset(CONTIG_OTU_LH_Compare, 0 < Mean_Stable)
CONTIG_LH_Markers2 <- CONTIG_LH_Stable2$Species
```
Left hand contig markers that are stable over time 
```{r}
CONTIG_LH_Markers2
```

## Set C Stable Right Hand Contigs
Subset by right hand and identify contigs that are persistent across 4 out of the 5 time points by subject
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_OTU_RH <- subset(CONTIGStable, select = c(P01_RH,P02_RH,P03_RH,P04_RH,P05_RH,P06_RH,P07_RH,P08_RH,P09_RH,P10_RH,P11_RH,P12_RH,P13_RH,P14_RH,P15_RH,P16_RH, P17_RH,P18_RH,P19_RH,P20_RH,P21_RH,P22_RH,P23_RH,P24_RH,P25_RH,P26_RH,P27_RH,P28_RH,P29_RH,P30_RH,P31_RH,P32_RH,P34_RH,P35_RH,P36_RH,P37_RH,P38_RH,P39_RH,P40_RH,P41_RH,P42_RH,P43_RH,Species))
row.names(CONTIG_OTU_RH) <- CONTIG_OTU_RH$Species
CONTIG_OTU_ALL_RH <- CONTIG_OTU_RH %>% mutate_if(is.numeric, ~1 * (. != 0))
row.names(CONTIG_OTU_ALL_RH) <- CONTIG_OTU_ALL_RH$Species
CONTIG_OTU_ALL_RH <- subset (CONTIG_OTU_ALL_RH, select = -c(Species))
CONTIG_OTU_ALL_RH$Mean <- rowMeans(CONTIG_OTU_ALL_RH)
CONTIG_OTU_ALL_RH$Species <- row.names(CONTIG_OTU_ALL_RH)
CONTIGStable_RH <- CONTIG_OTU_RH %>% mutate_if(is.numeric, ~1 * (. > 3 ))
row.names(CONTIGStable_RH) <- CONTIGStable_RH$Species
CONTIGStable_RH <- subset (CONTIGStable_RH, select = -c(Species))
CONTIGStable_RH$Mean_Stable <- rowMeans(CONTIGStable_RH)
CONTIGStable_RH$Species <- row.names(CONTIGStable_RH)
CONTIG_OTU_RH_Compare<- subset (CONTIGStable_RH, select = c(Mean_Stable,Species))
CONTIG_OTU_RH_Compare<- merge(CONTIG_OTU_ALL_RH, CONTIG_OTU_RH_Compare, by= "Species")
CONTIG_OTU_RH_Compare$Mean_temp <- CONTIG_OTU_RH_Compare$Mean - CONTIG_OTU_RH_Compare$Mean_Stable
CONTIG_RH_Stable2 <- subset(CONTIG_OTU_RH_Compare, 0 < Mean_Stable)
CONTIG_RH_Markers2 <- CONTIG_RH_Stable2$Species
```
Right hand contig markers that are stable over time 
```{r}
CONTIG_RH_Markers2
```

## Set C Stable Scalp Contigs
Subset by scalp and identify contigs that are persistent across 4 out of the 5 time points by subject
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_OTU_SC <- subset(CONTIGStable, select = c(P01_SC,P02_SC,P03_SC,P04_SC,P05_SC,P06_SC,P07_SC,P08_SC,P09_SC,P10_SC,P11_SC,P12_SC,P13_SC,P14_SC,P15_SC,P16_SC, P17_SC,P18_SC,P19_SC,P20_SC,P21_SC,P22_SC,P23_SC,P24_SC,P25_SC,P26_SC,P27_SC,P28_SC,P29_SC,P30_SC,P31_SC,P32_SC,P34_SC,P35_SC,P36_SC,P37_SC,P38_SC,P39_SC,P40_SC,P41_SC,P42_SC,P43_SC,Species))
row.names(CONTIG_OTU_SC) <- CONTIG_OTU_SC$Species
CONTIG_OTU_ALL_SC <- CONTIG_OTU_SC %>% mutate_if(is.numeric, ~1 * (. != 0))
row.names(CONTIG_OTU_ALL_SC) <- CONTIG_OTU_ALL_SC$Species
CONTIG_OTU_ALL_SC <- subset (CONTIG_OTU_ALL_SC, select = -c(Species))
CONTIG_OTU_ALL_SC$Mean <- rowMeans(CONTIG_OTU_ALL_SC)
CONTIG_OTU_ALL_SC$Species <- row.names(CONTIG_OTU_ALL_SC)
CONTIGStable_SC <- CONTIG_OTU_SC %>% mutate_if(is.numeric, ~1 * (. > 3 ))
row.names(CONTIGStable_SC) <- CONTIGStable_SC$Species
CONTIGStable_SC <- subset (CONTIGStable_SC, select = -c(Species))
CONTIGStable_SC$Mean_Stable <- rowMeans(CONTIGStable_SC)
CONTIGStable_SC$Species <- row.names(CONTIGStable_SC)
CONTIG_OTU_SC_Compare<- subset (CONTIGStable_SC, select = c(Mean_Stable,Species))
CONTIG_OTU_SC_Compare<- merge(CONTIG_OTU_ALL_SC, CONTIG_OTU_SC_Compare, by= "Species")
CONTIG_OTU_SC_Compare$Mean_temp <- CONTIG_OTU_SC_Compare$Mean - CONTIG_OTU_SC_Compare$Mean_Stable
CONTIG_SC_Stable2 <- subset(CONTIG_OTU_SC_Compare, 0 < Mean_Stable)
CONTIG_SC_Markers2 <- CONTIG_SC_Stable2$Species
```
Scalp contig markers that are stable over time 
```{r}
CONTIG_SC_Markers2
```

## Set C Stable Hand Contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_Hand_Markers_Shared2 <- CONTIG_LH_Markers2[CONTIG_LH_Markers2 %in% CONTIG_RH_Markers2]
```
Hand Stable Contig Markers
```{r}
CONTIG_Hand_Markers_Shared2
```

## Set B Stable Across All Locations Contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_All_Markers_Shared2 <- CONTIG_Hand_Markers_Shared2[CONTIG_Hand_Markers_Shared2 %in% CONTIG_SC_Markers2]
```
Overall Across All Locations Contig Markers
```{r}
CONTIG_All_Markers_Shared2
```

# Identify Unclassified Viral Contigs

Make list of CheckV identified viral contigs to remove
```{r,message=FALSE,warning=FALSE,results="hide"}
tax_ann <- read.csv("vc_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
tax_ann$Contigs<-row.names(tax_ann)
Checkv_contig_list<-tax_ann$Contig
```
Remove CheckV contigs from Set C stable left hand contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_LH_Markers2_final <- CONTIG_LH_Markers2[!(CONTIG_LH_Markers2 %in% Checkv_contig_list)]
```
Left Hand Stable Contigs (with Checkv contigs removed)
```{r}
CONTIG_LH_Markers2_final
```

Remove CheckV contigs from Set C stable right hand contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_RH_Markers2_final <- CONTIG_LH_Markers2[!(CONTIG_LH_Markers2 %in% Checkv_contig_list)]
```
Right Hand Stable Contigs (with Checkv contigs removed)
```{r}
CONTIG_RH_Markers2_final
```

Remove CheckV contigs from Set C stable scalp contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_SC_Markers2_final <- CONTIG_SC_Markers2[!(CONTIG_SC_Markers2 %in% Checkv_contig_list)]
```
Scalp Stable Contigs (with Checkv contigs removed)
```{r}
CONTIG_SC_Markers2_final
```

Remove CheckV contigs from Set C stable Hand contigs 
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_Hand_Markers_Shared2_final <- CONTIG_Hand_Markers_Shared2[!(CONTIG_Hand_Markers_Shared2 %in% Checkv_contig_list)]
```
Hand Stable Contigs (with Checkv contigs removed)
```{r}
CONTIG_Hand_Markers_Shared2_final
```

Remove CheckV contigs from Set C overall across all locations contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
CONTIG_All_Markers_Shared2_final <- CONTIG_All_Markers_Shared2[!(CONTIG_All_Markers_Shared2 %in% Checkv_contig_list)]
```
Overall across all locations contigs (with Checkv contigs removed)
```{r}
CONTIG_All_Markers_Shared2_final
```

For all of the identified contigs from CONTIG_LH_Markers2_final, CONTIG_RH_Markers2_final, CONTIG_SC_Markers2_final, CONTIG_Hand_Markers_Shared2_final, and CONTIG_All_Markers_Shared2_final their sequences were obtained from unmapped_1000_contigs.fa and then run through Blast using the BlastN algarithum.
Contigs containing <70% identity to a known organism or contigs with no synteny to prokaryotic or eukaryotic genomes were considered to be putative viral sequences although viral origin could not be fully confirmed and thus retained in Set C.
