---
title: "13_Heatmap_Profile_Fig5"
output: html_document
author: "Ema H Graham"
---
For Questions Email: ema.graham@huskers.unl.edu

## Description

Input Notes: 
Will need the following files:
- 
  
Output Notes: 

```{r setup,message=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggsignif)
library(cowplot)
library(phyloseq)
```

Metadata for all Phyloseq objects produced in this script
```{r}
Metadata2 <- read_csv("~/Desktop/Current_work/OTU_Builber/Sequencing_Data_Info_Sheet3.csv")
Metadata3 <- Metadata2
Metadata3$Time <- Metadata3$Time_Collected
Metadata3$Time[which(Metadata3$Time == "T_0")] <- "00_Weeks"
Metadata3$Time[which(Metadata3$Time == "2_week")] <- "02_Weeks"
Metadata3$Time[which(Metadata3$Time == "1_month")] <- "04_Weeks"
Metadata3$Time[which(Metadata3$Time == "3_month")] <- "12_Weeks"
Metadata3$Time[which(Metadata3$Time == "6_month")] <- "24_Weeks"
META <- sample_data(Metadata3)
sample_names(META)= META$SampleID
```

Make Phyloseq object for stable Set A CheckV identified and annotated viral species Makers 
```{r,message=FALSE,warning=FALSE,results="hide"}
CHeckV_counts <- read.csv("counts2_bowtie.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CHeckV_counts  <- subset(CHeckV_counts , select = -c(length))
tax_ann <- read.csv("vc_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CHeckV_counts2 <- merge(tax_ann, CHeckV_counts, by.x = "row.names", by.y = "row.names")
CHeckV_counts2<- subset (CHeckV_counts2, select = -c(Superkingdom, Realm, Kingdom, Phylum, Class, Family, Order,Subfamily, Genus))
CHeckV_spec<-c("Autographa californica multiple nucleopolyhedrovirus","Autographa californica nucleopolyhedrovirus","Staphylococcus phage St 134","Unclassified Caudovirales","Unclassified Homo sapiens like virus","Unclassified Siphoviridae","Uncultured Caudovirales phage")
CHeckV_counts2<-subset(CHeckV_counts2, Species %in% CHeckV_spec)
CHeckV_counts2<-ddply(CHeckV_counts2,"Species",numcolwise(sum))
row.names(CHeckV_counts2)<- CHeckV_counts2$Species
CHeckV_counts2<- subset (CHeckV_counts2, select = -c(Species))
CHeckV_OTU <- otu_table(CHeckV_counts2, taxa_are_rows = TRUE)
tax_ann <- read.csv("vc_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE,row.names=NULL)
tax_ann<-subset(tax_ann, Species %in% CHeckV_spec)
tax_ann<- subset (tax_ann, select = -c(contig_id))
tax_ann<-unique(tax_ann)
remv<-c("4","70")
tax_ann<-subset(tax_ann, !row.names(tax_ann) %in% remv)
row.names(tax_ann)<-tax_ann$Species
CHeckV_tax <-as.matrix(tax_ann)
CHeckV_tax <- tax_table(CHeckV_tax)
CHeckV_tax <-as.matrix(CHeckV_tax)
CHeckV_tax <- tax_table(CHeckV_tax)
CHeckV_PHY <- phyloseq(CHeckV_OTU, CHeckV_tax, META)
```

Make Phyloseq object for stable Set B Caudovirales Makers 
```{r,message=FALSE,warning=FALSE,results="hide"}
CAUDO_counts <- read.csv("counts2_CAUDO.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CAUDO_tax <- read.csv("CAUDO_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CAUDO_OTU <- merge(CAUDO_tax, CAUDO_counts, by.x="row.names", by.y="row.names")
CAUDO_OTU<- subset (CAUDO_OTU, select = -c(Superkingdom, Realm, Kingdom, Phylum, Class, Order, Family, Subfamily, Genus))
CAUDO_spec<-c("Bacillus phage Stitch","Caudovirales sp.","Escherichia phage T7","Escherichia virus DE3","Escherichia virus Lambda","Escherichia virus T7","Escherichia virus TH38","Marine virus AFVG_250M104","Marine virus AFVG_25M557","Staphylococcus phage HOB 14.1.R1","Staphylococcus phage PhiSepi-HH3","Staphylococcus phage SPbeta-like","Staphylococcus phage vB_SauH_DELF3","Staphylococcus virus IPLA7","Staphylococcus virus IPLAC1C","Staphylococcus virus PH15","Staphylococcus virus vB_SepS_456","Staphylococcus virus vB_SepS_459","Staphylococcus virus vB_SepS_E72","Streptococcus phage phi-SC181","Streptococcus phage phiJH1301-2","Uncultured Caudovirales phage")
CAUDO_OTU<-subset(CAUDO_OTU, Species %in% CAUDO_spec)
CAUDO_OTU<-ddply(CAUDO_OTU,"Species",numcolwise(sum))
row.names(CAUDO_OTU)<-CAUDO_OTU$Species
CAUDO_OTU<- subset (CAUDO_OTU, select = -c(Species))
CAUDO_OTU <- otu_table(CAUDO_OTU, taxa_are_rows = TRUE)
CAUDO_tax <- read.csv("CAUDO_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE)
CAUDO_tax<-subset(CAUDO_tax, Species %in% CAUDO_spec)
CAUDO_tax<- subset (CAUDO_tax, select = -c(ContigID))
CAUDO_tax<-unique(CAUDO_tax)
row.names(CAUDO_tax)<-CAUDO_tax$Species
CAUDO_tax <-as.matrix(CAUDO_tax)
CAUDO_tax <- tax_table(CAUDO_tax)
CAUDO_PHY <- phyloseq(CAUDO_OTU, CAUDO_tax, META)
```

Make Phyloseq object for stable Set B Papillomaviridae Makers 
```{r,message=FALSE,warning=FALSE,results="hide"}
PAP_counts <- read.csv("papilloma/PAPcounts.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
PAP_tax <- read.csv("papilloma/papilloma_taxa.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
PAP_tax <- subset(PAP_tax, select = -c(Serotype,Isolate))
PAP_OTU <- merge(PAP_tax, PAP_counts, by.x="row.names", by.y="row.names")
PAP_OTU<- subset (PAP_OTU, select = -c(Superkingdom, Realm, Kingdom, Phylum, Class, Order, Family, Subfamily, Genus))
PAP_spec<-c("Alphapapillomavirus 5","Betapapillomavirus 1","Betapapillomavirus 2","Betapapillomavirus 3","Gammapapillomavirus 12","Gammapapillomavirus 22","Gammapapillomavirus 7","Gammapapillomavirus 8")
PAP_OTU<-subset(PAP_OTU, Species %in% PAP_spec)
PAP_OTU<-ddply(PAP_OTU,"Species",numcolwise(sum))
row.names(PAP_OTU)<-PAP_OTU$Species
PAP_OTU<- subset (PAP_OTU, select = -c(Species))
PAP_OTU <- otu_table(PAP_OTU, taxa_are_rows = TRUE)
PAP_tax <- read.csv("papilloma/papilloma_taxa.csv", quote = "", header = TRUE, stringsAsFactors = FALSE)
PAP_tax <- subset(PAP_tax, select = -c(Serotype,Isolate))
PAP_tax<-subset(PAP_tax, Species %in% PAP_spec)
PAP_tax<- subset (PAP_tax, select = -c(ContigID))
PAP_tax<-unique(PAP_tax)
remv<-c("1341")
PAP_tax<-subset(PAP_tax, !row.names(PAP_tax) %in% remv)
row.names(PAP_tax)<-PAP_tax$Species
PAP_tax <-as.matrix(PAP_tax)
PAP_tax <- tax_table(PAP_tax)
PAP_PHY <- phyloseq(PAP_OTU, PAP_tax, META)
```

Make Phyloseq object for stable Set B Baculoviridae Makers 
```{r,message=FALSE,warning=FALSE,results="hide"}
BAC_counts <- read.csv("baculo/counts2_baculo_edited.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
BAC_tax <- read.csv("baculo/baculo_taxa.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
BAC_tax <- subset(BAC_tax, select = -c(Isolate))
BAC_OTU <- merge(BAC_tax, BAC_counts, by.x="row.names", by.y="row.names")
BAC_OTU<- subset (BAC_OTU, select = -c(Superkingdom, Realm, Kingdom, Phylum, Class, Order, Family, Subfamily, Genus))
BAC_spec<-c("Autographa californica multiple nucleopolyhedrovirus","Malacosoma neustria nucleopolyhedrovirus","Unclassified Baculoviridae")
BAC_OTU<-subset(BAC_OTU, Species %in% BAC_spec)
BAC_OTU<-ddply(BAC_OTU,"Species",numcolwise(sum))
row.names(BAC_OTU)<-BAC_OTU$Species
BAC_OTU<- subset (BAC_OTU, select = -c(Species))
BAC_OTU <- otu_table(BAC_OTU, taxa_are_rows = TRUE)
BAC_tax <- read.csv("baculo/baculo_taxa.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
BAC_tax <- subset(BAC_tax, select = -c(Isolate))
BAC_tax<-subset(BAC_tax, Species %in% BAC_spec)
BAC_tax<-unique(BAC_tax)
row.names(BAC_tax)<-BAC_tax$Species
BAC_tax <-as.matrix(BAC_tax)
BAC_tax <- tax_table(BAC_tax)
BAC_PHY <- phyloseq(BAC_OTU, BAC_tax, META)
```

Make Phyloseq object for stable Set B Genomoviridae Makers 
```{r,message=FALSE,warning=FALSE,results="hide"}
GEN_counts <- read.csv("genomovir/counts2_genomovir_edited.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
GEN_tax <- read.csv("genomovir/genomovir_taxa.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
GEN_tax <- subset(GEN_tax, select = -c(Isolate))
GEN_OTU <- merge(GEN_tax, GEN_counts, by.x="row.names", by.y="row.names")
GEN_OTU<- subset (GEN_OTU, select = -c(Superkingdom, Realm, Kingdom, Phylum, Class, Order, Family, Subfamily, Genus))
GEN_spec<-c("Genomoviridae sp.")
GEN_OTU<-subset(GEN_OTU, Species %in% GEN_spec)
GEN_OTU<-ddply(GEN_OTU,"Species",numcolwise(sum))
row.names(GEN_OTU)<-GEN_OTU$Species
GEN_OTU<- subset (GEN_OTU, select = -c(Species))
GEN_OTU <- otu_table(GEN_OTU, taxa_are_rows = TRUE)
GEN_tax <- read.csv("genomovir/genomovir_taxa.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
GEN_tax <- subset(GEN_tax, select = -c(Isolate))
GEN_tax<-subset(GEN_tax, Species %in% GEN_spec)
GEN_tax<-unique(GEN_tax)
row.names(GEN_tax)<-GEN_tax$Species
GEN_tax <-as.matrix(GEN_tax)
GEN_tax <- tax_table(GEN_tax)
GEN_PHY <- phyloseq(GEN_OTU, GEN_tax, META)
```

Make Phyloseq object for stable Set C contigs
```{r,message=FALSE,warning=FALSE,results="hide"}
Contigs_counts <- read.csv("counts2_bowtie.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
Contigs_counts  <- subset(Contigs_counts , select = -c(length))
CONTIG_spec<-c("k127_12278877","k127_1246730","k127_12842510","k127_12954","k127_13186497","k127_13257999","k127_14008563","k127_14874687","k127_3126920","k127_3443640","k127_4343132","k127_5189512","k127_5608134","k127_5988390","k127_6026611","k127_639643","k127_6473642","k127_699139","k127_8568361","k127_9807842","k127_9848036")
Contigs_counts<-subset(Contigs_counts, row.names(Contigs_counts) %in% CONTIG_spec)
CONTIG_OTU <- otu_table(Contigs_counts, taxa_are_rows = TRUE)
Contigs_tax <- Contigs_counts
Contigs_tax$Superkingdom<-"Viruses"
Contigs_tax$Realm <- row.names(Contigs_tax)
Contigs_tax <- subset(Contigs_tax, select = c(Superkingdom,Realm))
Contigs_tax$Kingdom<-Contigs_tax$Realm
Contigs_tax$Phylum <-Contigs_tax$Realm
Contigs_tax$Class<-Contigs_tax$Realm
Contigs_tax$Order<-Contigs_tax$Realm
Contigs_tax$Family<-Contigs_tax$Realm
Contigs_tax$Subfamily<-Contigs_tax$Realm
Contigs_tax$Genus<-Contigs_tax$Realm
Contigs_tax$Species<-Contigs_tax$Realm
Contigs_tax<-subset(Contigs_tax, row.names(Contigs_tax) %in% CONTIG_spec)
Contigs_tax <-as.matrix(Contigs_tax)
Contigs_tax <- tax_table(Contigs_tax)
CONTIG_PHY <- phyloseq(CONTIG_OTU, Contigs_tax, META)
```

Remove repeat samples and samples not used in this study
```{r,message=FALSE,warning=FALSE,results="hide"}
Samples_toRemove <- c("HV_001_27", "HV_002_27", "HV_003_27", "HV_004_27", "HV_005_27", "HV_006_27", "HV_007_27", "HV_008_27",
                      "HV_009_27", "HV_010_27", "HV_011_27", "HV_012_27", "HV_013_27", "HV_014_27", "HV_015_27", "HV_016_27",
                      "HV_017_27", "HV_018_27", "HV_019_27", "HV_020_27", "HV_021_27", "HV_022_27", "HV_023_27", "HV_024_27",
                      "HV_025_27", "HV_026_27", "HV_027_27", "HV_028_27", "HV_029_27", "HV_030_27", "HV_015_20", "HV_015_21", 
                      "HV_020_22", "HV_027_02", "HV_027_03", "HV_027_04", "HV_027_05", "HV_027_06", "HV_027_07", "HV_020_10",
                      "HV_021_13", "HV_027_01","HV_003_15")

CAUDO_PHY2 <- subset_samples(CAUDO_PHY, !(SampleID %in% Samples_toRemove))
CHeckV_PHY2 <- subset_samples(CHeckV_PHY, !(SampleID %in% Samples_toRemove))
PAP_PHY2 <- subset_samples(PAP_PHY, !(SampleID %in% Samples_toRemove))
BAC_PHY2 <- subset_samples(BAC_PHY, !(SampleID %in% Samples_toRemove))
GEN_PHY2 <- subset_samples(GEN_PHY, !(SampleID %in% Samples_toRemove))
CONTIG_PHY2 <- subset_samples(CONTIG_PHY, !(SampleID %in% Samples_toRemove))
```
Merge Phyloseq objects to make Set A Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
Profile_Checkv<-CHeckV_PHY2
```

Merge Phyloseq objects to make Set B Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
Profile_NCBI<-merge_phyloseq(CAUDO_PHY2,PAP_PHY2,BAC_PHY2,GEN_PHY2)
```

Merge Phyloseq objects to make Set C Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
Profile_Contig<-CONTIG_PHY2
```

Merge Phyloseq objects to make an overall profile (all three sets) Phyloseq object
```{r,message=FALSE,warning=FALSE,results="hide"}
Profile<- merge_phyloseq(CAUDO_PHY2,CHeckV_PHY2,PAP_PHY2,BAC_PHY2,GEN_PHY2,CONTIG_PHY2)
```
Make lists of SampleID by subject for organization and within and between dissimilarity calculations for Set comparisons
```{r,echo=FALSE}
P01<-c("HV_001_01", "HV_001_02", "HV_001_03", "HV_002_01", "HV_002_02", "HV_002_03", "HV_003_01", "HV_003_02", "HV_003_03", "HV_004_01", "HV_004_02", "HV_004_03", "HV_005_01","HV_005_03") 
P02<-c("HV_001_04", "HV_001_05", "HV_001_06", "HV_002_04", "HV_002_05", "HV_002_06", "HV_003_04", "HV_003_05", "HV_003_06", "HV_004_04", "HV_004_05", "HV_004_06", "HV_005_04", "HV_005_05","HV_005_06") 
P03<-c("HV_001_07", "HV_001_08", "HV_001_09", "HV_002_07", "HV_002_08", "HV_002_09", "HV_003_07", "HV_003_08", "HV_003_09", "HV_004_07", "HV_004_08", "HV_004_09", "HV_005_07", "HV_005_08", "HV_005_09")
P04<-c("HV_001_10", "HV_001_11", "HV_001_12", "HV_002_10", "HV_002_11", "HV_002_12", "HV_003_10", "HV_003_11", "HV_003_12", "HV_004_10", "HV_004_11", "HV_004_12", "HV_005_10", "HV_005_11","HV_005_12")
P05<-c("HV_001_13", "HV_001_14", "HV_001_15", "HV_002_13", "HV_002_14", "HV_002_15", "HV_003_13", "HV_003_14", "HV_004_13", "HV_004_14", "HV_004_15", "HV_005_13", "HV_005_14","HV_005_15")
P06<-c("HV_001_16", "HV_001_18", "HV_001_19", "HV_002_18", "HV_002_19", "HV_003_16", "HV_003_18", "HV_003_19", "HV_004_16", "HV_004_18", "HV_004_19", "HV_005_16", "HV_005_18") 
P07<-c("HV_001_20",  "HV_001_21",  "HV_001_22",  "HV_002_20",  "HV_002_21",  "HV_002_22",  "HV_003_20",  "HV_003_21",  "HV_003_22",  "HV_004_20",  "HV_004_21",  "HV_004_22",  "HV_005_20", "HV_005_22") 
P08<-c("HV_006_01", "HV_006_02", "HV_006_03", "HV_007_01", "HV_007_02", "HV_007_03", "HV_008_01", "HV_008_02", "HV_008_03", "HV_009_01", "HV_009_03", "HV_010_01", "HV_010_02","HV_010_03")
P09<-c("HV_006_04", "HV_006_05", "HV_006_06", "HV_007_04", "HV_007_05", "HV_007_06", "HV_008_04", "HV_008_05", "HV_008_06", "HV_009_04", "HV_009_05", "HV_009_06", "HV_010_04", "HV_010_05", "HV_010_06")
P10<-c("HV_006_07", "HV_006_08", "HV_006_09", "HV_007_07", "HV_007_08", "HV_007_09", "HV_008_07", "HV_008_08", "HV_008_09", "HV_009_07", "HV_009_08", "HV_009_09", "HV_010_07", "HV_010_08","HV_010_09")
P11<-c("HV_006_10", "HV_006_11", "HV_006_12", "HV_007_10", "HV_007_11", "HV_007_12", "HV_008_10", "HV_008_11", "HV_008_12", "HV_009_10", "HV_009_11", "HV_009_12", "HV_010_10", "HV_010_11","HV_010_12")
P12<-c("HV_006_13", "HV_006_14", "HV_006_15", "HV_007_13", "HV_007_14", "HV_007_15", "HV_008_13", "HV_008_14", "HV_008_15", "HV_009_13", "HV_009_14", "HV_009_15", "HV_010_13", "HV_010_14","HV_010_15")
P13<-c("HV_006_16", "HV_006_18", "HV_006_19", "HV_007_16", "HV_007_18", "HV_007_19", "HV_008_16", "HV_008_18", "HV_008_19", "HV_009_16", "HV_009_18", "HV_009_19", "HV_010_16", "HV_010_18","HV_010_19")
P14<-c("HV_006_20", "HV_006_21", "HV_006_22", "HV_007_20", "HV_007_21", "HV_007_22", "HV_008_20", "HV_008_21", "HV_008_22", "HV_009_20", "HV_009_21", "HV_009_22", "HV_010_20", "HV_010_21","HV_010_22")
P15<-c("HV_011_01", "HV_011_02", "HV_011_03", "HV_012_01", "HV_012_02", "HV_012_03", "HV_013_01", "HV_013_02", "HV_013_03", "HV_014_01", "HV_014_02", "HV_014_03", "HV_015_01", "HV_015_02","HV_015_03")
P16<-c("HV_011_04", "HV_011_05", "HV_011_06", "HV_012_04", "HV_012_05", "HV_012_06", "HV_013_04", "HV_013_05", "HV_014_04", "HV_014_05", "HV_014_06", "HV_015_04", "HV_015_05","HV_015_06")
P17<-c("HV_011_07", "HV_011_08", "HV_011_09", "HV_012_07", "HV_012_08", "HV_012_09", "HV_013_07", "HV_013_08", "HV_013_09", "HV_014_07", "HV_014_08", "HV_014_09", "HV_015_07", "HV_015_08","HV_015_09")
P18<-c("HV_011_10", "HV_011_11", "HV_011_12", "HV_012_10", "HV_012_11", "HV_012_12", "HV_013_10", "HV_013_11", "HV_013_12", "HV_014_10", "HV_014_11", "HV_014_12", "HV_015_10", "HV_015_11", "HV_015_12")
P19<-c("HV_011_13", "HV_011_14", "HV_011_15", "HV_012_13", "HV_012_14", "HV_012_15", "HV_013_13", "HV_013_14", "HV_013_15", "HV_014_13", "HV_014_14", "HV_014_15", "HV_015_13", "HV_015_14","HV_015_15")
P20<-c("HV_011_16", "HV_011_18", "HV_011_19", "HV_012_16", "HV_012_18", "HV_012_19", "HV_013_16", "HV_013_18", "HV_013_19", "HV_014_16", "HV_014_18", "HV_014_19", "HV_015_16", "HV_015_18","HV_015_19")
P21<-c("HV_011_20", "HV_011_21", "HV_011_22", "HV_012_20", "HV_012_21", "HV_012_22", "HV_013_20", "HV_013_21", "HV_013_22", "HV_014_20", "HV_014_21","HV_014_22")
P22<-c("HV_016_01", "HV_017_01", "HV_018_01", "HV_019_01", "HV_020_01", "HV_021_02", "HV_022_01", "HV_023_01", "HV_024_01", "HV_025_02", "HV_026_01", "HV_027_08", "HV_028_01", "HV_029_01","HV_030_01")
P23<-c("HV_016_02", "HV_017_02", "HV_018_02", "HV_019_02", "HV_020_02", "HV_021_03", "HV_022_02", "HV_023_02", "HV_024_02", "HV_025_03", "HV_026_02", "HV_027_09", "HV_028_02", "HV_029_02","HV_030_02")
P24<-c("HV_016_03", "HV_017_03", "HV_018_03", "HV_019_03", "HV_021_01", "HV_021_04", "HV_022_03", "HV_023_03", "HV_024_03", "HV_025_04", "HV_026_03", "HV_027_10", "HV_028_03", "HV_029_03","HV_030_03")
P25<-c("HV_016_04", "HV_017_04", "HV_018_04", "HV_019_04", "HV_020_03", "HV_021_05", "HV_022_04", "HV_023_04", "HV_024_04", "HV_025_05", "HV_026_04", "HV_027_11", "HV_028_04", "HV_029_04","HV_030_04")
P26<-c("HV_016_05", "HV_017_05", "HV_018_05", "HV_019_05", "HV_020_04", "HV_021_06", "HV_022_05", "HV_023_05", "HV_024_05", "HV_025_06", "HV_026_05", "HV_027_12", "HV_028_05", "HV_029_05", "HV_030_05")
P27<-c("HV_016_06", "HV_017_06", "HV_018_06", "HV_019_06", "HV_020_05", "HV_021_07", "HV_022_06", "HV_023_06", "HV_024_06", "HV_025_07", "HV_026_06", "HV_027_13", "HV_028_06", "HV_029_06","HV_030_06")
P28<-c("HV_016_07", "HV_017_07", "HV_018_07", "HV_019_07", "HV_020_06", "HV_021_08", "HV_022_07", "HV_023_07", "HV_024_07", "HV_025_08", "HV_026_07", "HV_027_14", "HV_028_07", "HV_029_07","HV_030_07")
P29<-c("HV_016_08", "HV_017_08", "HV_018_08", "HV_019_08", "HV_020_07", "HV_021_09", "HV_022_08", "HV_023_08", "HV_024_08", "HV_025_09", "HV_026_08", "HV_027_15", "HV_028_08", "HV_029_08","HV_030_08")
P30<-c("HV_016_09", "HV_017_09", "HV_018_09", "HV_019_09", "HV_020_08", "HV_021_10", "HV_022_09", "HV_023_09", "HV_024_09", "HV_025_10", "HV_026_09", "HV_027_16", "HV_028_09", "HV_029_09","HV_030_09")
P31<-c("HV_016_10", "HV_017_10", "HV_018_10", "HV_019_10", "HV_021_11", "HV_022_10", "HV_023_10", "HV_024_10", "HV_026_10", "HV_027_18", "HV_028_10", "HV_029_10")
P32<-c("HV_016_11", "HV_017_11", "HV_018_11", "HV_019_11", "HV_020_09", "HV_021_12", "HV_022_11", "HV_023_11", "HV_024_11", "HV_025_11", "HV_026_11", "HV_027_19", "HV_028_11", "HV_029_11","HV_030_10")
P34<-c("HV_016_12", "HV_017_12", "HV_018_12", "HV_019_12", "HV_020_11", "HV_021_14", "HV_022_12", "HV_023_12", "HV_024_12", "HV_025_12", "HV_026_12", "HV_027_20", "HV_028_12", "HV_029_12","HV_030_11")
P35<-c("HV_016_13", "HV_017_13", "HV_018_13", "HV_019_13", "HV_020_12", "HV_021_15", "HV_022_13", "HV_023_13", "HV_024_13", "HV_025_13", "HV_026_13", "HV_027_21", "HV_028_13", "HV_029_13","HV_030_12")
P36<-c("HV_016_14", "HV_017_14", "HV_018_14", "HV_019_14", "HV_020_13", "HV_021_16", "HV_022_14", "HV_023_14", "HV_024_14", "HV_025_14", "HV_026_14", "HV_027_22", "HV_028_14", "HV_029_14","HV_030_13")
P37<-c("HV_016_15", "HV_017_15", "HV_018_15", "HV_019_15", "HV_020_14", "HV_021_18", "HV_022_15", "HV_023_15", "HV_024_15", "HV_025_15", "HV_026_15", "HV_028_15", "HV_029_15", "HV_030_14","HV_030_22")
P38<-c("HV_016_16", "HV_017_16", "HV_018_16", "HV_019_16", "HV_020_15", "HV_021_19", "HV_022_16", "HV_023_16", "HV_024_16", "HV_025_16", "HV_026_16", "HV_028_16", "HV_029_16","HV_030_15")
P39<-c("HV_016_18", "HV_017_18", "HV_018_18", "HV_019_18", "HV_020_16", "HV_021_20", "HV_022_18", "HV_023_18", "HV_024_18", "HV_025_18", "HV_026_18", "HV_028_18", "HV_029_18","HV_030_16")
P40<-c("HV_016_19", "HV_017_19", "HV_018_19", "HV_019_19", "HV_020_18", "HV_021_21", "HV_022_19", "HV_023_19", "HV_024_19", "HV_025_19", "HV_026_19", "HV_028_19", "HV_029_19","HV_030_18")
P41<-c("HV_016_20", "HV_017_20", "HV_018_20", "HV_019_20", "HV_020_19", "HV_021_22", "HV_022_20", "HV_023_20", "HV_024_20", "HV_025_20", "HV_026_20", "HV_028_20", "HV_029_20","HV_030_19")
P42<-c("HV_016_21", "HV_017_21", "HV_018_21", "HV_019_21", "HV_020_20", "HV_022_21", "HV_023_21", "HV_024_21", "HV_025_21", "HV_026_21", "HV_028_21", "HV_029_21", "HV_030_20")
P43<-c("HV_016_22", "HV_017_22", "HV_018_22", "HV_019_22", "HV_020_21", "HV_022_22", "HV_023_22", "HV_024_22", "HV_025_01", "HV_025_22", "HV_026_22", "HV_028_22", "HV_029_22","HV_030_21")
```
## Set A Binary Jaccard Dissimilairty Matrix
```{r,message=FALSE,warning=FALSE,results="hide"}
norm_groups <- transform_sample_counts(Profile_Checkv, function(x) x / sum(x) )
mea<-phyloseq::distance(norm_groups, method="jaccard", binary = TRUE)
df <- melt(as.matrix(mea), varnames = c("row", "col"))
```
Set A Subject P01
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P01)
df_between<-subset(df_P, !row %in% P01)
df_within<-subset(df_P, row %in% P01)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P01_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P01_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P02
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P02)
df_between<-subset(df_P, !row %in% P02)
df_within<-subset(df_P, row %in% P02)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P02_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P02_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P03
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P03)
df_between<-subset(df_P, !row %in% P03)
df_within<-subset(df_P, row %in% P03)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P03_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P03_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P04
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P04)
df_between<-subset(df_P, !row %in% P04)
df_within<-subset(df_P, row %in% P04)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P04_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P04_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P05
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P05)
df_between<-subset(df_P, !row %in% P05)
df_within<-subset(df_P, row %in% P05)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P05_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P05_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P06
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P06)
df_between<-subset(df_P, !row %in% P06)
df_within<-subset(df_P, row %in% P06)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P06_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P06_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P07
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P07)
df_between<-subset(df_P, !row %in% P07)
df_within<-subset(df_P, row %in% P07)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P07_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P07_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P08
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P08)
df_between<-subset(df_P, !row %in% P08)
df_within<-subset(df_P, row %in% P08)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P08_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P08_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P09
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P09)
df_between<-subset(df_P, !row %in% P09)
df_within<-subset(df_P, row %in% P09)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P09_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P09_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P10
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P10)
df_between<-subset(df_P, !row %in% P10)
df_within<-subset(df_P, row %in% P10)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P10_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P10_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P11
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P11)
df_between<-subset(df_P, !row %in% P11)
df_within<-subset(df_P, row %in% P11)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P11_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P11_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P12
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P12)
df_between<-subset(df_P, !row %in% P12)
df_within<-subset(df_P, row %in% P12)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P12_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P12_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P13
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P13)
df_between<-subset(df_P, !row %in% P13)
df_within<-subset(df_P, row %in% P13)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P13_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P13_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P14
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P14)
df_between<-subset(df_P, !row %in% P14)
df_within<-subset(df_P, row %in% P14)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P14_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P14_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P15
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P15)
df_between<-subset(df_P, !row %in% P15)
df_within<-subset(df_P, row %in% P15)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P15_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P15_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P16
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P16)
df_between<-subset(df_P, !row %in% P16)
df_within<-subset(df_P, row %in% P16)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P16_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P16_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P17
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P17)
df_between<-subset(df_P, !row %in% P17)
df_within<-subset(df_P, row %in% P17)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P17_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P17_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P18
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P18)
df_between<-subset(df_P, !row %in% P18)
df_within<-subset(df_P, row %in% P18)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P18_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P18_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P19
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P19)
df_between<-subset(df_P, !row %in% P19)
df_within<-subset(df_P, row %in% P19)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P19_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P19_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P20
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P20)
df_between<-subset(df_P, !row %in% P20)
df_within<-subset(df_P, row %in% P20)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P20_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P20_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P21
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P21)
df_between<-subset(df_P, !row %in% P21)
df_within<-subset(df_P, row %in% P21)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P21_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P21_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P22
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P22)
df_between<-subset(df_P, !row %in% P22)
df_within<-subset(df_P, row %in% P22)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P22_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P22_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P23
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P23)
df_between<-subset(df_P, !row %in% P23)
df_within<-subset(df_P, row %in% P23)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P23_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P23_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P24
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P24)
df_between<-subset(df_P, !row %in% P24)
df_within<-subset(df_P, row %in% P24)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P24_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P24_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P25
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P25)
df_between<-subset(df_P, !row %in% P25)
df_within<-subset(df_P, row %in% P25)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P25_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P25_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P26
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P26)
df_between<-subset(df_P, !row %in% P26)
df_within<-subset(df_P, row %in% P26)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P26_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P26_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P27
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P27)
df_between<-subset(df_P, !row %in% P27)
df_within<-subset(df_P, row %in% P27)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P27_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P27_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P28
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P28)
df_between<-subset(df_P, !row %in% P28)
df_within<-subset(df_P, row %in% P28)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P28_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P28_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P29
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P29)
df_between<-subset(df_P, !row %in% P29)
df_within<-subset(df_P, row %in% P29)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P29_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P29_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P30
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P30)
df_between<-subset(df_P, !row %in% P30)
df_within<-subset(df_P, row %in% P30)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P30_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P30_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P31
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P31)
df_between<-subset(df_P, !row %in% P31)
df_within<-subset(df_P, row %in% P31)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P31_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P31_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P32
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P32)
df_between<-subset(df_P, !row %in% P32)
df_within<-subset(df_P, row %in% P32)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P32_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P32_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P34
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P34)
df_between<-subset(df_P, !row %in% P34)
df_within<-subset(df_P, row %in% P34)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P34_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P34_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P35
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P35)
df_between<-subset(df_P, !row %in% P35)
df_within<-subset(df_P, row %in% P35)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P35_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P35_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P36
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P36)
df_between<-subset(df_P, !row %in% P36)
df_within<-subset(df_P, row %in% P36)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P36_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P36_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P37
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P37)
df_between<-subset(df_P, !row %in% P37)
df_within<-subset(df_P, row %in% P37)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P37_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P37_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P38
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P38)
df_between<-subset(df_P, !row %in% P38)
df_within<-subset(df_P, row %in% P38)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P38_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P38_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P39
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P39)
df_between<-subset(df_P, !row %in% P39)
df_within<-subset(df_P, row %in% P39)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P39_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P39_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P40
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P40)
df_between<-subset(df_P, !row %in% P40)
df_within<-subset(df_P, row %in% P40)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P40_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P40_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P41
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P41)
df_between<-subset(df_P, !row %in% P41)
df_within<-subset(df_P, row %in% P41)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P41_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P41_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P42
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P42)
df_between<-subset(df_P, !row %in% P42)
df_within<-subset(df_P, row %in% P42)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P42_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P42_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set A Subject P43
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P43)
df_between<-subset(df_P, !row %in% P43)
df_within<-subset(df_P, row %in% P43)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SA_P43_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SA_P43_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```

## Set B Binary Jaccard Dissimilairty Matrix
```{r,message=FALSE,warning=FALSE,results="hide"}
norm_groups <- transform_sample_counts(Profile_NCBI, function(x) x / sum(x) )
mea<-phyloseq::distance(norm_groups, method="jaccard", binary = TRUE)
df <- melt(as.matrix(mea), varnames = c("row", "col"))
```
Set B Subject P01
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P01)
df_between<-subset(df_P, !row %in% P01)
df_within<-subset(df_P, row %in% P01)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P01_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P01_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P02
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P02)
df_between<-subset(df_P, !row %in% P02)
df_within<-subset(df_P, row %in% P02)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P02_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P02_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P03
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P03)
df_between<-subset(df_P, !row %in% P03)
df_within<-subset(df_P, row %in% P03)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P03_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P03_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P04
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P04)
df_between<-subset(df_P, !row %in% P04)
df_within<-subset(df_P, row %in% P04)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P04_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P04_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P05
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P05)
df_between<-subset(df_P, !row %in% P05)
df_within<-subset(df_P, row %in% P05)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P05_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P05_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P06
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P06)
df_between<-subset(df_P, !row %in% P06)
df_within<-subset(df_P, row %in% P06)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P06_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P06_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P07
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P07)
df_between<-subset(df_P, !row %in% P07)
df_within<-subset(df_P, row %in% P07)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P07_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P07_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P08
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P08)
df_between<-subset(df_P, !row %in% P08)
df_within<-subset(df_P, row %in% P08)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P08_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P08_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P09
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P09)
df_between<-subset(df_P, !row %in% P09)
df_within<-subset(df_P, row %in% P09)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P09_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P09_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P10
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P10)
df_between<-subset(df_P, !row %in% P10)
df_within<-subset(df_P, row %in% P10)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P10_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P10_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P11
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P11)
df_between<-subset(df_P, !row %in% P11)
df_within<-subset(df_P, row %in% P11)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P11_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P11_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P12
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P12)
df_between<-subset(df_P, !row %in% P12)
df_within<-subset(df_P, row %in% P12)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P12_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P12_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P13
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P13)
df_between<-subset(df_P, !row %in% P13)
df_within<-subset(df_P, row %in% P13)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P13_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P13_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P14
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P14)
df_between<-subset(df_P, !row %in% P14)
df_within<-subset(df_P, row %in% P14)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P14_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P14_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P15
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P15)
df_between<-subset(df_P, !row %in% P15)
df_within<-subset(df_P, row %in% P15)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P15_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P15_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P16
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P16)
df_between<-subset(df_P, !row %in% P16)
df_within<-subset(df_P, row %in% P16)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P16_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P16_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P17
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P17)
df_between<-subset(df_P, !row %in% P17)
df_within<-subset(df_P, row %in% P17)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P17_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P17_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P18
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P18)
df_between<-subset(df_P, !row %in% P18)
df_within<-subset(df_P, row %in% P18)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P18_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P18_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P19
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P19)
df_between<-subset(df_P, !row %in% P19)
df_within<-subset(df_P, row %in% P19)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P19_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P19_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P20
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P20)
df_between<-subset(df_P, !row %in% P20)
df_within<-subset(df_P, row %in% P20)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P20_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P20_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P21
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P21)
df_between<-subset(df_P, !row %in% P21)
df_within<-subset(df_P, row %in% P21)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P21_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P21_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P22
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P22)
df_between<-subset(df_P, !row %in% P22)
df_within<-subset(df_P, row %in% P22)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P22_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P22_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P23
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P23)
df_between<-subset(df_P, !row %in% P23)
df_within<-subset(df_P, row %in% P23)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P23_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P23_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P24
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P24)
df_between<-subset(df_P, !row %in% P24)
df_within<-subset(df_P, row %in% P24)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P24_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P24_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P25
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P25)
df_between<-subset(df_P, !row %in% P25)
df_within<-subset(df_P, row %in% P25)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P25_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P25_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P26
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P26)
df_between<-subset(df_P, !row %in% P26)
df_within<-subset(df_P, row %in% P26)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P26_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P26_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P27
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P27)
df_between<-subset(df_P, !row %in% P27)
df_within<-subset(df_P, row %in% P27)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P27_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P27_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P28
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P28)
df_between<-subset(df_P, !row %in% P28)
df_within<-subset(df_P, row %in% P28)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P28_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P28_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P29
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P29)
df_between<-subset(df_P, !row %in% P29)
df_within<-subset(df_P, row %in% P29)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P29_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P29_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P30
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P30)
df_between<-subset(df_P, !row %in% P30)
df_within<-subset(df_P, row %in% P30)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P30_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P30_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P31
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P31)
df_between<-subset(df_P, !row %in% P31)
df_within<-subset(df_P, row %in% P31)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P31_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P31_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P32
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P32)
df_between<-subset(df_P, !row %in% P32)
df_within<-subset(df_P, row %in% P32)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P32_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P32_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P34
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P34)
df_between<-subset(df_P, !row %in% P34)
df_within<-subset(df_P, row %in% P34)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P34_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P34_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P35
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P35)
df_between<-subset(df_P, !row %in% P35)
df_within<-subset(df_P, row %in% P35)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P35_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P35_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P36
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P36)
df_between<-subset(df_P, !row %in% P36)
df_within<-subset(df_P, row %in% P36)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P36_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P36_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P37
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P37)
df_between<-subset(df_P, !row %in% P37)
df_within<-subset(df_P, row %in% P37)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P37_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P37_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P38
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P38)
df_between<-subset(df_P, !row %in% P38)
df_within<-subset(df_P, row %in% P38)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P38_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P38_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P39
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P39)
df_between<-subset(df_P, !row %in% P39)
df_within<-subset(df_P, row %in% P39)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P39_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P39_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P40
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P40)
df_between<-subset(df_P, !row %in% P40)
df_within<-subset(df_P, row %in% P40)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P40_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P40_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P41
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P41)
df_between<-subset(df_P, !row %in% P41)
df_within<-subset(df_P, row %in% P41)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P41_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P41_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P42
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P42)
df_between<-subset(df_P, !row %in% P42)
df_within<-subset(df_P, row %in% P42)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P42_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P42_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set B Subject P43
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P43)
df_between<-subset(df_P, !row %in% P43)
df_within<-subset(df_P, row %in% P43)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SB_P43_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SB_P43_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```

## Set C Binary Jaccard Dissimilairty Matrix
```{r,message=FALSE,warning=FALSE,results="hide"}
norm_groups <- transform_sample_counts(Profile_Contig, function(x) x / sum(x) )
mea<-phyloseq::distance(norm_groups, method="jaccard", binary = TRUE)
df <- melt(as.matrix(mea), varnames = c("row", "col"))
```
Set C Subject P01
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P01)
df_between<-subset(df_P, !row %in% P01)
df_within<-subset(df_P, row %in% P01)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P01_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P01_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P02
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P02)
df_between<-subset(df_P, !row %in% P02)
df_within<-subset(df_P, row %in% P02)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P02_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P02_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P03
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P03)
df_between<-subset(df_P, !row %in% P03)
df_within<-subset(df_P, row %in% P03)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P03_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P03_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P04
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P04)
df_between<-subset(df_P, !row %in% P04)
df_within<-subset(df_P, row %in% P04)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P04_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P04_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P05
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P05)
df_between<-subset(df_P, !row %in% P05)
df_within<-subset(df_P, row %in% P05)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P05_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P05_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P06
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P06)
df_between<-subset(df_P, !row %in% P06)
df_within<-subset(df_P, row %in% P06)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P06_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P06_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P07
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P07)
df_between<-subset(df_P, !row %in% P07)
df_within<-subset(df_P, row %in% P07)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P07_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P07_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P08
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P08)
df_between<-subset(df_P, !row %in% P08)
df_within<-subset(df_P, row %in% P08)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P08_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P08_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P09
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P09)
df_between<-subset(df_P, !row %in% P09)
df_within<-subset(df_P, row %in% P09)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P09_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P09_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P10
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P10)
df_between<-subset(df_P, !row %in% P10)
df_within<-subset(df_P, row %in% P10)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P10_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P10_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P11
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P11)
df_between<-subset(df_P, !row %in% P11)
df_within<-subset(df_P, row %in% P11)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P11_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P11_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P12
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P12)
df_between<-subset(df_P, !row %in% P12)
df_within<-subset(df_P, row %in% P12)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P12_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P12_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P13
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P13)
df_between<-subset(df_P, !row %in% P13)
df_within<-subset(df_P, row %in% P13)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P13_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P13_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P14
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P14)
df_between<-subset(df_P, !row %in% P14)
df_within<-subset(df_P, row %in% P14)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P14_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P14_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P15
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P15)
df_between<-subset(df_P, !row %in% P15)
df_within<-subset(df_P, row %in% P15)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P15_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P15_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P16
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P16)
df_between<-subset(df_P, !row %in% P16)
df_within<-subset(df_P, row %in% P16)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P16_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P16_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P17
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P17)
df_between<-subset(df_P, !row %in% P17)
df_within<-subset(df_P, row %in% P17)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P17_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P17_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P18
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P18)
df_between<-subset(df_P, !row %in% P18)
df_within<-subset(df_P, row %in% P18)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P18_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P18_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P19
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P19)
df_between<-subset(df_P, !row %in% P19)
df_within<-subset(df_P, row %in% P19)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P19_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P19_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P20
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P20)
df_between<-subset(df_P, !row %in% P20)
df_within<-subset(df_P, row %in% P20)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P20_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P20_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P21
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P21)
df_between<-subset(df_P, !row %in% P21)
df_within<-subset(df_P, row %in% P21)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P21_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P21_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P22
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P22)
df_between<-subset(df_P, !row %in% P22)
df_within<-subset(df_P, row %in% P22)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P22_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P22_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P23
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P23)
df_between<-subset(df_P, !row %in% P23)
df_within<-subset(df_P, row %in% P23)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P23_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P23_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P24
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P24)
df_between<-subset(df_P, !row %in% P24)
df_within<-subset(df_P, row %in% P24)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P24_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P24_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P25
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P25)
df_between<-subset(df_P, !row %in% P25)
df_within<-subset(df_P, row %in% P25)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P25_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P25_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P26
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P26)
df_between<-subset(df_P, !row %in% P26)
df_within<-subset(df_P, row %in% P26)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P26_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P26_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P27
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P27)
df_between<-subset(df_P, !row %in% P27)
df_within<-subset(df_P, row %in% P27)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P27_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P27_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P28
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P28)
df_between<-subset(df_P, !row %in% P28)
df_within<-subset(df_P, row %in% P28)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P28_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P28_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P29
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P29)
df_between<-subset(df_P, !row %in% P29)
df_within<-subset(df_P, row %in% P29)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P29_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P29_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P30
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P30)
df_between<-subset(df_P, !row %in% P30)
df_within<-subset(df_P, row %in% P30)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P30_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P30_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P31
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P31)
df_between<-subset(df_P, !row %in% P31)
df_within<-subset(df_P, row %in% P31)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P31_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P31_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P32
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P32)
df_between<-subset(df_P, !row %in% P32)
df_within<-subset(df_P, row %in% P32)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P32_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P32_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P34
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P34)
df_between<-subset(df_P, !row %in% P34)
df_within<-subset(df_P, row %in% P34)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P34_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P34_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P35
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P35)
df_between<-subset(df_P, !row %in% P35)
df_within<-subset(df_P, row %in% P35)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P35_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P35_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P36
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P36)
df_between<-subset(df_P, !row %in% P36)
df_within<-subset(df_P, row %in% P36)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P36_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P36_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P37
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P37)
df_between<-subset(df_P, !row %in% P37)
df_within<-subset(df_P, row %in% P37)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P37_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P37_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P38
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P38)
df_between<-subset(df_P, !row %in% P38)
df_within<-subset(df_P, row %in% P38)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P38_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P38_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P39
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P39)
df_between<-subset(df_P, !row %in% P39)
df_within<-subset(df_P, row %in% P39)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P39_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P39_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P40
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P40)
df_between<-subset(df_P, !row %in% P40)
df_within<-subset(df_P, row %in% P40)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P40_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P40_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P41
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P41)
df_between<-subset(df_P, !row %in% P41)
df_within<-subset(df_P, row %in% P41)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P41_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P41_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P42
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P42)
df_between<-subset(df_P, !row %in% P42)
df_within<-subset(df_P, row %in% P42)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P42_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P42_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```
Set C Subject P43
```{r,message=FALSE,warning=FALSE,results="hide"}
df_P<-subset(df, col %in% P43)
df_between<-subset(df_P, !row %in% P43)
df_within<-subset(df_P, row %in% P43)
#remove same sample comparisons
df_within2 <- df_within[df_within$row != df_within$col,]
#mean betwen
mean(df_between$value)
#mean within
mean(df_within2$value)
SC_P43_both<-c(mean(df_between$value),mean(df_within2$value))
```
```{r}
SC_P43_both
# Results were stored in an excel file named Jaccard_bw_win (avalible on Github)
# The first output value is the average between dissimilarity index and the second value is the average within dissimilarity index
```








Make lists of SampleID by location within subject for organization and within and between dissimilarity calculations
```{r,echo=FALSE}
P01_LH<-c("HV_001_01", "HV_002_01", "HV_003_01", "HV_004_01","HV_005_01")
P01_RH<-c("HV_001_02", "HV_002_02", "HV_003_02","HV_004_02")
P01_SC<-c("HV_001_03", "HV_002_03", "HV_003_03", "HV_004_03","HV_005_03")

P02_LH<-c("HV_001_04", "HV_002_04", "HV_003_04", "HV_004_04","HV_005_04")
P02_RH<-c("HV_001_05", "HV_002_05", "HV_003_05", "HV_004_05","HV_005_05")
P02_SC<-c("HV_001_06", "HV_002_06", "HV_003_06", "HV_004_06","HV_005_06")

P03_LH<-c("HV_001_07", "HV_002_07", "HV_003_07", "HV_004_07","HV_005_07")
P03_RH<-c("HV_001_08", "HV_002_08", "HV_003_08", "HV_004_08","HV_005_08")
P03_SC<-c("HV_001_09", "HV_002_09", "HV_003_09", "HV_004_09","HV_005_09")

P04_LH<-c("HV_001_10", "HV_002_10", "HV_003_10", "HV_004_10", "HV_005_10")
P04_RH<-c("HV_001_11", "HV_002_11", "HV_003_11", "HV_004_11","HV_005_11")
P04_SC<-c("HV_001_12", "HV_002_12", "HV_003_12", "HV_004_12","HV_005_12")

P05_LH<-c("HV_001_13", "HV_002_13", "HV_003_13", "HV_004_13","HV_005_13")
P05_RH<-c("HV_001_14", "HV_002_14", "HV_003_14", "HV_004_14", "HV_005_14")
P05_SC<-c("HV_001_15", "HV_002_15", "HV_004_15","HV_005_15")

P06_LH<-c("HV_001_16", "HV_003_16", "HV_004_16", "HV_005_16")
P06_RH<-c("HV_001_18", "HV_002_18", "HV_003_18", "HV_004_18","HV_005_18")
P06_SC<-c("HV_001_19", "HV_002_19", "HV_003_19", "HV_004_19","HV_005_19")

P07_LH<-c("HV_001_20", "HV_002_20", "HV_003_20", "HV_004_20","HV_005_20")
P07_RH<-c("HV_001_21", "HV_002_21", "HV_003_21","HV_004_21")
P07_SC<-c("HV_001_22", "HV_002_22", "HV_003_22", "HV_004_22","HV_005_22")

P08_LH<-c("HV_006_01", "HV_007_01", "HV_008_01", "HV_009_01","HV_010_01")
P08_RH<-c("HV_006_02", "HV_007_02", "HV_008_02","HV_010_02")
P08_SC<-c("HV_006_03", "HV_007_03", "HV_008_03", "HV_009_03","HV_010_03")

P09_LH<-c("HV_006_04", "HV_007_04", "HV_008_04", "HV_009_04","HV_010_04")
P09_RH<-c("HV_006_05", "HV_007_05", "HV_008_05", "HV_009_05","HV_010_05")
P09_SC<-c("HV_006_06", "HV_007_06", "HV_008_06", "HV_009_06","HV_010_06")

P10_LH<-c("HV_006_07", "HV_007_07", "HV_008_07", "HV_009_07","HV_010_07")
P10_RH<-c("HV_006_08", "HV_007_08", "HV_008_08", "HV_009_08","HV_010_08")
P10_SC<-c("HV_006_09", "HV_007_09", "HV_008_09", "HV_009_09","HV_010_09")

P11_LH<-c("HV_006_10", "HV_007_10", "HV_008_10", "HV_009_10","HV_010_10")
P11_RH<-c("HV_006_11", "HV_007_11", "HV_008_11", "HV_009_11","HV_010_11")
P11_SC<-c("HV_006_12", "HV_007_12", "HV_008_12", "HV_009_12","HV_010_12")

P12_LH<-c("HV_006_13", "HV_007_13", "HV_008_13", "HV_009_13","HV_010_13")
P12_RH<-c("HV_006_14", "HV_007_14", "HV_008_14", "HV_009_14","HV_010_14")
P12_SC<-c("HV_006_15", "HV_007_15", "HV_008_15", "HV_009_15","HV_010_15")

P13_LH<-c("HV_006_16", "HV_007_16", "HV_008_16", "HV_009_16","HV_010_16")
P13_RH<-c("HV_006_18", "HV_007_18", "HV_008_18", "HV_009_18","HV_010_18")
P13_SC<-c("HV_006_19", "HV_007_19", "HV_008_19", "HV_009_19","HV_010_19")

P14_LH<-c("HV_006_20", "HV_007_20", "HV_008_20", "HV_009_20","HV_010_20")
P14_RH<-c("HV_006_21", "HV_007_21", "HV_008_21", "HV_009_21","HV_010_21")
P14_SC<-c("HV_006_22", "HV_007_22", "HV_008_22", "HV_009_22","HV_010_22")

P15_LH<-c("HV_011_01", "HV_012_01", "HV_013_01", "HV_014_01","HV_015_01")
P15_RH<-c("HV_011_02", "HV_012_02", "HV_013_02", "HV_014_02","HV_015_02")
P15_SC<-c("HV_011_03", "HV_012_03", "HV_013_03", "HV_014_03","HV_015_03")

P16_LH<-c("HV_011_04", "HV_012_04", "HV_013_04", "HV_014_04","HV_015_04")
P16_RH<-c("HV_011_05", "HV_012_05", "HV_013_05", "HV_014_05","HV_015_05")
P16_SC<-c("HV_011_06", "HV_012_06", "HV_014_06","HV_015_06")

P17_LH<-c("HV_011_07", "HV_012_07", "HV_013_07", "HV_014_07","HV_015_07")
P17_RH<-c("HV_011_08", "HV_012_08", "HV_013_08", "HV_014_08","HV_015_08")
P17_SC<-c("HV_011_09", "HV_012_09", "HV_013_09", "HV_014_09","HV_015_09")

P18_LH<-c("HV_011_10", "HV_012_10", "HV_013_10", "HV_014_10","HV_015_10")
P18_RH<-c("HV_011_11", "HV_012_11", "HV_013_11", "HV_014_11","HV_015_11")
P18_SC<-c("HV_011_12", "HV_012_12", "HV_013_12", "HV_014_12","HV_015_12")

P19_LH<-c("HV_011_13", "HV_012_13", "HV_013_13", "HV_014_13","HV_015_13")
P19_RH<-c("HV_011_14", "HV_012_14", "HV_013_14", "HV_014_14","HV_015_14")
P19_SC<-c("HV_011_15", "HV_012_15", "HV_013_15", "HV_014_15","HV_015_15")

P20_LH<-c("HV_011_16", "HV_012_16", "HV_013_16", "HV_014_16","HV_015_16")
P20_RH<-c("HV_011_18", "HV_012_18", "HV_013_18", "HV_014_18","HV_015_18")
P20_SC<-c("HV_011_19", "HV_012_19", "HV_013_19", "HV_014_19","HV_015_19")

P21_LH<-c("HV_011_20", "HV_012_20", "HV_013_20","HV_014_20")
P21_RH<-c("HV_011_21", "HV_012_21", "HV_013_21","HV_014_21")
P21_SC<-c("HV_011_22", "HV_012_22", "HV_013_22","HV_014_22")

P22_LH<-c("HV_021_02", "HV_022_01", "HV_023_01", "HV_024_01","HV_025_02")
P22_RH<-c("HV_026_01", "HV_027_08", "HV_028_01", "HV_029_01","HV_030_01")
P22_SC<-c("HV_016_01", "HV_017_01", "HV_018_01", "HV_019_01","HV_020_01")

P23_LH<-c("HV_021_03", "HV_022_02", "HV_023_02", "HV_024_02","HV_025_03")
P23_RH<-c("HV_026_02", "HV_027_09", "HV_028_02", "HV_029_02","HV_030_02")
P23_SC<-c("HV_016_02", "HV_017_02", "HV_018_02", "HV_019_02","HV_020_02")

P24_LH<-c("HV_021_04", "HV_022_03", "HV_023_03", "HV_024_03","HV_025_04")
P24_RH<-c("HV_026_03", "HV_027_10", "HV_028_03", "HV_029_03","HV_030_03")
P24_SC<-c("HV_016_03", "HV_017_03", "HV_018_03", "HV_019_03","HV_021_01")

P25_LH<-c("HV_021_05", "HV_022_04", "HV_023_04", "HV_024_04","HV_025_05")
P25_RH<-c("HV_026_04", "HV_027_11", "HV_028_04", "HV_029_04","HV_030_04")
P25_SC<-c("HV_016_04", "HV_017_04", "HV_018_04", "HV_019_04","HV_020_03")

P26_LH<-c("HV_021_06", "HV_022_05", "HV_023_05", "HV_024_05","HV_025_06")
P26_RH<-c("HV_026_05", "HV_027_12", "HV_028_05", "HV_029_05","HV_030_05")
P26_SC<-c("HV_016_05", "HV_017_05", "HV_018_05", "HV_019_05","HV_020_04")

P27_LH<-c("HV_021_07", "HV_022_06", "HV_023_06", "HV_024_06","HV_025_07")
P27_RH<-c("HV_026_06", "HV_027_13", "HV_028_06", "HV_029_06","HV_030_06")
P27_SC<-c("HV_016_06", "HV_017_06", "HV_018_06", "HV_019_06","HV_020_05")

P28_LH<-c("HV_021_08", "HV_022_07", "HV_023_07", "HV_024_07","HV_025_08")
P28_RH<-c("HV_026_07", "HV_027_14", "HV_028_07", "HV_029_07","HV_030_07")
P28_SC<-c("HV_016_07", "HV_017_07", "HV_018_07", "HV_019_07","HV_020_06")

P29_LH<-c("HV_021_09", "HV_022_08", "HV_023_08", "HV_024_08","HV_025_09")
P29_RH<-c("HV_026_08", "HV_027_15", "HV_028_08", "HV_029_08","HV_030_08")
P29_SC<-c("HV_016_08", "HV_017_08", "HV_018_08", "HV_019_08","HV_020_07")

P30_LH<-c("HV_021_10", "HV_022_09", "HV_023_09", "HV_024_09","HV_025_10")
P30_RH<-c("HV_026_09", "HV_027_16", "HV_028_09", "HV_029_09","HV_030_09")
P30_SC<-c("HV_016_09", "HV_017_09", "HV_018_09", "HV_019_09","HV_020_08")

P31_LH<-c("HV_021_11", "HV_022_10", "HV_023_10","HV_024_10")
P31_RH<-c("HV_026_10", "HV_027_18", "HV_028_10","HV_029_10")
P31_SC<-c("HV_016_10", "HV_017_10", "HV_018_10","HV_019_10")

P32_LH<-c("HV_021_12", "HV_022_11", "HV_023_11", "HV_024_11","HV_025_11")
P32_RH<-c("HV_026_11", "HV_027_19", "HV_028_11", "HV_029_11","HV_030_10")
P32_SC<-c("HV_016_11", "HV_017_11", "HV_018_11", "HV_019_11","HV_020_09")

P34_LH<-c("HV_021_14", "HV_022_12", "HV_023_12", "HV_024_12","HV_025_12")
P34_RH<-c("V_026_12", "HV_027_20", "HV_028_12", "HV_029_12","HV_030_11")
P34_SC<-c("HV_016_12", "HV_017_12", "HV_018_12", "HV_019_12","HV_020_11")

P35_LH<-c("HV_021_15", "HV_022_13", "HV_023_13", "HV_024_13","HV_025_13")
P35_RH<-c("HV_026_13", "HV_027_21", "HV_028_13", "HV_029_13","HV_030_12")
P35_SC<-c("HV_016_13", "HV_017_13", "HV_018_13", "HV_019_13","HV_020_12")

P36_LH<-c("HV_021_16", "HV_022_14", "HV_023_14", "HV_024_14","HV_025_14")
P36_RH<-c("HV_026_14", "HV_027_22", "HV_028_14", "HV_029_14","HV_030_13")
P36_SC<-c("HV_016_14", "HV_017_14", "HV_018_14", "HV_019_14","HV_020_13")

P37_LH<-c("HV_021_18", "HV_022_15", "HV_023_15", "HV_024_15","HV_025_15")
P37_RH<-c("HV_026_15", "HV_028_15", "HV_029_15", "HV_030_14","HV_030_22")
P37_SC<-c("HV_016_15", "HV_017_15", "HV_018_15", "HV_019_15","HV_020_14")

P38_LH<-c("HV_021_19", "HV_022_16", "HV_023_16", "HV_024_16","HV_025_16")
P38_RH<-c("HV_026_16", "HV_028_16", "HV_029_16","HV_030_15")
P38_SC<-c("HV_016_16", "HV_017_16", "HV_018_16", "HV_019_16","HV_020_15")

P39_LH<-c("HV_021_20", "HV_022_18", "HV_023_18", "HV_024_18","HV_025_18")
P39_RH<-c("HV_026_18", "HV_028_18", "HV_029_18","HV_030_16")
P39_SC<-c("HV_016_18", "HV_017_18", "HV_018_18", "HV_019_18","HV_020_16")

P40_LH<-c("HV_021_21", "HV_022_19", "HV_023_19", "HV_024_19","HV_025_19")
P40_RH<-c("HV_026_19", "HV_028_19", "HV_029_19","HV_030_18")
P40_SC<-c("HV_016_19", "HV_017_19", "HV_018_19", "HV_019_19","HV_020_18")

P41_LH<-c("HV_021_22", "HV_022_20", "HV_023_20", "HV_024_20","HV_025_20")
P41_RH<-c("HV_026_20", "HV_028_20", "HV_029_20","HV_030_19")
P41_SC<-c("HV_016_20", "HV_017_20", "HV_018_20", "HV_019_20","HV_020_19")

P42_LH<-c("HV_022_21", "HV_023_21", "HV_024_21","HV_025_21")
P42_RH<-c("HV_026_21", "HV_028_21", "HV_029_21","HV_030_20")
P42_SC<-c("HV_016_21", "HV_017_21", "HV_018_21", "HV_019_21","HV_020_20")

P43_LH<-c("HV_022_22", "HV_023_22", "HV_024_22", "HV_025_01","HV_025_22")
P43_RH<-c("HV_026_22", "HV_028_22", "HV_029_22","HV_030_21")
P43_SC<-c("HV_016_22", "HV_017_22", "HV_018_22", "HV_019_22","HV_020_21")
```
\
