---
title: "6_Relative_Abundance_Fig2"
output: html_document
---

## Description

# Input Notes: 
  #Will need the following files:
  #Sequencing_Data_Info_Sheet3.csv (Metadata, provided on Github)
  #counts2_bowtie.csv (generated in 3_Virome_Contig_Mapping.sh)
   #vc_tax.csv (generated in 4_Contig_Annotation.sh)

# Output Notes: 
  #Will generate a relative abundance plot (Figure 2) for the top then most abundant viral family taxonomy per subject by location

```{r setup, include=FALSE}
############################################
## -------------------------------------- ##
## ---------- Packages to Load ---------- ##
## -------------------------------------- ##
############################################
library(readr)
library(dplyr)
library(tidyr)
library(phyloseq)
library(ggplot2)
```

```{r setup, include=FALSE}
############################################
## -------------------------------------- ##
## -------- Make Phyloseq Object -------- ##
## -------------------------------------- ##
############################################

## Upload sample metadata for the Phyloseq object
Upload_Metadata <- read_csv("Sequencing_Data_Info_Sheet3.csv")
Metadata <- Upload_Metadata
# In the metadata change the Time_Collected so that it is better for graph outputs
Metadata$Time <- Metadata$Time_Collected
Metadata$Time[which(Metadata$Time == "T_0")] <- "00_Weeks"
Metadata$Time[which(Metadata$Time == "2_week")] <- "02_Weeks"
Metadata$Time[which(Metadata$Time == "1_month")] <- "04_Weeks"
Metadata$Time[which(Metadata$Time == "3_month")] <- "12_Weeks"
Metadata$Time[which(Metadata$Time == "6_month")] <- "24_Weeks"
# Make sample_data for Phyloseq
META <- sample_data(Metadata)
sample_names(META)= META$SampleID

## Upload count data to make the OTU table for the Phyloseq object

CHeckV_counts <- read.csv("counts2_bowtie.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
CHeckV_counts  <- subset(CHeckV_counts , select = -c(length))
# Make otu_table for Phyloseq
CHeckV_bar_OTU <- otu_table(CHeckV_counts, taxa_are_rows = TRUE)

## Upload taxonomy information to make the OTU table for the Phyloseq object

tax_ann <- read.csv("vc_tax.csv", quote = "", header = TRUE, stringsAsFactors = FALSE, row.names = 1)
tax_ann <-as.matrix(tax_ann)
# Make tax_table for Phyloseq
CHeckV_bar_tax <- tax_table(tax_ann)

## Make Phyloseq object

CHeckV_bar_PHY <- phyloseq(CHeckV_bar_OTU, CHeckV_bar_tax, META)

## Remove samples from individuals who did not complete from the study, samples from individuals who did not have a complete set of samples, and samples that were repeated samples

Samples_toRemove <- c("HV_001_27", "HV_002_27", "HV_003_27", "HV_004_27", "HV_005_27", "HV_006_27", "HV_007_27", "HV_008_27",
                      "HV_009_27", "HV_010_27", "HV_011_27", "HV_012_27", "HV_013_27", "HV_014_27", "HV_015_27", "HV_016_27",
                      "HV_017_27", "HV_018_27", "HV_019_27", "HV_020_27", "HV_021_27", "HV_022_27", "HV_023_27", "HV_024_27",
                      "HV_025_27", "HV_026_27", "HV_027_27", "HV_028_27", "HV_029_27", "HV_030_27", "HV_015_20", "HV_015_21", 
                      "HV_020_22", "HV_027_02", "HV_027_03", "HV_027_04", "HV_027_05", "HV_027_06", "HV_027_07", "HV_020_10",
                      "HV_021_13", "HV_027_01","HV_003_15")

## Final Phyloseq Object

CHeckV_bar_PHY2 <- subset_samples(CHeckV_bar_PHY, !(SampleID %in% Samples_toRemove))
```

# Human Skin Virome Phyloseq Object:
```{r}
CHeckV_bar_PHY2
```

```{r, include=FALSE}
############################################
## -------------------------------------- ##
## --------- Left Hand Taxa Sums -------- ##
## -------------------------------------- ##
############################################

## Calculate the top ten most abundant identified family level taxonomy for each subject for all left hand samples

CHeckV_bar_PHY2_LH<- subset_samples(CHeckV_bar_PHY2, Location=="left")
P_01 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P01")
TopNOTUs_P01 <- sort(tapply(taxa_sums(P_01), tax_table(P_01)[, "Family"], sum), TRUE)[1:10]
P_02 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P02")
TopNOTUs_P02 <- sort(tapply(taxa_sums(P_02), tax_table(P_02)[, "Family"], sum), TRUE)[1:10]
P_03 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P03")
TopNOTUs_P03 <- sort(tapply(taxa_sums(P_03), tax_table(P_03)[, "Family"], sum), TRUE)[1:10]
P_04 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P04")
TopNOTUs_P04 <- sort(tapply(taxa_sums(P_04), tax_table(P_04)[, "Family"], sum), TRUE)[1:10]
P_05 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P05")
TopNOTUs_P05 <- sort(tapply(taxa_sums(P_05), tax_table(P_05)[, "Family"], sum), TRUE)[1:10]
P_06 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P06")
TopNOTUs_P06 <- sort(tapply(taxa_sums(P_06), tax_table(P_06)[, "Family"], sum), TRUE)[1:10]
P_07 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P07")
TopNOTUs_P07 <- sort(tapply(taxa_sums(P_07), tax_table(P_07)[, "Family"], sum), TRUE)[1:10]
P_08 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P08")
TopNOTUs_P08 <- sort(tapply(taxa_sums(P_08), tax_table(P_08)[, "Family"], sum), TRUE)[1:10]
P_09 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P09")
TopNOTUs_P09 <- sort(tapply(taxa_sums(P_09), tax_table(P_09)[, "Family"], sum), TRUE)[1:10]
P_10 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P10")
TopNOTUs_P10 <- sort(tapply(taxa_sums(P_10), tax_table(P_10)[, "Family"], sum), TRUE)[1:10]
P_11 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P11")
TopNOTUs_P11 <- sort(tapply(taxa_sums(P_11), tax_table(P_11)[, "Family"], sum), TRUE)[1:10]
P_12 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P12")
TopNOTUs_P12 <- sort(tapply(taxa_sums(P_12), tax_table(P_12)[, "Family"], sum), TRUE)[1:10]
P_13 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P13")
TopNOTUs_P13 <- sort(tapply(taxa_sums(P_13), tax_table(P_13)[, "Family"], sum), TRUE)[1:10]
P_14 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P14")
TopNOTUs_P14 <- sort(tapply(taxa_sums(P_14), tax_table(P_14)[, "Family"], sum), TRUE)[1:10]
P_15 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P15")
TopNOTUs_P15 <- sort(tapply(taxa_sums(P_15), tax_table(P_15)[, "Family"], sum), TRUE)[1:10]
P_16 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P16")
TopNOTUs_P16 <- sort(tapply(taxa_sums(P_16), tax_table(P_16)[, "Family"], sum), TRUE)[1:10]
P_17 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P17")
TopNOTUs_P17 <- sort(tapply(taxa_sums(P_17), tax_table(P_17)[, "Family"], sum), TRUE)[1:10]
P_18 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P18")
TopNOTUs_P18 <- sort(tapply(taxa_sums(P_18), tax_table(P_18)[, "Family"], sum), TRUE)[1:10]
P_19 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P19")
TopNOTUs_P19 <- sort(tapply(taxa_sums(P_19), tax_table(P_19)[, "Family"], sum), TRUE)[1:10]
P_20 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P20")
TopNOTUs_P20 <- sort(tapply(taxa_sums(P_20), tax_table(P_20)[, "Family"], sum), TRUE)[1:10]
P_21 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P21")
TopNOTUs_P21 <- sort(tapply(taxa_sums(P_21), tax_table(P_21)[, "Family"], sum), TRUE)[1:10]
P_22 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P22")
TopNOTUs_P22 <- sort(tapply(taxa_sums(P_22), tax_table(P_22)[, "Family"], sum), TRUE)[1:10]
P_23 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P23")
TopNOTUs_P23 <- sort(tapply(taxa_sums(P_23), tax_table(P_23)[, "Family"], sum), TRUE)[1:10]
P_24 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P24")
TopNOTUs_P24 <- sort(tapply(taxa_sums(P_24), tax_table(P_24)[, "Family"], sum), TRUE)[1:10]
P_25 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P25")
TopNOTUs_P25 <- sort(tapply(taxa_sums(P_25), tax_table(P_25)[, "Family"], sum), TRUE)[1:10]
P_26 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P26")
TopNOTUs_P26 <- sort(tapply(taxa_sums(P_26), tax_table(P_26)[, "Family"], sum), TRUE)[1:10]
P_27 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P27")
TopNOTUs_P27 <- sort(tapply(taxa_sums(P_27), tax_table(P_27)[, "Family"], sum), TRUE)[1:10]
P_28 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P28")
TopNOTUs_P28 <- sort(tapply(taxa_sums(P_28), tax_table(P_28)[, "Family"], sum), TRUE)[1:10]
P_29 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P29")
TopNOTUs_P29 <- sort(tapply(taxa_sums(P_29), tax_table(P_29)[, "Family"], sum), TRUE)[1:10]
P_30 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P30")
TopNOTUs_P30 <- sort(tapply(taxa_sums(P_30), tax_table(P_30)[, "Family"], sum), TRUE)[1:10]
P_31 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P31")
TopNOTUs_P31 <- sort(tapply(taxa_sums(P_31), tax_table(P_31)[, "Family"], sum), TRUE)[1:10]
P_32 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P32")
TopNOTUs_P32 <- sort(tapply(taxa_sums(P_32), tax_table(P_32)[, "Family"], sum), TRUE)[1:10]
P_34 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P34")
TopNOTUs_P34 <- sort(tapply(taxa_sums(P_34), tax_table(P_34)[, "Family"], sum), TRUE)[1:10]
P_35 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P35")
TopNOTUs_P35 <- sort(tapply(taxa_sums(P_35), tax_table(P_35)[, "Family"], sum), TRUE)[1:10]
P_36 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P36")
TopNOTUs_P36 <- sort(tapply(taxa_sums(P_36), tax_table(P_36)[, "Family"], sum), TRUE)[1:10]
P_37 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P37")
TopNOTUs_P37 <- sort(tapply(taxa_sums(P_37), tax_table(P_37)[, "Family"], sum), TRUE)[1:10]
P_38 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P38")
TopNOTUs_P38 <- sort(tapply(taxa_sums(P_38), tax_table(P_38)[, "Family"], sum), TRUE)[1:10]
P_39 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P39")
TopNOTUs_P39 <- sort(tapply(taxa_sums(P_39), tax_table(P_39)[, "Family"], sum), TRUE)[1:10]
P_40 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P40")
TopNOTUs_P40 <- sort(tapply(taxa_sums(P_40), tax_table(P_40)[, "Family"], sum), TRUE)[1:10]
P_41 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P41")
TopNOTUs_P41 <- sort(tapply(taxa_sums(P_41), tax_table(P_41)[, "Family"], sum), TRUE)[1:10]
P_42 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P42")
TopNOTUs_P42 <- sort(tapply(taxa_sums(P_42), tax_table(P_42)[, "Family"], sum), TRUE)[1:10]
P_43 <- subset_samples(CHeckV_bar_PHY2_LH, Subject=="P43")
TopNOTUs_P43 <- sort(tapply(taxa_sums(P_43), tax_table(P_43)[, "Family"], sum), TRUE)[1:10]
TopNOTUs_10_LH<-c(TopNOTUs_P01,TopNOTUs_P02,TopNOTUs_P03,TopNOTUs_P04,TopNOTUs_P05,TopNOTUs_P06,TopNOTUs_P07,TopNOTUs_P08,TopNOTUs_P09,TopNOTUs_P10,TopNOTUs_P11,TopNOTUs_P12,TopNOTUs_P13,TopNOTUs_P14,TopNOTUs_P15,TopNOTUs_P16,TopNOTUs_P17,TopNOTUs_P18,TopNOTUs_P19,TopNOTUs_P20,TopNOTUs_P21,TopNOTUs_P22,TopNOTUs_P23,TopNOTUs_P24,TopNOTUs_P25,TopNOTUs_P26,TopNOTUs_P27,TopNOTUs_P28,TopNOTUs_P29,TopNOTUs_P30,TopNOTUs_P31,TopNOTUs_P32,TopNOTUs_P34,TopNOTUs_P35,TopNOTUs_P36,TopNOTUs_P37,TopNOTUs_P38,TopNOTUs_P39,TopNOTUs_P40,TopNOTUs_P41,TopNOTUs_P42,TopNOTUs_P43)
TopNOTUs_10_list_LH<-unique(names(TopNOTUs_10_LH))

# Viral Families that were not able to be taxonomically annotated (i.e. Unclassified Virus) were reduced
TopNOTUs_10_list_noUn_LH<-TopNOTUs_10_list_LH[!grepl("Unclassified",TopNOTUs_10_list_LH)]
TopNOTUs_10_list_noUn_LH<-TopNOTUs_10_list_noUn_LH[!grepl("Unlcassified",TopNOTUs_10_list_noUn_LH)]
TopNOTUs_10_list_noUn_LH<-c(TopNOTUs_10_list_noUn_LH,"Unclassified Cressdnaviricota")
TopNOTUs_10_list_noUn_LH<-c(TopNOTUs_10_list_noUn_LH,"Unclassified Duplodnaviria")
TopNOTUs_10_list_noUn_LH<-c(TopNOTUs_10_list_noUn_LH,"Unclassified Monodnaviria")
```

```{r}
# Top ten most abundant family level taxa per individual for left hand samples:
TopNOTUs_10_list_noUn_LH
```

```{r, include=FALSE}
############################################
## -------------------------------------- ##
## -------- Right Hand Taxa Sums -------- ##
## -------------------------------------- ##
############################################

## Calculate the top ten most abundant identified family level taxonomy for each subject for all right hand samples

CHeckV_bar_PHY2_RH<- subset_samples(CHeckV_bar_PHY2, Location=="right")
P_01 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P01")
TopNOTUs_P01 <- sort(tapply(taxa_sums(P_01), tax_table(P_01)[, "Family"], sum), TRUE)[1:10]
P_02 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P02")
TopNOTUs_P02 <- sort(tapply(taxa_sums(P_02), tax_table(P_02)[, "Family"], sum), TRUE)[1:10]
P_03 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P03")
TopNOTUs_P03 <- sort(tapply(taxa_sums(P_03), tax_table(P_03)[, "Family"], sum), TRUE)[1:10]
P_04 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P04")
TopNOTUs_P04 <- sort(tapply(taxa_sums(P_04), tax_table(P_04)[, "Family"], sum), TRUE)[1:10]
P_05 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P05")
TopNOTUs_P05 <- sort(tapply(taxa_sums(P_05), tax_table(P_05)[, "Family"], sum), TRUE)[1:10]
P_06 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P06")
TopNOTUs_P06 <- sort(tapply(taxa_sums(P_06), tax_table(P_06)[, "Family"], sum), TRUE)[1:10]
P_07 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P07")
TopNOTUs_P07 <- sort(tapply(taxa_sums(P_07), tax_table(P_07)[, "Family"], sum), TRUE)[1:10]
P_08 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P08")
TopNOTUs_P08 <- sort(tapply(taxa_sums(P_08), tax_table(P_08)[, "Family"], sum), TRUE)[1:10]
P_09 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P09")
TopNOTUs_P09 <- sort(tapply(taxa_sums(P_09), tax_table(P_09)[, "Family"], sum), TRUE)[1:10]
P_10 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P10")
TopNOTUs_P10 <- sort(tapply(taxa_sums(P_10), tax_table(P_10)[, "Family"], sum), TRUE)[1:10]
P_11 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P11")
TopNOTUs_P11 <- sort(tapply(taxa_sums(P_11), tax_table(P_11)[, "Family"], sum), TRUE)[1:10]
P_12 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P12")
TopNOTUs_P12 <- sort(tapply(taxa_sums(P_12), tax_table(P_12)[, "Family"], sum), TRUE)[1:10]
P_13 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P13")
TopNOTUs_P13 <- sort(tapply(taxa_sums(P_13), tax_table(P_13)[, "Family"], sum), TRUE)[1:10]
P_14 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P14")
TopNOTUs_P14 <- sort(tapply(taxa_sums(P_14), tax_table(P_14)[, "Family"], sum), TRUE)[1:10]
P_15 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P15")
TopNOTUs_P15 <- sort(tapply(taxa_sums(P_15), tax_table(P_15)[, "Family"], sum), TRUE)[1:10]
P_16 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P16")
TopNOTUs_P16 <- sort(tapply(taxa_sums(P_16), tax_table(P_16)[, "Family"], sum), TRUE)[1:10]
P_17 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P17")
TopNOTUs_P17 <- sort(tapply(taxa_sums(P_17), tax_table(P_17)[, "Family"], sum), TRUE)[1:10]
P_18 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P18")
TopNOTUs_P18 <- sort(tapply(taxa_sums(P_18), tax_table(P_18)[, "Family"], sum), TRUE)[1:10]
P_19 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P19")
TopNOTUs_P19 <- sort(tapply(taxa_sums(P_19), tax_table(P_19)[, "Family"], sum), TRUE)[1:10]
P_20 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P20")
TopNOTUs_P20 <- sort(tapply(taxa_sums(P_20), tax_table(P_20)[, "Family"], sum), TRUE)[1:10]
P_21 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P21")
TopNOTUs_P21 <- sort(tapply(taxa_sums(P_21), tax_table(P_21)[, "Family"], sum), TRUE)[1:10]
P_22 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P22")
TopNOTUs_P22 <- sort(tapply(taxa_sums(P_22), tax_table(P_22)[, "Family"], sum), TRUE)[1:10]
P_23 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P23")
TopNOTUs_P23 <- sort(tapply(taxa_sums(P_23), tax_table(P_23)[, "Family"], sum), TRUE)[1:10]
P_24 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P24")
TopNOTUs_P24 <- sort(tapply(taxa_sums(P_24), tax_table(P_24)[, "Family"], sum), TRUE)[1:10]
P_25 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P25")
TopNOTUs_P25 <- sort(tapply(taxa_sums(P_25), tax_table(P_25)[, "Family"], sum), TRUE)[1:10]
P_26 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P26")
TopNOTUs_P26 <- sort(tapply(taxa_sums(P_26), tax_table(P_26)[, "Family"], sum), TRUE)[1:10]
P_27 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P27")
TopNOTUs_P27 <- sort(tapply(taxa_sums(P_27), tax_table(P_27)[, "Family"], sum), TRUE)[1:10]
P_28 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P28")
TopNOTUs_P28 <- sort(tapply(taxa_sums(P_28), tax_table(P_28)[, "Family"], sum), TRUE)[1:10]
P_29 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P29")
TopNOTUs_P29 <- sort(tapply(taxa_sums(P_29), tax_table(P_29)[, "Family"], sum), TRUE)[1:10]
P_30 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P30")
TopNOTUs_P30 <- sort(tapply(taxa_sums(P_30), tax_table(P_30)[, "Family"], sum), TRUE)[1:10]
P_31 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P31")
TopNOTUs_P31 <- sort(tapply(taxa_sums(P_31), tax_table(P_31)[, "Family"], sum), TRUE)[1:10]
P_32 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P32")
TopNOTUs_P32 <- sort(tapply(taxa_sums(P_32), tax_table(P_32)[, "Family"], sum), TRUE)[1:10]
P_34 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P34")
TopNOTUs_P34 <- sort(tapply(taxa_sums(P_34), tax_table(P_34)[, "Family"], sum), TRUE)[1:10]
P_35 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P35")
TopNOTUs_P35 <- sort(tapply(taxa_sums(P_35), tax_table(P_35)[, "Family"], sum), TRUE)[1:10]
P_36 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P36")
TopNOTUs_P36 <- sort(tapply(taxa_sums(P_36), tax_table(P_36)[, "Family"], sum), TRUE)[1:10]
P_37 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P37")
TopNOTUs_P37 <- sort(tapply(taxa_sums(P_37), tax_table(P_37)[, "Family"], sum), TRUE)[1:10]
P_38 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P38")
TopNOTUs_P38 <- sort(tapply(taxa_sums(P_38), tax_table(P_38)[, "Family"], sum), TRUE)[1:10]
P_39 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P39")
TopNOTUs_P39 <- sort(tapply(taxa_sums(P_39), tax_table(P_39)[, "Family"], sum), TRUE)[1:10]
P_40 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P40")
TopNOTUs_P40 <- sort(tapply(taxa_sums(P_40), tax_table(P_40)[, "Family"], sum), TRUE)[1:10]
P_41 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P41")
TopNOTUs_P41 <- sort(tapply(taxa_sums(P_41), tax_table(P_41)[, "Family"], sum), TRUE)[1:10]
P_42 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P42")
TopNOTUs_P42 <- sort(tapply(taxa_sums(P_42), tax_table(P_42)[, "Family"], sum), TRUE)[1:10]
P_43 <- subset_samples(CHeckV_bar_PHY2_RH, Subject=="P43")
TopNOTUs_P43 <- sort(tapply(taxa_sums(P_43), tax_table(P_43)[, "Family"], sum), TRUE)[1:10]
TopNOTUs_10_RH<-c(TopNOTUs_P01,TopNOTUs_P02,TopNOTUs_P03,TopNOTUs_P04,TopNOTUs_P05,TopNOTUs_P06,TopNOTUs_P07,TopNOTUs_P08,TopNOTUs_P09,TopNOTUs_P10,TopNOTUs_P11,TopNOTUs_P12,TopNOTUs_P13,TopNOTUs_P14,TopNOTUs_P15,TopNOTUs_P16,TopNOTUs_P17,TopNOTUs_P18,TopNOTUs_P19,TopNOTUs_P20,TopNOTUs_P21,TopNOTUs_P22,TopNOTUs_P23,TopNOTUs_P24,TopNOTUs_P25,TopNOTUs_P26,TopNOTUs_P27,TopNOTUs_P28,TopNOTUs_P29,TopNOTUs_P30,TopNOTUs_P31,TopNOTUs_P32,TopNOTUs_P34,TopNOTUs_P35,TopNOTUs_P36,TopNOTUs_P37,TopNOTUs_P38,TopNOTUs_P39,TopNOTUs_P40,TopNOTUs_P41,TopNOTUs_P42,TopNOTUs_P43)
TopNOTUs_10_list_RH<-unique(names(TopNOTUs_10_RH))

# Viral Families that were not able to be taxonomically annotated (i.e. Unclassified Virus) were reduced
TopNOTUs_10_list_noUn_RH<-TopNOTUs_10_list_RH[!grepl("Unclassified",TopNOTUs_10_list_RH)]
TopNOTUs_10_list_noUn_RH<-TopNOTUs_10_list_noUn_RH[!grepl("Unlcassified",TopNOTUs_10_list_noUn_RH)]
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Caudovirales")
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Cressdnaviricota")
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Duplodnaviria")
TopNOTUs_10_list_noUn_RH<-c(TopNOTUs_10_list_noUn_RH,"Unclassified Monodnaviria")
```

```{r}
# Top ten most abundant family level taxa per individual for right hand samples:
TopNOTUs_10_list_noUn_RH
```

```{r, include=FALSE}
############################################
## -------------------------------------- ##
## ----------  Scalp Taxa Sums ---------- ##
## -------------------------------------- ##
############################################

## Calculate the top ten most abundant identified family level taxonomy for each subject for all scalp samples

CHeckV_bar_PHY2_SC<- subset_samples(CHeckV_bar_PHY2, Location=="scalp")
P_01 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P01")
TopNOTUs_P01 <- sort(tapply(taxa_sums(P_01), tax_table(P_01)[, "Family"], sum), TRUE)[1:10]
P_02 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P02")
TopNOTUs_P02 <- sort(tapply(taxa_sums(P_02), tax_table(P_02)[, "Family"], sum), TRUE)[1:10]
P_03 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P03")
TopNOTUs_P03 <- sort(tapply(taxa_sums(P_03), tax_table(P_03)[, "Family"], sum), TRUE)[1:10]
P_04 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P04")
TopNOTUs_P04 <- sort(tapply(taxa_sums(P_04), tax_table(P_04)[, "Family"], sum), TRUE)[1:10]
P_05 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P05")
TopNOTUs_P05 <- sort(tapply(taxa_sums(P_05), tax_table(P_05)[, "Family"], sum), TRUE)[1:10]
P_06 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P06")
TopNOTUs_P06 <- sort(tapply(taxa_sums(P_06), tax_table(P_06)[, "Family"], sum), TRUE)[1:10]
P_07 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P07")
TopNOTUs_P07 <- sort(tapply(taxa_sums(P_07), tax_table(P_07)[, "Family"], sum), TRUE)[1:10]
P_08 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P08")
TopNOTUs_P08 <- sort(tapply(taxa_sums(P_08), tax_table(P_08)[, "Family"], sum), TRUE)[1:10]
P_09 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P09")
TopNOTUs_P09 <- sort(tapply(taxa_sums(P_09), tax_table(P_09)[, "Family"], sum), TRUE)[1:10]
P_10 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P10")
TopNOTUs_P10 <- sort(tapply(taxa_sums(P_10), tax_table(P_10)[, "Family"], sum), TRUE)[1:10]
P_11 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P11")
TopNOTUs_P11 <- sort(tapply(taxa_sums(P_11), tax_table(P_11)[, "Family"], sum), TRUE)[1:10]
P_12 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P12")
TopNOTUs_P12 <- sort(tapply(taxa_sums(P_12), tax_table(P_12)[, "Family"], sum), TRUE)[1:10]
P_13 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P13")
TopNOTUs_P13 <- sort(tapply(taxa_sums(P_13), tax_table(P_13)[, "Family"], sum), TRUE)[1:10]
P_14 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P14")
TopNOTUs_P14 <- sort(tapply(taxa_sums(P_14), tax_table(P_14)[, "Family"], sum), TRUE)[1:10]
P_15 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P15")
TopNOTUs_P15 <- sort(tapply(taxa_sums(P_15), tax_table(P_15)[, "Family"], sum), TRUE)[1:10]
P_16 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P16")
TopNOTUs_P16 <- sort(tapply(taxa_sums(P_16), tax_table(P_16)[, "Family"], sum), TRUE)[1:10]
P_17 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P17")
TopNOTUs_P17 <- sort(tapply(taxa_sums(P_17), tax_table(P_17)[, "Family"], sum), TRUE)[1:10]
P_18 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P18")
TopNOTUs_P18 <- sort(tapply(taxa_sums(P_18), tax_table(P_18)[, "Family"], sum), TRUE)[1:10]
P_19 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P19")
TopNOTUs_P19 <- sort(tapply(taxa_sums(P_19), tax_table(P_19)[, "Family"], sum), TRUE)[1:10]
P_20 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P20")
TopNOTUs_P20 <- sort(tapply(taxa_sums(P_20), tax_table(P_20)[, "Family"], sum), TRUE)[1:10]
P_21 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P21")
TopNOTUs_P21 <- sort(tapply(taxa_sums(P_21), tax_table(P_21)[, "Family"], sum), TRUE)[1:10]
P_22 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P22")
TopNOTUs_P22 <- sort(tapply(taxa_sums(P_22), tax_table(P_22)[, "Family"], sum), TRUE)[1:10]
P_23 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P23")
TopNOTUs_P23 <- sort(tapply(taxa_sums(P_23), tax_table(P_23)[, "Family"], sum), TRUE)[1:10]
P_24 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P24")
TopNOTUs_P24 <- sort(tapply(taxa_sums(P_24), tax_table(P_24)[, "Family"], sum), TRUE)[1:10]
P_25 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P25")
TopNOTUs_P25 <- sort(tapply(taxa_sums(P_25), tax_table(P_25)[, "Family"], sum), TRUE)[1:10]
P_26 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P26")
TopNOTUs_P26 <- sort(tapply(taxa_sums(P_26), tax_table(P_26)[, "Family"], sum), TRUE)[1:10]
P_27 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P27")
TopNOTUs_P27 <- sort(tapply(taxa_sums(P_27), tax_table(P_27)[, "Family"], sum), TRUE)[1:10]
P_28 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P28")
TopNOTUs_P28 <- sort(tapply(taxa_sums(P_28), tax_table(P_28)[, "Family"], sum), TRUE)[1:10]
P_29 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P29")
TopNOTUs_P29 <- sort(tapply(taxa_sums(P_29), tax_table(P_29)[, "Family"], sum), TRUE)[1:10]
P_30 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P30")
TopNOTUs_P30 <- sort(tapply(taxa_sums(P_30), tax_table(P_30)[, "Family"], sum), TRUE)[1:10]
P_31 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P31")
TopNOTUs_P31 <- sort(tapply(taxa_sums(P_31), tax_table(P_31)[, "Family"], sum), TRUE)[1:10]
P_32 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P32")
TopNOTUs_P32 <- sort(tapply(taxa_sums(P_32), tax_table(P_32)[, "Family"], sum), TRUE)[1:10]
P_34 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P34")
TopNOTUs_P34 <- sort(tapply(taxa_sums(P_34), tax_table(P_34)[, "Family"], sum), TRUE)[1:10]
P_35 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P35")
TopNOTUs_P35 <- sort(tapply(taxa_sums(P_35), tax_table(P_35)[, "Family"], sum), TRUE)[1:10]
P_36 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P36")
TopNOTUs_P36 <- sort(tapply(taxa_sums(P_36), tax_table(P_36)[, "Family"], sum), TRUE)[1:10]
P_37 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P37")
TopNOTUs_P37 <- sort(tapply(taxa_sums(P_37), tax_table(P_37)[, "Family"], sum), TRUE)[1:10]
P_38 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P38")
TopNOTUs_P38 <- sort(tapply(taxa_sums(P_38), tax_table(P_38)[, "Family"], sum), TRUE)[1:10]
P_39 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P39")
TopNOTUs_P39 <- sort(tapply(taxa_sums(P_39), tax_table(P_39)[, "Family"], sum), TRUE)[1:10]
P_40 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P40")
TopNOTUs_P40 <- sort(tapply(taxa_sums(P_40), tax_table(P_40)[, "Family"], sum), TRUE)[1:10]
P_41 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P41")
TopNOTUs_P41 <- sort(tapply(taxa_sums(P_41), tax_table(P_41)[, "Family"], sum), TRUE)[1:10]
P_42 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P42")
TopNOTUs_P42 <- sort(tapply(taxa_sums(P_42), tax_table(P_42)[, "Family"], sum), TRUE)[1:10]
P_43 <- subset_samples(CHeckV_bar_PHY2_SC, Subject=="P43")
TopNOTUs_P43 <- sort(tapply(taxa_sums(P_43), tax_table(P_43)[, "Family"], sum), TRUE)[1:10]
TopNOTUs_10_SC<-c(TopNOTUs_P01,TopNOTUs_P02,TopNOTUs_P03,TopNOTUs_P04,TopNOTUs_P05,TopNOTUs_P06,TopNOTUs_P07,TopNOTUs_P08,TopNOTUs_P09,TopNOTUs_P10,TopNOTUs_P11,TopNOTUs_P12,TopNOTUs_P13,TopNOTUs_P14,TopNOTUs_P15,TopNOTUs_P16,TopNOTUs_P17,TopNOTUs_P18,TopNOTUs_P19,TopNOTUs_P20,TopNOTUs_P21,TopNOTUs_P22,TopNOTUs_P23,TopNOTUs_P24,TopNOTUs_P25,TopNOTUs_P26,TopNOTUs_P27,TopNOTUs_P28,TopNOTUs_P29,TopNOTUs_P30,TopNOTUs_P31,TopNOTUs_P32,TopNOTUs_P34,TopNOTUs_P35,TopNOTUs_P36,TopNOTUs_P37,TopNOTUs_P38,TopNOTUs_P39,TopNOTUs_P40,TopNOTUs_P41,TopNOTUs_P42,TopNOTUs_P43)
TopNOTUs_10_list_SC<-unique(names(TopNOTUs_10_SC))

# Viral Families that were not able to be taxonomically annotated (i.e. Unclassified Virus) were reduced
TopNOTUs_10_list_noUn_SC<-TopNOTUs_10_list_SC[!grepl("Unclassified",TopNOTUs_10_list_SC)]
TopNOTUs_10_list_noUn_SC<-TopNOTUs_10_list_noUn_SC[!grepl("Unlcassified",TopNOTUs_10_list_noUn_SC)]
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Caudovirales")
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Cressdnaviricota")
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Duplodnaviria")
TopNOTUs_10_list_noUn_SC<-c(TopNOTUs_10_list_noUn_SC,"Unclassified Monodnaviria")
```

```{r}
# Top ten most abundant family level taxa per individual for scalp samples:
TopNOTUs_10_list_noUn_SC
```

```{r, include=FALSE}
############################################
## -------------------------------------- ##
## ---------  Relative Abundance -------- ##
## -------------------------------------- ##
############################################

## Calculation of relative abundance for the top ten most abundant taxonomy per subject for left hand 

ent10_LH <- subset_taxa(CHeckV_bar_PHY2, Family %in% TopNOTUs_10_list_noUn_LH)
glom.subject_LH <- merge_samples(ent10_LH, "Subject")
# Calculate the relative abundance for each family in set
glom.subject.family_LH <- transform_sample_counts(glom.subject_LH, function(x) x / sum(x) )
glom_LH <- tax_glom(glom.subject.family_LH, taxrank = 'Family')
# Turn into a data.frame for graph generation
data_glom_LH<- psmelt(glom_LH)
data_glom_LH$Family <- as.character(data_glom_LH$Family)
data_glom_LH$Location<-"Left Hand"
data_glom_LH$Family <- factor(data_glom_LH$Family, levels = c("Siphoviridae", "Podoviridae", "Uncultured phage", "Myoviridae", "Herelleviridae", "Genomoviridae", "Microviridae", "Papillomaviridae", "Lake Sarah-associated circular molecule 3", "Pithoviridae", "Uncultured virus", "Sewage-associated circular DNA molecule", "Streptococcus satellite phage Javan305", "Caulimoviridae", "Staphylococcus phage PhiSepi-HH1", "Phycodnaviridae", "Circoviridae", "Staphylococcus phage PI-Sepi-HH2", "Baculoviridae", "Poxviridae", "Polyomaviridae", "Bovine faeces associated circular DNA virus 1", "Unclassified Cressdnaviricota", "Unclassified Duplodnaviria", "Unclassified Monodnaviria"))

## Calculation of relative abundance for the top ten most abundant taxonomy per subject for right hand 

ent10_RH <- subset_taxa(CHeckV_bar_PHY2, Family %in% TopNOTUs_10_list_noUn_RH)
glom.subject_RH <- merge_samples(ent10_RH, "Subject")
# Calculate the relative abundance for each family in set
glom.subject.family_RH <- transform_sample_counts(glom.subject_RH, function(x) x / sum(x) )
glom_RH <- tax_glom(glom.subject.family_RH, taxrank = 'Family')
# Turn into a data.frame for graph generation
data_glom_RH<- psmelt(glom_RH)
data_glom_RH$Family <- as.character(data_glom_RH$Family)
data_glom_RH$Location<-"Right Hand"
data_glom_RH$Family <- factor(data_glom_RH$Family, levels = c("Caulimoviridae", "Siphoviridae", "Microviridae", "Papillomaviridae", "Genomoviridae", "Herelleviridae", "Baculoviridae", "Circoviridae", "Uncultured phage", "Myoviridae", "Sewage-associated circular DNA molecule", "Lake Sarah-associated circular molecule 3", "Podoviridae", "Mimiviridae", "Staphylococcus phage PI-Sepi-HH2", "Staphylococcus phage PhiSepi-HH1", "Streptococcus satellite phage Javan359", "Streptococcus satellite phage Javan360", "Smacoviridae", "Uncultured human fecal virus clone E.ramosum_S04.r3.N09_4_c1", "Inoviridae", "Uncultured virus isolate Wastewater_Circular_Virus_FL54", "Unclassified Caudovirales", "Unclassified Cressdnaviricota", "Unclassified Duplodnaviria", "Unclassified Monodnaviria"))

## Calculation of relative abundance for the top ten most abundant taxonomy per subject for scalp

ent10_SC <- subset_taxa(CHeckV_bar_PHY2, Family %in% TopNOTUs_10_list_noUn_SC)
glom.subject_SC <- merge_samples(ent10_SC, "Subject")
# Calculate the relative abundance for each family in set
glom.subject.family_SC <- transform_sample_counts(glom.subject_SC, function(x) x / sum(x) )
glom_SC <- tax_glom(glom.subject.family_SC, taxrank = 'Family')
# Turn into a data.frame for graph generation
data_glom_SC<- psmelt(glom_SC)
data_glom_SC$Family <- as.character(data_glom_SC$Family)
data_glom_SC$Location<-"Scalp"
data_glom_SC$Family <- factor(data_glom_SC$Family, levels = c("Circoviridae", "Siphoviridae", "Herelleviridae", "Genomoviridae", "Papillomaviridae", "Lake Sarah-associated circular molecule 3", "Myoviridae", "Uncultured virus", "Podoviridae", "Microviridae", "Caulimoviridae", "Sewage-associated circular DNA molecule", "Autographiviridae", "Retroviridae", "Anelloviridae", "Gopherus associated circular DNA virus 4", "Baculoviridae", "Phycodnaviridae", "Chicken virus mg4_2302", "Streptococcus satellite phage Javan361", "Unclassified Caudovirales", "Unclassified Cressdnaviricota", "Unclassified Duplodnaviria", "Unclassified Monodnaviria" ))

## Combine the three autotomical location datasets

data_glom_ALL<-rbind(data_glom_SC,data_glom_RH,data_glom_LH)

## Generate relative abundance plot

spatial_plot <- ggplot(data=data_glom_ALL, aes(x=Location, y=Abundance, fill=Family)) + facet_grid(~Sample, scales = "free")+geom_col(position = "fill")

relativeabund<-spatial_plot + geom_bar(aes(), stat="identity", position="stack",colour = 'black')  +
theme(legend.position="bottom",axis.title.x = element_text(vjust=1, hjust=2,size=12),legend.text=element_text(size=12),
      axis.title.y = element_text(vjust=1,size=12),) + guides(fill=guide_legend(nrow=7),size=12)+theme(axis.text.x = element_text(angle = 90,size=12))+ylab("Relative Abundance")
ggsave(plot=relativeabund,"Figures/RelativeAbundanceFIGURE.pdf",dpi = 500, width = 29,
  height = 16, units="in",pointsize=12)
```
```{r}
# Relative abundance of the top ten most abundant identified viral families per subject by location:
relativeabund
```
